---
author: "James Howe"
params:
  dataset: "projections"
  path: "data/behavior/projections_silence_epm/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
projection_id <- params$dataset
projection_path <- params$path
start_min <- params$start_min
end_min <- params$end_min

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

projection_groups <- unlist(strsplit(Sys.glob(paste0(projection_path, "SAL/*")),
                                         paste0(projection_path, "SAL/")))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_projection_sal <- vector(mode = "list", length = 4)
data_projection_sal <- lapply(projection_groups, 
                        function(x) lapply(Sys.glob(paste0(projection_path, "SAL/", x, "/*")),
                                           function(y) process_series_epm(y, "silence")))

data_projection_cno <- vector(mode = "list", length = 4)
data_projection_cno <- lapply(projection_groups, 
                        function(x) lapply(Sys.glob(paste0(projection_path, "CNO/", x, "/*")),
                                           function(y) process_series_epm(y, "silence")))

# add names to each
names(data_projection_sal) <- Sys.glob(paste0(projection_path, "SAL/", "*"))
names(data_projection_sal) <- unlist(strsplit(names(data_projection_sal), 
                                                  paste0(projection_path, "SAL/")))[c(FALSE, TRUE)]

names(data_projection_cno) <- Sys.glob(paste0(projection_path, "CNO/", "*"))
names(data_projection_cno) <- unlist(strsplit(names(data_projection_cno), 
                                                  paste0(projection_path, "CNO/")))[c(FALSE, TRUE)]

for (i in 1:length(projection_groups)){
  data_projection_sal <- add_custom_names(data_projection_sal, paste0(projection_path, "SAL/"), 
                                              projection_groups[i], projection_labels[i])
  data_projection_cno <- add_custom_names(data_projection_cno, paste0(projection_path, "CNO/"), 
                                              projection_groups[i], projection_labels[i])
}

data_projection_sal <- list(data_projection_sal$`MeA-control`, data_projection_sal$`MeA-Gi`, 
                                data_projection_sal$`NAc-control`, data_projection_sal$`NAc-Gi`)
names(data_projection_sal) <- c("MeA-control", "MeA-Gi", "NAc-control", "NAc-Gi")

data_projection_cno <- list(data_projection_cno$`MeA-control`, data_projection_cno$`MeA-Gi`, 
                                data_projection_cno$`NAc-control`, data_projection_cno$`NAc-Gi`)
names(data_projection_cno) <- c("MeA-control", "MeA-Gi", "NAc-control", "NAc-Gi")
```

# Open Time-based metrics

### Summary statistics

```{r 2-all_centertime_stats, message = FALSE, warning = FALSE}
projection_sal_array <- transform_epm_opentime(data_projection_sal, "full", "Region", 1, 2400)

projection_cno_array <- transform_epm_opentime(data_projection_cno, "full", "Region", 1, 2400)

opentime_group_projection <- group_array(data_projection_sal, projection_sal_array,
                                         projection_cno_array, "OpenTime")
```

#### MeA

```{r 3-MeA_opentime_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "OpenTime", baseline_OpenTime, treatment_OpenTime) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection$time) <- c("SAL", "CNO")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                  levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection$group) <- c("mCh", "Gi")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

#### NAc

```{r 4-NAc_opentime_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "OpenTime", baseline_OpenTime, treatment_OpenTime) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection$time) <- c("SAL", "CNO")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                  levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection$group) <- c("mCh", "Gi")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

### Stats {.tabset}

#### MeA {.tabset}

##### ANOVA

```{r 5-MeA_open_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 6-MeA_open_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "OpenTime")
```

##### T-test each

```{r 7-MeA_ttest_opentimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "SAL"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "SAL"])

# CNO
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "CNO"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "CNO"])
```

#### NAc {.tabset}

##### ANOVA

```{r 8-NAc_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 9-NAc_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "OpenTime")
```

##### T-test each

```{r 10-NAc_ttest_opentimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "SAL"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "SAL"])

# CNO
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "CNO"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "CNO"])
```

### Plots {.tabset}

#### MeA

```{r 11-MeA_open_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(MeA_group_projection, "Proportion Time in Open Arms", 
            c(control_color, mea_color), topo_ot_axes_min, "white")
```

#### NAc

```{r 12-NAc_open_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(NAc_group_projection, "Proportion Time in Open Arms", 
            c(control_color, nac_color), topo_ot_axes_min, "white")
```

# Open Entry-based metrics

### Summary statistics

```{r 13-all_openentry_stats, message = FALSE, warning = FALSE}
projection_sal_array <- transform_epm_openentry(data_projection_sal, "full", "OpenEntry", 1, 2400)

projection_cno_array <- transform_epm_openentry(data_projection_cno, "full", "OpenEntry", 1, 2400)

openentry_group_projection <- group_array(data_projection_sal, projection_sal_array, projection_cno_array, "OpenEntry")
```

#### MeA

```{r 14-MeA_openentry_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "OpenEntry", baseline_OpenEntry, treatment_OpenEntry) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection$time) <- c("SAL", "CNO")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                  levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection$group) <- c("mCh", "Gi")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenEntry, type = "mean_se")
```

#### NAc

```{r 15-NAc_openentry_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "OpenEntry", baseline_OpenEntry, treatment_OpenEntry) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection$time) <- c("SAL", "CNO")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                  levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection$group) <- c("mCh", "Gi")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenEntry, type = "mean_se")
```

### Stats {.tabset}

#### MeA {.tabset}

##### ANOVA

```{r 16-MeA_openentry_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "OpenEntry")
```

##### Pairwise comparisons

```{r 17-MeA_openentry_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "OpenEntry")
```

##### T-test each

```{r 18-MeA_ttest_openentry, message = FALSE, warning = FALSE}
# SAL
t.test(x = MeA_group_projection$OpenEntry[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "SAL"], 
       y = MeA_group_projection$OpenEntry[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "SAL"])

# CNO
t.test(x = MeA_group_projection$OpenEntry[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "CNO"], 
       y = MeA_group_projection$OpenEntry[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "CNO"])
```

#### NAc {.tabset}

##### ANOVA

```{r 19-NAc_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "OpenEntry")
```

##### Pairwise comparisons

```{r 20-NAc_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "OpenEntry")
```

##### T-test each

```{r 21-NAc_ttest_openentry, message = FALSE, warning = FALSE}
# SAL
t.test(x = NAc_group_projection$OpenEntry[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "SAL"], 
       y = NAc_group_projection$OpenEntry[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "SAL"])

# CNO
t.test(x = NAc_group_projection$OpenEntry[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "CNO"], 
       y = NAc_group_projection$OpenEntry[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "CNO"])
```

### Plots {.tabset}

#### MeA

```{r 22-MeA_openarm_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(MeA_group_projection, "Open Arm Entries", 
            c(control_color, mea_color), proj_entry_axes_silence, "white")
```

#### NAc

```{r 23-NAc_openarm_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(NAc_group_projection, "Open Arm Entries", 
            c(control_color, nac_color), proj_entry_axes_silence, "white")
```

# Distance-based metrics

### Summary statistics

```{r 24-all_distance_stats, message = FALSE, warning = FALSE}
projection_sal_array <- transform_epm_openentry(data_projection_sal, "full", "Distance", 1, 2400)

projection_cno_array <- transform_epm_openentry(data_projection_cno, "full", "Distance", 1, 2400)

distance_group_projection <- group_array(data_projection_sal, projection_sal_array, projection_cno_array, "Distance")
```

#### MeA

```{r 25-MeA_distance_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "Distance", baseline_Distance, treatment_Distance) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection$time) <- c("SAL", "CNO")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                  levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection$group) <- c("mCh", "Gi")

MeA_group_projection$Distance <- MeA_group_projection$Distance / 100

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(Distance, type = "mean_se")
```

#### NAc

```{r 26-NAc_distance_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "Distance", baseline_Distance, treatment_Distance) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection$time) <- c("SAL", "CNO")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                  levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection$group) <- c("mCh", "Gi")

NAc_group_projection$Distance <- NAc_group_projection$Distance / 100

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(Distance, type = "mean_se")
```

### Stats {.tabset}

#### MeA {.tabset}

##### ANOVA

```{r 27-MeA_distance_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "Distance")
```

##### Pairwise comparisons

```{r 28-MeA_distance_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "Distance")
```

##### T-test each

```{r 29-MeA_distance_centertimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = MeA_group_projection$Distance[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "SAL"], 
       y = MeA_group_projection$Distance[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "SAL"])

# CNO
t.test(x = MeA_group_projection$Distance[MeA_group_projection$group == "mCh" & 
                                              MeA_group_projection$time == "CNO"], 
       y = MeA_group_projection$Distance[MeA_group_projection$group == "Gi" & 
                                         MeA_group_projection$time == "CNO"])
```

#### NAc {.tabset}

##### ANOVA

```{r 30-NAc_distance_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "Distance")
```

##### Pairwise comparisons

```{r 31-NAc_distance_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "Distance")
```

##### T-test each

```{r 32-NAc_ttest_distance, message = FALSE, warning = FALSE}
# SAL
t.test(x = NAc_group_projection$Distance[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "SAL"], 
       y = NAc_group_projection$Distance[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "SAL"])

# CNO
t.test(x = NAc_group_projection$Distance[NAc_group_projection$group == "mCh" & 
                                              NAc_group_projection$time == "CNO"], 
       y = NAc_group_projection$Distance[NAc_group_projection$group == "Gi" & 
                                         NAc_group_projection$time == "CNO"])
```

### Plots {.tabset}

#### MeA

```{r 33-MeA_distance_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(MeA_group_projection, "Distance (m)", 
            c(control_color, mea_color), openfield_axes_dist_silence_epm, "white")
```

#### NAc

```{r 34-NAc_distance_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(NAc_group_projection, "Distance (m)", 
            c(control_color, nac_color), openfield_axes_dist_silence_epm, "white")
```

# Heatmaps {.tabset}

```{r 35-get_heatmaps, message = FALSE, warning = FALSE}
sal_heatmap <- get_heatmap_epm(data_projection_sal, "full")
cno_heatmap <- get_heatmap_epm(data_projection_cno, "full")
```

## MeA {.tabset}

### mCh {.tabset}

#### SAL

```{r 36-MeA_mCh_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`MeA-control`)
```

#### CNO

```{r 37-MeA_mCh_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`MeA-control`)
```

### Gi {.tabset}

#### SAL

```{r 38-MeA_Gi_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`MeA-Gi`)
```

#### CNO

```{r 39-MeA_Gi_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`MeA-Gi`)
```

## NAc {.tabset}

### mCh {.tabset}

#### SAL

```{r 40-NAc_mCh_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`NAc-control`)
```

#### CNO

```{r 41-NAc_mCh_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`NAc-control`)
```

### Gi {.tabset}

#### SAL

```{r 42-NAc_Gi_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`NAc-Gi`)
```

#### CNO

```{r 43-NAc_Gi_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`NAc-Gi`)
```

## Scale bars {.tabset}

### Horizontal

```{r 44-scale_bar_horizontal, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(sal_heatmap$`MeA-control`, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```

### Vertical

```{r 45-scale_bar_vertical, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(sal_heatmap$`MeA-control`, "vertical")

grid.newpage()
grid.draw(plot_legend)
```
