---
author: "James Howe"
params:
  dataset: "genes"
  path: "data/behavior/genes_silence_epm/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
gene_id <- params$dataset
gene_path <- params$path
start_min <- params$start_min
end_min <- params$end_min

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

gene_groups <- unlist(strsplit(Sys.glob(paste0(gene_path, "SAL/*")),
                                        paste0(gene_path, "SAL/")))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_gene_sal <- vector(mode = "list", length = 4)
data_gene_sal <- lapply(gene_groups, 
                        function(x) lapply(Sys.glob(paste0(gene_path, "SAL/", x, "/*")),
                                           function(y) process_series_epm(y, "silence")))

data_gene_cno <- vector(mode = "list", length = 4)
data_gene_cno <- lapply(gene_groups, 
                        function(x) lapply(Sys.glob(paste0(gene_path, "CNO/", x, "/*")),
                                           function(y) process_series_epm(y, "silence")))

# add names to each
names(data_gene_sal) <- Sys.glob(paste0(gene_path, "SAL/", "*"))
names(data_gene_sal) <- unlist(strsplit(names(data_gene_sal), 
                                                  paste0(gene_path, "SAL/")))[c(FALSE, TRUE)]

names(data_gene_cno) <- Sys.glob(paste0(gene_path, "CNO/", "*"))
names(data_gene_cno) <- unlist(strsplit(names(data_gene_cno), 
                                                  paste0(gene_path, "CNO/")))[c(FALSE, TRUE)]

for (i in 1:length(gene_groups)){
  data_gene_sal <- add_custom_names(data_gene_sal, paste0(gene_path, "SAL/"), 
                                              gene_groups[i], gene_labels[i])
  data_gene_cno <- add_custom_names(data_gene_cno, paste0(gene_path, "CNO/"), 
                                              gene_groups[i], gene_labels[i])
}

data_gene_sal <- list(data_gene_sal$`VGlut1-control`, data_gene_sal$`VGlut1-Gi`, 
                                data_gene_sal$`VGlut2-control`, data_gene_sal$`VGlut2-Gi`)
names(data_gene_sal) <- c("VGlut1-control", "VGlut1-Gi", "VGlut2-control", "VGlut2-Gi")

data_gene_cno <- list(data_gene_cno$`VGlut1-control`, data_gene_cno$`VGlut1-Gi`, 
                                data_gene_cno$`VGlut2-control`, data_gene_cno$`VGlut2-Gi`)
names(data_gene_cno) <- c("VGlut1-control", "VGlut1-Gi", "VGlut2-control", "VGlut2-Gi")
```

# Open Time-based metrics

### Summary statistics

```{r 2-all_centertime_stats, message = FALSE, warning = FALSE}
gene_sal_array <- transform_epm_opentime(data_gene_sal, "full", "Region", 1, 2400)

gene_cno_array <- transform_epm_opentime(data_gene_cno, "full", "Region", 1, 2400)

opentime_group_gene <- group_array(data_gene_sal, gene_sal_array, gene_cno_array, "OpenTime")
```

#### VGlut1

```{r 3-VGlut1_opentime_stats, message = FALSE, warning = FALSE}
VGlut1_group_gene <- opentime_group_gene[opentime_group_gene$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "OpenTime", baseline_OpenTime, treatment_OpenTime) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene$time) <- c("SAL", "CNO")

VGlut1_group_gene$group <- factor(VGlut1_group_gene$group, 
                                  levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene$group) <- c("mCh", "Gi")

VGlut1_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

#### VGlut2

```{r 4-VGlut2_opentime_stats, message = FALSE, warning = FALSE}
VGlut2_group_gene <- opentime_group_gene[opentime_group_gene$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "OpenTime", baseline_OpenTime, treatment_OpenTime) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene$time) <- c("SAL", "CNO")

VGlut2_group_gene$group <- factor(VGlut2_group_gene$group, 
                                  levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene$group) <- c("mCh", "Gi")

VGlut2_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

### Stats {.tabset}

#### VGlut1 {.tabset}

##### ANOVA

```{r 5-VGlut1_open_anova, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_gene, "OpenTime")
```

##### Pairwise comparisons

```{r 6-VGlut1_open_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_gene, "OpenTime")
```

##### T-test each

```{r 7-VGlut1_ttest_opentimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut1_group_gene$OpenTime[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "SAL"], 
       y = VGlut1_group_gene$OpenTime[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut1_group_gene$OpenTime[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "CNO"], 
       y = VGlut1_group_gene$OpenTime[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "CNO"])
```

#### VGlut2 {.tabset}

##### ANOVA

```{r 8-VGlut2_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_gene, "OpenTime")
```

##### Pairwise comparisons

```{r 9-VGlut2_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_gene, "OpenTime")
```

##### T-test each

```{r 10-VGlut2_ttest_opentimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut2_group_gene$OpenTime[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "SAL"], 
       y = VGlut2_group_gene$OpenTime[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut2_group_gene$OpenTime[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "CNO"], 
       y = VGlut2_group_gene$OpenTime[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "CNO"])
```

### Plots {.tabset}

#### VGlut1

```{r 11-VGlut1_open_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut1_group_gene, "Proportion Time in Open Arms", 
            c(control_color, VGlut1_color), topo_corner_axes, "white")
```

#### VGlut2

```{r 12-VGlut2_open_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut2_group_gene, "Proportion Time in Open Arms", 
            c(control_color, VGlut2_color), topo_corner_axes, "white")
```

# Open Entry-based metrics

### Summary statistics

```{r 13-all_openentry_stats, message = FALSE, warning = FALSE}
gene_sal_array <- transform_epm_openentry(data_gene_sal, "full", "OpenEntry", 1, 2400)

gene_cno_array <- transform_epm_openentry(data_gene_cno, "full", "OpenEntry", 1, 2400)

openentry_group_gene <- group_array(data_gene_sal, gene_sal_array, gene_cno_array, "OpenEntry")
```

#### VGlut1

```{r 14-VGlut1_openentry_stats, message = FALSE, warning = FALSE}
VGlut1_group_gene <- openentry_group_gene[openentry_group_gene$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "OpenEntry", baseline_OpenEntry, treatment_OpenEntry) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene$time) <- c("SAL", "CNO")

VGlut1_group_gene$group <- factor(VGlut1_group_gene$group, 
                                  levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene$group) <- c("mCh", "Gi")

VGlut1_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(OpenEntry, type = "mean_se")
```

#### VGlut2

```{r 15-VGlut2_openentry_stats, message = FALSE, warning = FALSE}
VGlut2_group_gene <- openentry_group_gene[openentry_group_gene$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "OpenEntry", baseline_OpenEntry, treatment_OpenEntry) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene$time) <- c("SAL", "CNO")

VGlut2_group_gene$group <- factor(VGlut2_group_gene$group, 
                                  levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene$group) <- c("mCh", "Gi")

VGlut2_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(OpenEntry, type = "mean_se")
```

### Stats {.tabset}

#### VGlut1 {.tabset}

##### ANOVA

```{r 16-VGlut1_openentry_anova, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_gene, "OpenEntry")
```

##### Pairwise comparisons

```{r 17-VGlut1_openentry_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_gene, "OpenEntry")
```

##### T-test each

```{r 18-VGlut1_ttest_openentry, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut1_group_gene$OpenEntry[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "SAL"], 
       y = VGlut1_group_gene$OpenEntry[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut1_group_gene$OpenEntry[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "CNO"], 
       y = VGlut1_group_gene$OpenEntry[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "CNO"])
```

#### VGlut2 {.tabset}

##### ANOVA

```{r 19-VGlut2_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_gene, "OpenEntry")
```

##### Pairwise comparisons

```{r 20-VGlut2_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_gene, "OpenEntry")
```

##### T-test each

```{r 21-VGlut2_ttest_openentry, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut2_group_gene$OpenEntry[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "SAL"], 
       y = VGlut2_group_gene$OpenEntry[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut2_group_gene$OpenEntry[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "CNO"], 
       y = VGlut2_group_gene$OpenEntry[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "CNO"])
```

### Plots {.tabset}

#### VGlut1

```{r 22-VGlut1_Corner_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut1_group_gene, "Open Arm Entries", 
            c(control_color, VGlut1_color), epm_axes_entry_genes, "white")
```

#### VGlut2

```{r 23-VGlut2_Corner_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut2_group_gene, "Open Arm Entries", 
            c(control_color, VGlut2_color), epm_axes_entry_genes, "white")
```

# Distance-based metrics

### Summary statistics

```{r 24-all_distance_stats, message = FALSE, warning = FALSE}
gene_sal_array <- transform_epm_openentry(data_gene_sal, "full", "Distance", 1, 2400)

gene_cno_array <- transform_epm_openentry(data_gene_cno, "full", "Distance", 1, 2400)

distance_group_gene <- group_array(data_gene_sal, gene_sal_array, gene_cno_array, "Distance")
```

#### VGlut1

```{r 25-VGlut1_distance_stats, message = FALSE, warning = FALSE}
VGlut1_group_gene <- distance_group_gene[distance_group_gene$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "Distance", baseline_Distance, treatment_Distance) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene$time) <- c("SAL", "CNO")

VGlut1_group_gene$group <- factor(VGlut1_group_gene$group, 
                                  levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene$group) <- c("mCh", "Gi")

VGlut1_group_gene$Distance <- VGlut1_group_gene$Distance / 100

VGlut1_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(Distance, type = "mean_se")
```

#### VGlut2

```{r 26-VGlut2_distance_stats, message = FALSE, warning = FALSE}
VGlut2_group_gene <- distance_group_gene[distance_group_gene$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "Distance", baseline_Distance, treatment_Distance) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene$time) <- c("SAL", "CNO")

VGlut2_group_gene$group <- factor(VGlut2_group_gene$group, 
                                  levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene$group) <- c("mCh", "Gi")

VGlut2_group_gene$Distance <- VGlut2_group_gene$Distance / 100

VGlut2_group_gene %>%
  group_by(group, time) %>%
  get_summary_stats(Distance, type = "mean_se")
```

### Stats {.tabset}

#### VGlut1 {.tabset}

##### ANOVA

```{r 27-VGlut1_distance_anova, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_gene, "Distance")
```

##### Pairwise comparisons

```{r 28-VGlut1_distance_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_gene, "Distance")
```

##### T-test each

```{r 29-VGlut1_distance_centertimes2, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut1_group_gene$Distance[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "SAL"], 
       y = VGlut1_group_gene$Distance[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut1_group_gene$Distance[VGlut1_group_gene$group == "mCh" & 
                                              VGlut1_group_gene$time == "CNO"], 
       y = VGlut1_group_gene$Distance[VGlut1_group_gene$group == "Gi" & 
                                         VGlut1_group_gene$time == "CNO"])
```

#### VGlut2 {.tabset}

##### ANOVA

```{r 30-VGlut2_distance_anova_prepost, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_gene, "Distance")
```

##### Pairwise comparisons

```{r 31-VGlut2_distance_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_gene, "Distance")
```

##### T-test each

```{r 32-VGlut2_ttest_distance, message = FALSE, warning = FALSE}
# SAL
t.test(x = VGlut2_group_gene$Distance[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "SAL"], 
       y = VGlut2_group_gene$Distance[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "SAL"])

# CNO
t.test(x = VGlut2_group_gene$Distance[VGlut2_group_gene$group == "mCh" & 
                                              VGlut2_group_gene$time == "CNO"], 
       y = VGlut2_group_gene$Distance[VGlut2_group_gene$group == "Gi" & 
                                         VGlut2_group_gene$time == "CNO"])
```

### Plots {.tabset}

#### VGlut1

```{r 33-VGlut1_distance_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut1_group_gene, "Distance (m)", 
            c(control_color, VGlut1_color), openfield_axes_dist_silence_epm, "white")
```

#### VGlut2

```{r 34-VGlut2_distance_prepost, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width= 2.4}
bg_twogroup(VGlut2_group_gene, "Distance (m)", 
            c(control_color, VGlut2_color), openfield_axes_dist_silence_epm, "white")
```

# Heatmaps {.tabset}

```{r 35-get_heatmaps, message = FALSE, warning = FALSE}
sal_heatmap <- get_heatmap_epm(data_gene_sal, "full")
cno_heatmap <- get_heatmap_epm(data_gene_cno, "full")
```

## VGlut1 {.tabset}

### mCh {.tabset}

#### SAL

```{r 36-VGlut1_mCh_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`VGlut1-control`)
```

#### CNO

```{r 37-VGlut1_mCh_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`VGlut1-control`)
```

### Gi {.tabset}

#### SAL

```{r 38-VGlut1_Gi_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`VGlut1-Gi`)
```

#### CNO

```{r 39-VGlut1_Gi_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`VGlut1-Gi`)
```

## VGlut2 {.tabset}

### mCh {.tabset}

#### SAL

```{r 40-VGlut2_mCh_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`VGlut2-control`)
```

#### CNO

```{r 41-VGlut2_mCh_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`VGlut2-control`)
```

### Gi {.tabset}

#### SAL

```{r 42-VGlut2_Gi_sal_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(sal_heatmap$`VGlut2-Gi`)
```

#### CNO

```{r 43-VGlut2_Gi_cno_heatmap, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_heatmap_epm(cno_heatmap$`VGlut2-Gi`)
```

## Scale bars {.tabset}

### Horizontal

```{r 44-scale_bar_horizontal, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(sal_heatmap$`VGlut1-control`, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```

### Vertical

```{r 45-scale_bar_vertical, message = FALSE, warning = FALSE, fig.height = 3, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(sal_heatmap$`VGlut1-control`, "vertical")

grid.newpage()
grid.draw(plot_legend)
```
