---
author: "James Howe"
params:
  dataset: "Projections (EPM)"
  path: "data/behavior/projections_epm/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
projection_id <- params$dataset
projection_path <- params$path
start_min <- params$start_min
end_min <- params$end_min

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

projection_groups <- unlist(strsplit(Sys.glob(paste0(projection_path, "*")), projection_path))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
data_projection <- read_stim_data("epm", projection_groups, projection_path, projection_stim_labels)

data_projection <- list(data_projection$`MeA-control`, data_projection$`MeA-stim`, 
                           data_projection$`NAc-control`, data_projection$`NAc-stim`)
names(data_projection) <- c("MeA-control", "MeA-stim", "NAc-control", "NAc-stim")
```

# Time-based metrics {.tabset}

## All 3 {.tabset}

### Summary statistics {.tabset}

```{r 2-open_all3_stats, message = FALSE, warning = FALSE}
baseline_pre_array_projection <- transform_epm_opentime(data_projection, 
                                                        "baseline_pre", "Region", 1, 1200)
treatment_array_projection <- transform_epm_opentime(data_projection, 
                                                     "treatment", "Region", 1, 1200)
baseline_post_array_projection <- transform_epm_opentime(data_projection, 
                                                         "baseline_post", "Region", 1, 1200)

opentime_group_projection <- group_array_epm(data_projection, 
                                             baseline_pre_array_projection, 
                                             treatment_array_projection, 
                                             baseline_post_array_projection,
                                             "opentime")

opentime_mins <- transform_epm_opentime_bymin(data_projection, "Region")
```

#### NAc

```{r 3-NAc_opentime_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "OpenTime", 
         baseline_pre_opentime, treatment_opentime, baseline_post_opentime) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("POST", "PRE", "STIM")
NAc_group_projection$time <- factor(NAc_group_projection$time, levels = c("PRE", "STIM", "POST"))

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

#### MeA

```{r 4-MeA_opentime_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "OpenTime", 
         baseline_pre_opentime, treatment_opentime, baseline_post_opentime) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("POST", "PRE", "STIM")
MeA_group_projection$time <- factor(MeA_group_projection$time, levels = c("PRE", "STIM", "POST"))

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 5-NAc_open_anova, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 6-NAc_open_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "OpenTime")
```

##### T-test each

```{r 7-NAc_ttest_opentimes, message = FALSE, warning = FALSE}
# PRE
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "PRE"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "PRE"])

# STIM
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "STIM"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "STIM"])

# POST
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "POST"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "POST"])
```

#### MeA {.tabset}

##### ANOVA

```{r 8-MeA_open_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 9-MeA_open_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "OpenTime")
```

##### T-test each

```{r 10-MeA_ttest_opentimes, message = FALSE, warning = FALSE}
# PRE
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "PRE"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "PRE"])

# STIM
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "STIM"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "STIM"])

# POST
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "POST"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "POST"])

```

### Plots {.tabset}

#### MeA

```{r 11-MeA_open_time, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
#bg_epm_prepost(MeA_group_projection, epm_opentime_label, mea_color, proj_ot_axes, chr2_blue)
bg_epm_mins(opentime_mins[1:2], epm_opentime_label, mea_color, proj_ot_axes_min, chr2_blue)
```

#### NAc

```{r 12-NAc_open_time, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
#bg_epm_prepost(NAc_group_projection, epm_opentime_label, nac_color, proj_ot_axes, chr2_blue)
bg_epm_mins(opentime_mins[3:4], epm_opentime_label, nac_color, proj_ot_axes_min, chr2_blue)
```

## Pre-Post Combined {.tabset}

```{r 13-prepost_opentime_stats, message = FALSE, warning = FALSE}
opentime_group_projection[,3] <- (opentime_group_projection[,3] + opentime_group_projection[,5])/2 
opentime_group_projection <- opentime_group_projection[,1:4]

colnames(opentime_group_projection)[3] <- "baseline_opentime" 
```

### Summary statistics {.tabset}

#### NAc

```{r 14-NAc_opentime_stats_prepost, message = FALSE, warning = FALSE}
NAc_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "OpenTime", 
         baseline_opentime, treatment_opentime) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("OFF", "ON")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

#### MeA

```{r 15-MeA_opentime_stats_prepost, message = FALSE, warning = FALSE}
MeA_group_projection <- opentime_group_projection[opentime_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "OpenTime", 
         baseline_opentime, treatment_opentime) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("OFF", "ON")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(OpenTime, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 16-NAc_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 17-NAc_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "OpenTime")
```

##### T-test each

```{r 18-NAc_ttest_opentimes2, message = FALSE, warning = FALSE}
# OFF
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "OFF"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "OFF"])

# ON
t.test(x = NAc_group_projection$OpenTime[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "ON"], 
       y = NAc_group_projection$OpenTime[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "ON"])
```

#### MeA {.tabset}

##### ANOVA

```{r 19-MeA_open_anova_prepost, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "OpenTime")
```

##### Pairwise comparisons

```{r 20-MeA_open_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "OpenTime")
```

##### T-test each

```{r 21-MeA_ttest_opentimes2, message = FALSE, warning = FALSE}
# OFF
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "OFF"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "OFF"])

# ON
t.test(x = MeA_group_projection$OpenTime[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "ON"], 
       y = MeA_group_projection$OpenTime[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "ON"])
```

### Plots {.tabset}

#### MeA

```{r 22-MeA_open_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(MeA_group_projection, epm_opentime_label, mea_color, proj_ot_axes, chr2_blue)
```

#### NAc

```{r 23-NAc_open_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(NAc_group_projection, epm_opentime_label, nac_color, proj_ot_axes, chr2_blue)
```

# Entry-based metrics {.tabset}

## All 3 {.tabset}

### Summary statistics {.tabset}

```{r 24-entry_all3_stats, message = FALSE, warning = FALSE}
baseline_pre_array_projection <- transform_epm_openentry(data_projection, 
                                                        "baseline_pre", "OpenEntry", 1, 1200)
treatment_array_projection <- transform_epm_openentry(data_projection, 
                                                     "treatment", "OpenEntry", 1, 1200)
baseline_post_array_projection <- transform_epm_openentry(data_projection, 
                                                         "baseline_post", "OpenEntry", 1, 1200)

openentry_group_projection <- group_array_epm(data_projection, 
                                             baseline_pre_array_projection, 
                                             treatment_array_projection, 
                                             baseline_post_array_projection,
                                             "openentry")

openentry_mins <- transform_epm_openentry_bymin(data_projection, "OpenEntry")
```

#### NAc

```{r 25-NAc_openentry_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "openentry", 
         baseline_pre_openentry, treatment_openentry, baseline_post_openentry) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("POST", "PRE", "STIM")
NAc_group_projection$time <- factor(NAc_group_projection$time, levels = c("PRE", "STIM", "POST"))

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(openentry, type = "mean_se")
```

#### MeA

```{r 26-MeA_openentry_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "openentry", 
         baseline_pre_openentry, treatment_openentry, baseline_post_openentry) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("POST", "PRE", "STIM")
MeA_group_projection$time <- factor(MeA_group_projection$time, levels = c("PRE", "STIM", "POST"))

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(openentry, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 27-NAc_entry_anova, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "openentry")
```

##### Pairwise comparisons

```{r 28-NAc_entry_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "openentry")
```

##### T-test each

```{r 29-NAc_ttest_entry, message = FALSE, warning = FALSE}
# PRE
t.test(x = NAc_group_projection$openentry[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "PRE"], 
       y = NAc_group_projection$openentry[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "PRE"])

# STIM
t.test(x = NAc_group_projection$openentry[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "STIM"], 
       y = NAc_group_projection$openentry[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "STIM"])

# POST
t.test(x = NAc_group_projection$openentry[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "POST"], 
       y = NAc_group_projection$openentry[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "POST"])
```

#### MeA {.tabset}

##### ANOVA

```{r 30-MeA_entry_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "openentry")
```

##### Pairwise comparisons

```{r 31-MeA_entry_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "openentry")
```

##### T-test each

```{r 32-MeA_ttest_entry, message = FALSE, warning = FALSE}
# PRE
t.test(x = MeA_group_projection$openentry[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "PRE"], 
       y = MeA_group_projection$openentry[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "PRE"])

# STIM
t.test(x = MeA_group_projection$openentry[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "STIM"], 
       y = MeA_group_projection$openentry[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "STIM"])

# POST
t.test(x = MeA_group_projection$openentry[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "POST"], 
       y = MeA_group_projection$openentry[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "POST"])

```

### Plots {.tabset}

#### MeA

```{r 33-MeA_entry_time, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_epm_mins(openentry_mins[1:2], epm_entry_label, mea_color, proj_entry_axes_min, chr2_blue)
```

#### NAc

```{r 34-NAc_entry_time, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_epm_mins(openentry_mins[3:4], epm_entry_label, nac_color, proj_entry_axes_min, chr2_blue)
```

## Pre-Post Combined {.tabset}

```{r 35-prepost_entry_stats, message = FALSE, warning = FALSE}
openentry_group_projection[,3] <- (openentry_group_projection[,3] + openentry_group_projection[,5])/2 
openentry_group_projection <- openentry_group_projection[,1:4]

colnames(openentry_group_projection)[3] <- "baseline_openentry" 
```

### Summary statistics {.tabset}

#### NAc

```{r 36-NAc_entry_stats_prepost, message = FALSE, warning = FALSE}
NAc_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "openentry", 
         baseline_openentry, treatment_openentry) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("OFF", "ON")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(openentry, type = "mean_se")
```

#### MeA

```{r 37-MeA_entry_stats_prepost, message = FALSE, warning = FALSE}
MeA_group_projection <- openentry_group_projection[openentry_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "openentry", 
         baseline_openentry, treatment_openentry) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("OFF", "ON")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(openentry, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 38-NAc_entry_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "openentry")
```

##### Pairwise comparisons

```{r 17-NAc_entry_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "openentry")
```

##### T-test each

```{r 18-NAc_ttest_entry2, message = FALSE, warning = FALSE}
# OFF
t.test(x = NAc_group_projection$openentry[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "OFF"], 
       y = NAc_group_projection$openentry[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "OFF"])

# ON
t.test(x = NAc_group_projection$openentry[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "ON"], 
       y = NAc_group_projection$openentry[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "ON"])
```

#### MeA {.tabset}

##### ANOVA

```{r 39-MeA_entry_anova_prepost, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "openentry")
```

##### Pairwise comparisons

```{r 20-MeA_entry_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "openentry")
```

##### T-test each

```{r 40-MeA_ttest_entry2, message = FALSE, warning = FALSE}
# OFF
t.test(x = MeA_group_projection$openentry[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "OFF"], 
       y = MeA_group_projection$openentry[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "OFF"])

# ON
t.test(x = MeA_group_projection$openentry[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "ON"], 
       y = MeA_group_projection$openentry[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "ON"])
```

### Plots {.tabset}

#### MeA

```{r 41-MeA_entry_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(MeA_group_projection, epm_entry_label, mea_color, proj_entry_axes, chr2_blue)
```

#### NAc

```{r 42-NAc_entry_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(NAc_group_projection, epm_entry_label, nac_color, proj_entry_axes, chr2_blue)
```

# Distance-based metrics {.tabset}

## All 3 {.tabset}

### Summary statistics {.tabset}

```{r 43-distance_all3_stats, message = FALSE, warning = FALSE}
# open entry function also works for distance
baseline_pre_array_projection <- transform_epm_openentry(data_projection, 
                                                        "baseline_pre", "Distance", 1, 1200)
treatment_array_projection <- transform_epm_openentry(data_projection, 
                                                     "treatment", "Distance", 1, 1200)
baseline_post_array_projection <- transform_epm_openentry(data_projection, 
                                                         "baseline_post", "Distance", 1, 1200)

distance_group_projection <- group_array_epm(data_projection, 
                                             baseline_pre_array_projection, 
                                             treatment_array_projection, 
                                             baseline_post_array_projection,
                                             "distance")

distance_mins <- transform_epm_openentry_bymin(data_projection, "Distance")
distance_mins <- lapply(distance_mins, function(x) cbind.data.frame(x[, 1:2], x$OpenEntry / 100))
```

#### NAc

```{r 44-NAc_distance_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "distance", 
         baseline_pre_distance, treatment_distance, baseline_post_distance) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("POST", "PRE", "STIM")
NAc_group_projection$time <- factor(NAc_group_projection$time, levels = c("PRE", "STIM", "POST"))

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

# convert to meters
NAc_group_projection$distance <- NAc_group_projection$distance / 100

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(distance, type = "mean_se")
```

#### MeA

```{r 45-MeA_distance_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "distance", 
         baseline_pre_distance, treatment_distance, baseline_post_distance) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("POST", "PRE", "STIM")
MeA_group_projection$time <- factor(MeA_group_projection$time, levels = c("PRE", "STIM", "POST"))

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

# convert to meters
MeA_group_projection$distance <- MeA_group_projection$distance / 100

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(distance, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 46-NAc_distance_anova, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "distance")
```

##### Pairwise comparisons

```{r 47-NAc_distance_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "distance")
```

##### T-test each

```{r 48-NAc_ttest_distance, message = FALSE, warning = FALSE}
# PRE
t.test(x = NAc_group_projection$distance[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "PRE"], 
       y = NAc_group_projection$distance[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "PRE"])

# STIM
t.test(x = NAc_group_projection$distance[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "STIM"], 
       y = NAc_group_projection$distance[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "STIM"])

# POST
t.test(x = NAc_group_projection$distance[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "POST"], 
       y = NAc_group_projection$distance[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "POST"])
```

#### MeA {.tabset}

##### ANOVA

```{r 49-MeA_distance_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "distance")
```

##### Pairwise comparisons

```{r 50-MeA_distance_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "distance")
```

##### T-test each

```{r 51-MeA_ttest_distances, message = FALSE, warning = FALSE}
# PRE
t.test(x = MeA_group_projection$distance[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "PRE"], 
       y = MeA_group_projection$distance[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "PRE"])

# STIM
t.test(x = MeA_group_projection$distance[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "STIM"], 
       y = MeA_group_projection$distance[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "STIM"])

# POST
t.test(x = MeA_group_projection$distance[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "POST"], 
       y = MeA_group_projection$distance[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "POST"])

```

### Plots {.tabset}

#### MeA

```{r 52-MeA_distance_open, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_epm_mins(distance_mins[1:2], epm_dist_label, mea_color, proj_epm_dist_axes_min, chr2_blue)
```

#### NAc

```{r 53-NAc_distance_open, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_epm_mins(distance_mins[3:4], epm_dist_label, nac_color, proj_epm_dist_axes_min, chr2_blue)
```

## Pre-Post Combined {.tabset}

```{r 54-prepost_distance_stats, message = FALSE, warning = FALSE}
distance_group_projection[,3] <- (distance_group_projection[,3] + distance_group_projection[,5])/2 
distance_group_projection <- distance_group_projection[,1:4]

colnames(distance_group_projection)[3] <- "baseline_distance" 
```

### Summary statistics {.tabset}

#### NAc

```{r 55-NAc_distance_stats_prepost, message = FALSE, warning = FALSE}
NAc_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "distance", 
         baseline_distance, treatment_distance) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(NAc_group_projection$time) <- c("OFF", "ON")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection$distance <- NAc_group_projection$distance / 100

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(distance, type = "mean_se")
```

#### MeA

```{r 56-MeA_distance_stats_prepost, message = FALSE, warning = FALSE}
MeA_group_projection <- distance_group_projection[distance_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "distance", 
         baseline_distance, treatment_distance) %>%
  convert_as_factor(group, time)
# out of order due to alphabetization, then put in order
levels(MeA_group_projection$time) <- c("OFF", "ON")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection$distance <- MeA_group_projection$distance / 100

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(distance, type = "mean_se")
```

### Stats {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 57-NAc_distance_anova_prepost, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "distance")
```

##### Pairwise comparisons

```{r 58-NAc_distance_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "distance")
```

##### T-test each

```{r 59-NAc_ttest_distance2, message = FALSE, warning = FALSE}
# OFF
t.test(x = NAc_group_projection$distance[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "OFF"], 
       y = NAc_group_projection$distance[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "OFF"])

# ON
t.test(x = NAc_group_projection$distance[NAc_group_projection$group == "eYFP" & 
                                         NAc_group_projection$time == "ON"], 
       y = NAc_group_projection$distance[NAc_group_projection$group == "ChR2" & 
                                         NAc_group_projection$time == "ON"])
```

#### MeA {.tabset}

##### ANOVA

```{r 60-MeA_distance_anova_prepost, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "distance")
```

##### Pairwise comparisons

```{r 61-MeA_distance_pairwise_prepost, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "distance")
```

```{r 62-MeA_ttest_distance2, message = FALSE, warning = FALSE}
# OFF
t.test(x = MeA_group_projection$distance[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "OFF"], 
       y = MeA_group_projection$distance[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "OFF"])

# ON
t.test(x = MeA_group_projection$distance[MeA_group_projection$group == "eYFP" & 
                                         MeA_group_projection$time == "ON"], 
       y = MeA_group_projection$distance[MeA_group_projection$group == "ChR2" & 
                                         MeA_group_projection$time == "ON"])
```

### Plots {.tabset}

#### MeA

```{r 63-MeA_open_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(MeA_group_projection, epm_dist_label, mea_color, proj_epm_dist_axes, chr2_blue)
```

#### NAc

```{r 64-NAc_open_prepost, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.4, fig.width = 2.4}
bg_twogroup(NAc_group_projection, epm_dist_label, nac_color, proj_epm_dist_axes, chr2_blue)
```

# Heatmaps {.tabset}

```{r 65-get_heatmaps, message = FALSE, warning = FALSE}
full_heatmap <- get_heatmap_epm(data_projection, "full")
baseline_heatmap <- get_heatmap_epm(data_projection, "baseline_all")
treatment_heatmap <- get_heatmap_epm(data_projection, "treatment")

heatmap_diff <- get_heatmap_epm_diff(data_projection)
```

## MeA {.tabset}

### eYFP {.tabset}

#### Full

```{r 66-mea_eyfp_full_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(full_heatmap$`MeA-control`)
```

#### OFF

```{r 67-mea_eyfp_off_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(baseline_heatmap$`MeA-control`)
```

#### ON

```{r 68-mea_eyfp_on_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(treatment_heatmap$`MeA-control`)
```

#### Difference

```{r 69-mea_eyfp_diff_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm_diff(heatmap_diff$`MeA-control`)
```

### ChR2 {.tabset}

#### Full

```{r 70-mea_chr2_full_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(full_heatmap$`MeA-stim`)
```

#### OFF

```{r 71-mea_chr2_off_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(baseline_heatmap$`MeA-stim`)
```

#### ON

```{r 72-mea_chr2_on_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(treatment_heatmap$`MeA-stim`)
```

#### Difference

```{r 73-mea_chr2_diff_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm_diff(heatmap_diff$`MeA-stim`)
```

## NAc {.tabset}

### eYFP {.tabset}

#### Full

```{r 74-nac_eyfp_full_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(full_heatmap$`NAc-control`)
```

#### OFF

```{r 75-nac_eyfp_off_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(baseline_heatmap$`NAc-control`)
```

#### ON

```{r 76-nac_eyfp_on_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(treatment_heatmap$`NAc-control`)
```

#### Difference

```{r 77-nac_eyfp_diff_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm_diff(heatmap_diff$`NAc-control`)
```

### ChR2 {.tabset}

#### Full

```{r 78-nac_chr2_full_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(full_heatmap$`NAc-stim`)
```

#### OFF

```{r 79-nac_chr2_off_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(baseline_heatmap$`NAc-stim`)
```

#### ON

```{r 80-nac_chr2_on_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm(treatment_heatmap$`NAc-stim`)
```

#### Difference

```{r 81-nac_chr2_diff_heatmap, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 2.4}
plot_heatmap_epm_diff(heatmap_diff$`NAc-stim`)
```

## Scale bars {.tabset}

### Absolute {.tabset}

#### Horizontal

```{r 82-scale_bar_horizontal, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(treatment_heatmap$`NAc-stim`, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```

#### Vertical

```{r 83-scale_bar_vertical, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend(treatment_heatmap$`NAc-stim`, "vertical")

grid.newpage()
grid.draw(plot_legend)
```

### Relative {.tabset}

#### Horizontal

```{r 84-scale_bar_horizontal_diff, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend_diff(heatmap_diff$`NAc-stim`, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```

#### Vertical

```{r 85-scale_bar_vertical_diff, message = FALSE, warning = FALSE, fig.height = 2.4, fig.width = 3}
plot_legend <- plot_heatmap_epm_legend_diff(heatmap_diff$`NAc-stim`, "vertical")

grid.newpage()
grid.draw(plot_legend)
```

### Legends {.tabset}

#### Vertical {.tabset}

##### MeA {.tabset}

```{r 86-vertical_legend_MeA, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width = 1.8}
plot_legend <- points_legend(MeA_group_projection, epm_entry_label, mea_color, proj_entry_axes, chr2_blue, "vertical")

grid.newpage()
grid.draw(plot_legend)
```

##### NAc {.tabset}

```{r 87-vertical_legend_NAc, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width = 1.8}
plot_legend <- points_legend(NAc_group_projection, epm_entry_label, nac_color, proj_entry_axes, chr2_blue, "vertical")

grid.newpage()
grid.draw(plot_legend)
```

#### Horizontal {.tabset}

##### MeA {.tabset}

```{r 88-horizontal_legend_MeA, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width = 1.8}
plot_legend <- points_legend(MeA_group_projection, epm_entry_label, mea_color, proj_entry_axes, chr2_blue, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```

##### NAc {.tabset}

```{r 89-horizontal_legend_NAc, message = FALSE, warning = FALSE, dev = "pdf", fig.height = 2.4, fig.width = 1.8}
plot_legend <- points_legend(NAc_group_projection, epm_entry_label, nac_color, proj_entry_axes, chr2_blue, "horizontal")

grid.newpage()
grid.draw(plot_legend)
```
