---
author: "James Howe"
params:
  start_min: 12
  end_min: 24
  dataset: "genes_silence"
  path: "data/behavior/genes_silence/"
title: "Behavioral analysis: `r params$dataset` (2PE)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
gene_id <- params$dataset
gene_path <- params$path
start_min <- params$start_min
end_min <- params$end_min

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

gene_groups_2PE <- unlist(strsplit(Sys.glob(paste0(gene_path, "2PE/SAL/*")),
                                         paste0(gene_path, "2PE/SAL/")))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_gene_2PE_sal <- vector(mode = "list", length = 4)
data_gene_2PE_sal <- lapply(gene_groups_2PE, 
                                  function(x) lapply(Sys.glob(paste0(gene_path, "2PE/SAL/", x, "/*")),
                                                     process_series))

data_gene_2PE_cno <- vector(mode = "list", length = 4)
data_gene_2PE_cno <- lapply(gene_groups_2PE, 
                                  function(x) lapply(Sys.glob(paste0(gene_path, "2PE/CNO/", x, "/*")),
                                                     process_series))

# add names to each
names(data_gene_2PE_sal) <- Sys.glob(paste0(gene_path, "2PE/SAL/", "*"))
names(data_gene_2PE_sal) <- unlist(strsplit(names(data_gene_2PE_sal), 
                                                  paste0(gene_path, "2PE/SAL/")))[c(FALSE, TRUE)]

names(data_gene_2PE_cno) <- Sys.glob(paste0(gene_path, "2PE/CNO/", "*"))
names(data_gene_2PE_cno) <- unlist(strsplit(names(data_gene_2PE_cno), 
                                                  paste0(gene_path, "2PE/CNO/")))[c(FALSE, TRUE)]

for (i in 1:length(gene_groups_2PE)){
  data_gene_2PE_sal <- add_custom_names(data_gene_2PE_sal, paste0(gene_path, "2PE/SAL/"), 
                                              gene_groups_2PE[i], gene_labels_2PE[i])
  data_gene_2PE_cno <- add_custom_names(data_gene_2PE_cno, paste0(gene_path, "2PE/CNO/"), 
                                              gene_groups_2PE[i], gene_labels_2PE[i])
}

data_gene_2PE_sal <- list(data_gene_2PE_sal$`VGlut1-control`, data_gene_2PE_sal$`VGlut1-Gi`, 
                                data_gene_2PE_sal$`VGlut2-control`, data_gene_2PE_sal$`VGlut2-Gi`)
names(data_gene_2PE_sal) <- c("VGlut1-control", "VGlut1-Gi", "VGlut2-control", "VGlut2-Gi")

data_gene_2PE_cno <- list(data_gene_2PE_cno$`VGlut1-control`, data_gene_2PE_cno$`VGlut1-Gi`, 
                                data_gene_2PE_cno$`VGlut2-control`, data_gene_2PE_cno$`VGlut2-Gi`)
names(data_gene_2PE_cno) <- c("VGlut1-control", "VGlut1-Gi", "VGlut2-control", "VGlut2-Gi")
```

# Performance Index metrics

## Repeated Measures {.tabset}

### Summary statistics {.tabset}

```{r 2-pi_stats, message = FALSE, warning = FALSE}
#saline
baseline_array_gene_2PE_sal <- transform_pi(data_gene_2PE_sal, "baseline", "Quadrant", 1, 2399)
treatment_array_gene_2PE_sal <- transform_pi(data_gene_2PE_sal, "treatment", "Quadrant", 1, 2880)

pi_group_gene_2PE_sal <- group_array(data_gene_2PE_sal, 
                                           baseline_array_gene_2PE_sal, 
                                           treatment_array_gene_2PE_sal, "pi")

# cno
baseline_array_gene_2PE_cno <- transform_pi(data_gene_2PE_cno, "baseline", "Quadrant", 1, 2399)
treatment_array_gene_2PE_cno <- transform_pi(data_gene_2PE_cno, "treatment", "Quadrant", 1, 2880)

pi_group_gene_2PE_cno <- group_array(data_gene_2PE_cno, 
                                           baseline_array_gene_2PE_cno, 
                                           treatment_array_gene_2PE_cno, "pi")
```

#### VGlut1 {.tabset}

##### SAL

```{r 3-VGlut1_pi_stats_2PE_sal, message = FALSE, warning = FALSE}
VGlut1_group_gene_2PE_sal <- pi_group_gene_2PE_sal[pi_group_gene_2PE_sal$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene_2PE_sal$time) <- c("Air", "2PE")

VGlut1_group_gene_2PE_sal$group <- factor(VGlut1_group_gene_2PE_sal$group, 
                                   levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene_2PE_sal$group) <- c("mCh", "Gi")

VGlut1_group_gene_2PE_sal %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

##### CNO

```{r 4-VGlut1_pi_stats_2PE_cno, message = FALSE, warning = FALSE}
VGlut1_group_gene_2PE_cno <- pi_group_gene_2PE_cno[pi_group_gene_2PE_cno$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene_2PE_cno$time) <- c("Air", "2PE")

VGlut1_group_gene_2PE_cno$group <- factor(VGlut1_group_gene_2PE_cno$group, 
                                   levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene_2PE_cno$group) <- c("mCh", "Gi")

VGlut1_group_gene_2PE_cno %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### VGlut2 {.tabset}

##### SAL

```{r 5-VGlut2_pi_stats_2PE_sal, message = FALSE, warning = FALSE}
VGlut2_group_gene_2PE_sal <- pi_group_gene_2PE_sal[pi_group_gene_2PE_sal$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene_2PE_sal$time) <- c("Air", "2PE")

VGlut2_group_gene_2PE_sal$group <- factor(VGlut2_group_gene_2PE_sal$group, 
                                             levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene_2PE_sal$group) <- c("mCh", "Gi")

VGlut2_group_gene_2PE_sal %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

##### CNO

```{r 6-VGlut2_pi_stats_2PE_cno, message = FALSE, warning = FALSE}
VGlut2_group_gene_2PE_cno <- pi_group_gene_2PE_cno[pi_group_gene_2PE_cno$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene_2PE_cno$time) <- c("Air", "2PE")

VGlut2_group_gene_2PE_cno$group <- factor(VGlut2_group_gene_2PE_cno$group, 
                                             levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene_2PE_cno$group) <- c("mCh", "Gi")

VGlut2_group_gene_2PE_cno %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

## Difference {.tabset}

### Summary statistics

#### VGlut1

```{r 7-VGlut1_pi_diff_stats, message = FALSE, warning = FALSE}
VGlut1_group_diffs_2PE_sal <- cbind.data.frame(VGlut1_group_gene_2PE_sal$id[1:                                                                             (length(rownames(VGlut1_group_gene_2PE_sal))/2)],
                                        VGlut1_group_gene_2PE_sal$group[1:                                                                          (length(rownames(VGlut1_group_gene_2PE_sal))/2)],
                                    rep("SAL", times = length(rownames(VGlut1_group_gene_2PE_sal))/2),
                               VGlut1_group_gene_2PE_sal$PI[(length(rownames(VGlut1_group_gene_2PE_sal))/2)+1:
                                                               (length(rownames(VGlut1_group_gene_2PE_sal))/2)] -
                                          VGlut1_group_gene_2PE_sal$PI[1:                                                                         (length(rownames(VGlut1_group_gene_2PE_sal))/2)])
colnames(VGlut1_group_diffs_2PE_sal) <- c("id", "group", "time", "PI_diff")

VGlut1_group_diffs_2PE_cno <- cbind.data.frame(VGlut1_group_gene_2PE_cno$id[1:                                                                             (length(rownames(VGlut1_group_gene_2PE_cno))/2)],
                                        VGlut1_group_gene_2PE_cno$group[1:                                                                          (length(rownames(VGlut1_group_gene_2PE_cno))/2)],
                                        rep("CNO", times = length(rownames(VGlut1_group_gene_2PE_cno))/2),
                               VGlut1_group_gene_2PE_cno$PI[(length(rownames(VGlut1_group_gene_2PE_cno))/2)+1:
                                                               (length(rownames(VGlut1_group_gene_2PE_cno))/2)] -
                                          VGlut1_group_gene_2PE_cno$PI[1:                                                                         (length(rownames(VGlut1_group_gene_2PE_cno))/2)])
colnames(VGlut1_group_diffs_2PE_cno) <- c("id", "group", "time", "PI_diff")

VGlut1_group_diffs_2PE <- rbind.data.frame(VGlut1_group_diffs_2PE_sal, VGlut1_group_diffs_2PE_cno)

VGlut1_group_diffs_2PE$time <- factor(VGlut1_group_diffs_2PE$time, 
                                        levels = c("SAL", "CNO"))

VGlut1_group_diffs_2PE %>%
  group_by(group, time) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

#### VGlut2

```{r 8-VGlut2_pi_diff_stats, message = FALSE, warning = FALSE}
VGlut2_group_diffs_2PE_sal <- cbind.data.frame(VGlut2_group_gene_2PE_sal$id[1:                                                                             (length(rownames(VGlut2_group_gene_2PE_sal))/2)],
                                        VGlut2_group_gene_2PE_sal$group[1:                                                                          (length(rownames(VGlut2_group_gene_2PE_sal))/2)],
                                    rep("SAL", times = length(rownames(VGlut2_group_gene_2PE_sal))/2),
                               VGlut2_group_gene_2PE_sal$PI[(length(rownames(VGlut2_group_gene_2PE_sal))/2)+1:
                                                               (length(rownames(VGlut2_group_gene_2PE_sal))/2)] -
                                          VGlut2_group_gene_2PE_sal$PI[1:                                                                         (length(rownames(VGlut2_group_gene_2PE_sal))/2)])
colnames(VGlut2_group_diffs_2PE_sal) <- c("id", "group", "time", "PI_diff")

VGlut2_group_diffs_2PE_cno <- cbind.data.frame(VGlut2_group_gene_2PE_cno$id[1:                                                                             (length(rownames(VGlut2_group_gene_2PE_cno))/2)],
                                        VGlut2_group_gene_2PE_cno$group[1:                                                                          (length(rownames(VGlut2_group_gene_2PE_cno))/2)],
                                        rep("CNO", times = length(rownames(VGlut2_group_gene_2PE_cno))/2),
                               VGlut2_group_gene_2PE_cno$PI[(length(rownames(VGlut2_group_gene_2PE_cno))/2)+1:
                                                               (length(rownames(VGlut2_group_gene_2PE_cno))/2)] -
                                          VGlut2_group_gene_2PE_cno$PI[1:                                                                         (length(rownames(VGlut2_group_gene_2PE_cno))/2)])
colnames(VGlut2_group_diffs_2PE_cno) <- c("id", "group", "time", "PI_diff")

VGlut2_group_diffs_2PE <- rbind.data.frame(VGlut2_group_diffs_2PE_sal, VGlut2_group_diffs_2PE_cno)

VGlut2_group_diffs_2PE$time <- factor(VGlut2_group_diffs_2PE$time, 
                                        levels = c("SAL", "CNO"))

VGlut2_group_diffs_2PE %>%
  group_by(group, time) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### Two-way repeated-Measures ANOVA {.tabset}

#### VGlut1 {.tabset}

##### ANOVA

```{r 9-VGlut1_pi_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_diffs_2PE, "PI_diff")
```

##### Pairwise comparisons

```{r 10-VGlut1_pi_diff_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_diffs_2PE, "PI_diff")
```

#### VGlut2 {.tabset}

##### ANOVA

```{r 11-VGlut2_pi_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_diffs_2PE, "PI_diff")
```

##### Pairwise comparisons

```{r 12-VGlut2_pi_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_diffs_2PE, "PI_diff")
```

### Plots {.tabset}

#### VGlut1

```{r 13-VGlut1_pi_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup(VGlut1_group_diffs_2PE, diff_pi_label_silence, VGlut1_color, pi_axes_2PE_genes, "white")
```

#### VGlut2

```{r 14-VGlut2_pi_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup(VGlut2_group_diffs_2PE, diff_pi_label_silence, VGlut2_color, pi_axes_2PE_genes, "white")
```

## Difference in Differences {.tabset}

### VGlut1 {.tabset}

```{r 15-VGlut1_pi_diff2x_2PE, message = FALSE, warning = FALSE}
VGlut1_group_diffs2x_2PE <- cbind.data.frame(VGlut1_group_diffs_2PE$id[1:                                                                             (length(rownames(VGlut1_group_diffs_2PE))/2)],
                                        VGlut1_group_diffs_2PE$group[1:                                                                          (length(rownames(VGlut1_group_diffs_2PE))/2)],
                              VGlut1_group_diffs_2PE$PI_diff[(length(rownames(VGlut1_group_diffs_2PE))/2)+1:
                                                               (length(rownames(VGlut1_group_diffs_2PE))/2)] -
                                          VGlut1_group_diffs_2PE$PI_diff[1:                                                                         (length(rownames(VGlut1_group_diffs_2PE))/2)])

colnames(VGlut1_group_diffs2x_2PE) <- c("id", "group", "PI_diff")

VGlut1_group_diffs2x_2PE %>%
  group_by(group) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### VGlut2

```{r 16-VGlut2_pi_diff2x_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 4, fig.width = 2}
VGlut2_group_diffs2x_2PE <- cbind.data.frame(VGlut2_group_diffs_2PE$id[1:                                                                             (length(rownames(VGlut2_group_diffs_2PE))/2)],
                                        VGlut2_group_diffs_2PE$group[1:                                                                          (length(rownames(VGlut2_group_diffs_2PE))/2)],
                              VGlut2_group_diffs_2PE$PI_diff[(length(rownames(VGlut2_group_diffs_2PE))/2)+1:
                                                               (length(rownames(VGlut2_group_diffs_2PE))/2)] -
                                          VGlut2_group_diffs_2PE$PI_diff[1:                                                                         (length(rownames(VGlut2_group_diffs_2PE))/2)])

colnames(VGlut2_group_diffs2x_2PE) <- c("id", "group", "PI_diff")

VGlut2_group_diffs2x_2PE %>%
  group_by(group) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### T-tests {.tabset}

#### VGlut1

```{r 17-VGlut1_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut1_group_diffs2x_2PE$PI_diff[VGlut1_group_diffs2x_2PE$group %in% "Gi"], 
       y = VGlut1_group_diffs2x_2PE$PI_diff[VGlut1_group_diffs2x_2PE$group %in% "mCh"])
```

#### VGlut2

```{r 18-VGlut2_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut2_group_diffs2x_2PE$PI_diff[VGlut2_group_diffs2x_2PE$group %in% "Gi"], 
       y = VGlut2_group_diffs2x_2PE$PI_diff[VGlut2_group_diffs2x_2PE$group %in% "mCh"])
```

### Graphs {.tabset}

#### VGlut1

```{r 19-VGlut1_diff_graph_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(VGlut1_group_diffs2x_2PE, silence_diff_label, VGlut1_color, diff_pi_axes_2PE_genes, "white")
```

#### VGlut2

```{r 20-VGlut2_diff_graph_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(VGlut2_group_diffs2x_2PE, silence_diff_label, VGlut2_color, diff_pi_axes_2PE_genes, "white")
```

# Port Distance metrics

## Difference {.tabset}

### Summary statistics

```{r 21-pd_calculate, message = FALSE, warning = FALSE}
#saline
baseline_array_gene_2PE_sal_pd <- transform_pd(data_gene_2PE_sal, "baseline", "PortDistance", 1, 2399)
treatment_array_gene_2PE_sal_pd <- transform_pd(data_gene_2PE_sal, "treatment", "PortDistance", 1, 2880)

pd_group_gene_2PE_sal <- group_array(data_gene_2PE_sal, 
                                           baseline_array_gene_2PE_sal_pd, 
                                           treatment_array_gene_2PE_sal_pd, "pd")

# cno
baseline_array_gene_2PE_cno_pd <- transform_pd(data_gene_2PE_cno, "baseline", "PortDistance", 1, 2399)
treatment_array_gene_2PE_cno_pd <- transform_pd(data_gene_2PE_cno, "treatment", "PortDistance", 1, 2880)

pd_group_gene_2PE_cno <- group_array(data_gene_2PE_cno, 
                                           baseline_array_gene_2PE_cno_pd, 
                                           treatment_array_gene_2PE_cno_pd, "pd")
```

#### VGlut1

```{r 22-VGlut1_pd_diff_stats, message = FALSE, warning = FALSE}
# saline
VGlut1_group_gene_2PE_sal_pd <- pd_group_gene_2PE_sal[pd_group_gene_2PE_sal$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene_2PE_sal_pd$time) <- c("Air", "2PE")

VGlut1_group_gene_2PE_sal_pd$group <- factor(VGlut1_group_gene_2PE_sal_pd$group, 
                                   levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene_2PE_sal_pd$group) <- c("mCh", "Gi")

VGlut1_group_diffs_2PE_sal_pd <- cbind.data.frame(VGlut1_group_gene_2PE_sal_pd$id[1:                                                                             (length(rownames(VGlut1_group_gene_2PE_sal_pd))/2)],
                                        VGlut1_group_gene_2PE_sal_pd$group[1:                                                                          (length(rownames(VGlut1_group_gene_2PE_sal_pd))/2)],
                                    rep("SAL", times = length(rownames(VGlut1_group_gene_2PE_sal_pd))/2),
                               VGlut1_group_gene_2PE_sal_pd$PD[(length(rownames(VGlut1_group_gene_2PE_sal_pd))/2)+1:
                                                               (length(rownames(VGlut1_group_gene_2PE_sal_pd))/2)] -
                                          VGlut1_group_gene_2PE_sal_pd$PD[1:                                                                         (length(rownames(VGlut1_group_gene_2PE_sal_pd))/2)])
colnames(VGlut1_group_diffs_2PE_sal_pd) <- c("id", "group", "time", "PD_diff")

# CNO
VGlut1_group_gene_2PE_cno_pd <- pd_group_gene_2PE_cno[pd_group_gene_2PE_cno$group 
                                     %in% c("VGlut1 Gi", "VGlut1 mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_gene_2PE_cno_pd$time) <- c("Air", "2PE")

VGlut1_group_gene_2PE_cno_pd$group <- factor(VGlut1_group_gene_2PE_cno_pd$group, 
                                   levels = c("VGlut1 mCh", "VGlut1 Gi"))
levels(VGlut1_group_gene_2PE_cno_pd$group) <- c("mCh", "Gi")

VGlut1_group_diffs_2PE_cno_pd <- cbind.data.frame(VGlut1_group_gene_2PE_cno_pd$id[1:                                                                             (length(rownames(VGlut1_group_gene_2PE_cno_pd))/2)],
                                        VGlut1_group_gene_2PE_cno_pd$group[1:                                                                          (length(rownames(VGlut1_group_gene_2PE_cno_pd))/2)],
                                    rep("CNO", times = length(rownames(VGlut1_group_gene_2PE_cno_pd))/2),
                               VGlut1_group_gene_2PE_cno_pd$PD[(length(rownames(VGlut1_group_gene_2PE_cno_pd))/2)+1:
                                                               (length(rownames(VGlut1_group_gene_2PE_cno_pd))/2)] -
                                          VGlut1_group_gene_2PE_cno_pd$PD[1:                                                                         (length(rownames(VGlut1_group_gene_2PE_cno_pd))/2)])
colnames(VGlut1_group_diffs_2PE_cno_pd) <- c("id", "group", "time", "PD_diff")

VGlut1_group_diffs_2PE_pd <- rbind.data.frame(VGlut1_group_diffs_2PE_sal_pd, VGlut1_group_diffs_2PE_cno_pd)

VGlut1_group_diffs_2PE_pd$time <- factor(VGlut1_group_diffs_2PE_pd$time, 
                                        levels = c("SAL", "CNO"))

VGlut1_group_diffs_2PE_pd %>%
  group_by(group, time) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

#### VGlut2

```{r 23-VGlut2_pd_diff_stats, message = FALSE, warning = FALSE}
# saline
VGlut2_group_gene_2PE_sal_pd <- pd_group_gene_2PE_sal[pd_group_gene_2PE_sal$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene_2PE_sal_pd$time) <- c("Air", "2PE")

VGlut2_group_gene_2PE_sal_pd$group <- factor(VGlut2_group_gene_2PE_sal_pd$group, 
                                   levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene_2PE_sal_pd$group) <- c("mCh", "Gi")

VGlut2_group_diffs_2PE_sal_pd <- cbind.data.frame(VGlut2_group_gene_2PE_sal_pd$id[1:                                                                             (length(rownames(VGlut2_group_gene_2PE_sal_pd))/2)],
                                        VGlut2_group_gene_2PE_sal_pd$group[1:                                                                          (length(rownames(VGlut2_group_gene_2PE_sal_pd))/2)],
                                    rep("SAL", times = length(rownames(VGlut2_group_gene_2PE_sal_pd))/2),
                               VGlut2_group_gene_2PE_sal_pd$PD[(length(rownames(VGlut2_group_gene_2PE_sal_pd))/2)+1:
                                                               (length(rownames(VGlut2_group_gene_2PE_sal_pd))/2)] -
                                          VGlut2_group_gene_2PE_sal_pd$PD[1:                                                                         (length(rownames(VGlut2_group_gene_2PE_sal_pd))/2)])
colnames(VGlut2_group_diffs_2PE_sal_pd) <- c("id", "group", "time", "PD_diff")

# CNO
VGlut2_group_gene_2PE_cno_pd <- pd_group_gene_2PE_cno[pd_group_gene_2PE_cno$group 
                                     %in% c("VGlut2 Gi", "VGlut2 mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_gene_2PE_cno_pd$time) <- c("Air", "2PE")

VGlut2_group_gene_2PE_cno_pd$group <- factor(VGlut2_group_gene_2PE_cno_pd$group, 
                                   levels = c("VGlut2 mCh", "VGlut2 Gi"))
levels(VGlut2_group_gene_2PE_cno_pd$group) <- c("mCh", "Gi")

VGlut2_group_diffs_2PE_cno_pd <- cbind.data.frame(VGlut2_group_gene_2PE_cno_pd$id[1:                                                                             (length(rownames(VGlut2_group_gene_2PE_cno_pd))/2)],
                                        VGlut2_group_gene_2PE_cno_pd$group[1:                                                                          (length(rownames(VGlut2_group_gene_2PE_cno_pd))/2)],
                                    rep("CNO", times = length(rownames(VGlut2_group_gene_2PE_cno_pd))/2),
                               VGlut2_group_gene_2PE_cno_pd$PD[(length(rownames(VGlut2_group_gene_2PE_cno_pd))/2)+1:
                                                               (length(rownames(VGlut2_group_gene_2PE_cno_pd))/2)] -
                                          VGlut2_group_gene_2PE_cno_pd$PD[1:                                                                         (length(rownames(VGlut2_group_gene_2PE_cno_pd))/2)])
colnames(VGlut2_group_diffs_2PE_cno_pd) <- c("id", "group", "time", "PD_diff")

VGlut2_group_diffs_2PE_pd <- rbind.data.frame(VGlut2_group_diffs_2PE_sal_pd, VGlut2_group_diffs_2PE_cno_pd)

VGlut2_group_diffs_2PE_pd$time <- factor(VGlut2_group_diffs_2PE_pd$time, 
                                        levels = c("SAL", "CNO"))

VGlut2_group_diffs_2PE_pd %>%
  group_by(group, time) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### Two-way repeated-Measures ANOVA {.tabset}

#### VGlut1 {.tabset}

##### ANOVA

```{r 24-VGlut1_pd_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_diffs_2PE_pd, "PD_diff")
```

##### Pairwise comparisons

```{r 25-VGlut1_pd_diff_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_diffs_2PE_pd, "PD_diff")
```

#### VGlut2 {.tabset}

##### ANOVA

```{r 26-VGlut2_pd_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_diffs_2PE_pd, "PD_diff")
```

##### Pairwise comparisons

```{r 27-VGlut2_pd_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_diffs_2PE_pd, "PD_diff")
```

### Plots {.tabset}

#### VGlut1

```{r 28-VGlut1_pd_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup_nobar(VGlut1_group_diffs_2PE_pd, diff_pd_label_silence, VGlut1_color,
                  pd_axes_2PE_genes, "white", 0)
```

#### VGlut2

```{r 29-VGlut2_pd_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup_nobar(VGlut2_group_diffs_2PE_pd, diff_pd_label_silence, VGlut2_color,
                  pd_axes_2PE_genes, "white", 0)
```

## Difference in Differences {.tabset}

### VGlut1 {.tabset}

```{r 30-VGlut1_pd_diff2x_2PE, message = FALSE, warning = FALSE}
VGlut1_group_diffs2x_2PE_pd <- cbind.data.frame(VGlut1_group_diffs_2PE_pd$id[1:                                                                             (length(rownames(VGlut1_group_diffs_2PE_pd))/2)],
                                        VGlut1_group_diffs_2PE_pd$group[1:                                                                          (length(rownames(VGlut1_group_diffs_2PE_pd))/2)],
                              VGlut1_group_diffs_2PE_pd$PD_diff[(length(rownames(VGlut1_group_diffs_2PE_pd))/2)+1:
                                                               (length(rownames(VGlut1_group_diffs_2PE_pd))/2)] -
                                          VGlut1_group_diffs_2PE_pd$PD_diff[1:                                                                         (length(rownames(VGlut1_group_diffs_2PE_pd))/2)])

colnames(VGlut1_group_diffs2x_2PE_pd) <- c("id", "group", "PD_diff")

VGlut1_group_diffs2x_2PE_pd %>%
  group_by(group) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### VGlut2

```{r 31-VGlut2_pd_diff2x_2PE, message = FALSE, warning = FALSE, dev = 'pdf'}
VGlut2_group_diffs2x_2PE_pd <- cbind.data.frame(VGlut2_group_diffs_2PE_pd$id[1:                                                                             (length(rownames(VGlut2_group_diffs_2PE_pd))/2)],
                                        VGlut2_group_diffs_2PE_pd$group[1:                                                                          (length(rownames(VGlut2_group_diffs_2PE_pd))/2)],
                              VGlut2_group_diffs_2PE_pd$PD_diff[(length(rownames(VGlut2_group_diffs_2PE_pd))/2)+1:
                                                               (length(rownames(VGlut2_group_diffs_2PE_pd))/2)] -
                                          VGlut2_group_diffs_2PE_pd$PD_diff[1:                                                                         (length(rownames(VGlut2_group_diffs_2PE_pd))/2)])

colnames(VGlut2_group_diffs2x_2PE_pd) <- c("id", "group", "PD_diff")

VGlut2_group_diffs2x_2PE_pd %>%
  group_by(group) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### T-tests {.tabset}

#### VGlut1

```{r 32-VGlut1_pd_diff_ttest_2x, message = FALSE, warning = FALSE}
t.test(x = VGlut1_group_diffs2x_2PE_pd$PD_diff[VGlut1_group_diffs2x_2PE_pd$group %in% "Gi"], 
       y = VGlut1_group_diffs2x_2PE_pd$PD_diff[VGlut1_group_diffs2x_2PE_pd$group %in% "mCh"])
```

#### VGlut2

```{r 33-VGlut2_pd_diff_ttest_2x, message = FALSE, warning = FALSE}
t.test(x = VGlut2_group_diffs2x_2PE_pd$PD_diff[VGlut2_group_diffs2x_2PE_pd$group %in% "Gi"], 
       y = VGlut2_group_diffs2x_2PE_pd$PD_diff[VGlut2_group_diffs2x_2PE_pd$group %in% "mCh"])
```

### Graphs {.tabset}

#### VGlut1

```{r 34-VGlut1_diff_graph_2PE_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.2, fig.height = 3}
bg_diff(VGlut1_group_diffs2x_2PE_pd, "∆ CNO - SAL", VGlut1_color, pd_axes_2PE_diff, pe_colors)
```

#### VGlut2

```{r 35-VGlut2_diff_graph_2PE_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.2, fig.height = 3}
bg_diff(VGlut2_group_diffs2x_2PE_pd, "∆ CNO - SAL", VGlut2_color, pd_axes_2PE_diff, pe_colors)
```

# Heatmap {.tabset}

Generates a heatmap for each group. Sums all groups together at baseline and at treatment, and applies a gaussian smooth filter to both. It then subtracts the baseline from the treatment to identify the difference between treatment and baseline for all groups. 

## SAL {.tabset}

```{r 36-heatmap_generate_sal, message=FALSE, warning=FALSE}
heatmap_list_sal <- get_heatmap(data_gene_2PE_sal)
```

## VGlut1 mCh

```{r 37-heatmap_mea_mch_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`VGlut1-control`)
```

## VGlut1 Gi

```{r 38-heatmap_mea_gi_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`VGlut1-Gi`)
```

## VGlut2 mCh

```{r 39-heatmap_nac_mch_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`VGlut2-control`)
```

## VGlut2 Gi

```{r 40-heatmap_nac_gi_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`VGlut2-Gi`)
```

## CNO {.tabset}

```{r 41-heatmap_generate_cno, message=FALSE, warning=FALSE}
heatmap_list_cno <- get_heatmap(data_gene_2PE_cno)
```

## VGlut1 mCh

```{r 42-heatmap_mea_mch_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`VGlut1-control`)
```

## VGlut1 Gi

```{r 43-heatmap_mea_gi_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`VGlut1-Gi`)
```

## VGlut2 mCh

```{r 44-heatmap_nac_mch_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`VGlut2-control`)
```

## VGlut2 Gi

```{r 45-heatmap_nac_gi_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`VGlut2-Gi`)
```
