---
author: "James Howe"
params:
  start_min: 12
  end_min: 24
  dataset: "projections_silence"
  path: "data/behavior/projections_silence/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
projection_id <- params$dataset
projection_path <- params$path
start_min <- params$start_min
end_min <- params$end_min

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

projection_groups_2PE <- unlist(strsplit(Sys.glob(paste0(projection_path, "2PE/SAL/*")),
                                         paste0(projection_path, "2PE/SAL/")))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_projection_2PE_sal <- vector(mode = "list", length = 4)
data_projection_2PE_sal <- lapply(projection_groups_2PE, 
                                  function(x) lapply(Sys.glob(paste0(projection_path, "2PE/SAL/", x, "/*")),
                                                     process_series))

data_projection_2PE_cno <- vector(mode = "list", length = 4)
data_projection_2PE_cno <- lapply(projection_groups_2PE, 
                                  function(x) lapply(Sys.glob(paste0(projection_path, "2PE/CNO/", x, "/*")),
                                                     process_series))

# add names to each
names(data_projection_2PE_sal) <- Sys.glob(paste0(projection_path, "2PE/SAL/", "*"))
names(data_projection_2PE_sal) <- unlist(strsplit(names(data_projection_2PE_sal), 
                                                  paste0(projection_path, "2PE/SAL/")))[c(FALSE, TRUE)]

names(data_projection_2PE_cno) <- Sys.glob(paste0(projection_path, "2PE/CNO/", "*"))
names(data_projection_2PE_cno) <- unlist(strsplit(names(data_projection_2PE_cno), 
                                                  paste0(projection_path, "2PE/CNO/")))[c(FALSE, TRUE)]

for (i in 1:length(projection_groups_2PE)){
  data_projection_2PE_sal <- add_custom_names(data_projection_2PE_sal, paste0(projection_path, "2PE/SAL/"), 
                                              projection_groups_2PE[i], projection_labels_2PE[i])
  data_projection_2PE_cno <- add_custom_names(data_projection_2PE_cno, paste0(projection_path, "2PE/CNO/"), 
                                              projection_groups_2PE[i], projection_labels_2PE[i])
}

data_projection_2PE_sal <- list(data_projection_2PE_sal$`MeA-control`, data_projection_2PE_sal$`MeA-Gi`, 
                                data_projection_2PE_sal$`NAc-control`, data_projection_2PE_sal$`NAc-Gi`)
names(data_projection_2PE_sal) <- c("MeA-control", "MeA-Gi", "NAc-control", "NAc-Gi")

data_projection_2PE_cno <- list(data_projection_2PE_cno$`MeA-control`, data_projection_2PE_cno$`MeA-Gi`, 
                                data_projection_2PE_cno$`NAc-control`, data_projection_2PE_cno$`NAc-Gi`)
names(data_projection_2PE_cno) <- c("MeA-control", "MeA-Gi", "NAc-control", "NAc-Gi")
```

# Performance Index metrics

## Repeated Measures {.tabset}

### Summary statistics {.tabset}

```{r 2-pi_stats, message = FALSE, warning = FALSE}
#saline
baseline_array_projection_2PE_sal <- transform_pi(data_projection_2PE_sal, "baseline", "Quadrant", 1, 2400)
treatment_array_projection_2PE_sal <- transform_pi(data_projection_2PE_sal, "treatment", "Quadrant", 1, 2880)

pi_group_projection_2PE_sal <- group_array(data_projection_2PE_sal, 
                                           baseline_array_projection_2PE_sal, 
                                           treatment_array_projection_2PE_sal, "pi")

# cno
baseline_array_projection_2PE_cno <- transform_pi(data_projection_2PE_cno, "baseline", "Quadrant", 1, 2400)
treatment_array_projection_2PE_cno <- transform_pi(data_projection_2PE_cno, "treatment", "Quadrant", 1, 2880)

pi_group_projection_2PE_cno <- group_array(data_projection_2PE_cno, 
                                           baseline_array_projection_2PE_cno, 
                                           treatment_array_projection_2PE_cno, "pi")
```

#### NAc {.tabset}

##### SAL

```{r 3-NAc_pi_stats_2PE_sal, message = FALSE, warning = FALSE}
NAc_group_projection_2PE_sal <- pi_group_projection_2PE_sal[pi_group_projection_2PE_sal$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection_2PE_sal$time) <- c("Air", "2PE")

NAc_group_projection_2PE_sal$group <- factor(NAc_group_projection_2PE_sal$group, 
                                   levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection_2PE_sal$group) <- c("mCh", "Gi")

NAc_group_projection_2PE_sal %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

##### CNO

```{r 4-NAc_pi_stats_2PE_cno, message = FALSE, warning = FALSE}
NAc_group_projection_2PE_cno <- pi_group_projection_2PE_cno[pi_group_projection_2PE_cno$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection_2PE_cno$time) <- c("Air", "2PE")

NAc_group_projection_2PE_cno$group <- factor(NAc_group_projection_2PE_cno$group, 
                                   levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection_2PE_cno$group) <- c("mCh", "Gi")

NAc_group_projection_2PE_cno %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### MeA {.tabset}

##### SAL

```{r 5-MeA_pi_stats_2PE_sal, message = FALSE, warning = FALSE}
MeA_group_projection_2PE_sal <- pi_group_projection_2PE_sal[pi_group_projection_2PE_sal$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection_2PE_sal$time) <- c("Air", "2PE")

MeA_group_projection_2PE_sal$group <- factor(MeA_group_projection_2PE_sal$group, 
                                             levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection_2PE_sal$group) <- c("mCh", "Gi")

MeA_group_projection_2PE_sal %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

##### CNO

```{r 6-MeA_pi_stats_2PE_cno, message = FALSE, warning = FALSE}
MeA_group_projection_2PE_cno <- pi_group_projection_2PE_cno[pi_group_projection_2PE_cno$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection_2PE_cno$time) <- c("Air", "2PE")

MeA_group_projection_2PE_cno$group <- factor(MeA_group_projection_2PE_cno$group, 
                                             levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection_2PE_cno$group) <- c("mCh", "Gi")

MeA_group_projection_2PE_cno %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

## Difference {.tabset}

### Summary statistics

#### NAc

```{r 7-NAc_pi_diff_stats, message = FALSE, warning = FALSE}
NAc_group_diffs_2PE_sal <- cbind.data.frame(NAc_group_projection_2PE_sal$id[1:                                                                             (length(rownames(NAc_group_projection_2PE_sal))/2)],
                                        NAc_group_projection_2PE_sal$group[1:                                                                          (length(rownames(NAc_group_projection_2PE_sal))/2)],
                                    rep("SAL", times = length(rownames(NAc_group_projection_2PE_sal))/2),
                               NAc_group_projection_2PE_sal$PI[(length(rownames(NAc_group_projection_2PE_sal))/2)+1:
                                                               (length(rownames(NAc_group_projection_2PE_sal))/2)] -
                                          NAc_group_projection_2PE_sal$PI[1:                                                                         (length(rownames(NAc_group_projection_2PE_sal))/2)])
colnames(NAc_group_diffs_2PE_sal) <- c("id", "group", "time", "PI_diff")

NAc_group_diffs_2PE_cno <- cbind.data.frame(NAc_group_projection_2PE_cno$id[1:                                                                             (length(rownames(NAc_group_projection_2PE_cno))/2)],
                                        NAc_group_projection_2PE_cno$group[1:                                                                          (length(rownames(NAc_group_projection_2PE_cno))/2)],
                                        rep("CNO", times = length(rownames(NAc_group_projection_2PE_cno))/2),
                               NAc_group_projection_2PE_cno$PI[(length(rownames(NAc_group_projection_2PE_cno))/2)+1:
                                                               (length(rownames(NAc_group_projection_2PE_cno))/2)] -
                                          NAc_group_projection_2PE_cno$PI[1:                                                                         (length(rownames(NAc_group_projection_2PE_cno))/2)])
colnames(NAc_group_diffs_2PE_cno) <- c("id", "group", "time", "PI_diff")

NAc_group_diffs_2PE <- rbind.data.frame(NAc_group_diffs_2PE_sal, NAc_group_diffs_2PE_cno)

NAc_group_diffs_2PE$time <- factor(NAc_group_diffs_2PE$time, 
                                        levels = c("SAL", "CNO"))

NAc_group_diffs_2PE %>%
  group_by(group, time) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

#### MeA

```{r 8-MeA_pi_diff_stats, message = FALSE, warning = FALSE}
MeA_group_diffs_2PE_sal <- cbind.data.frame(MeA_group_projection_2PE_sal$id[1:                                                                             (length(rownames(MeA_group_projection_2PE_sal))/2)],
                                        MeA_group_projection_2PE_sal$group[1:                                                                          (length(rownames(MeA_group_projection_2PE_sal))/2)],
                                    rep("SAL", times = length(rownames(MeA_group_projection_2PE_sal))/2),
                               MeA_group_projection_2PE_sal$PI[(length(rownames(MeA_group_projection_2PE_sal))/2)+1:
                                                               (length(rownames(MeA_group_projection_2PE_sal))/2)] -
                                          MeA_group_projection_2PE_sal$PI[1:                                                                         (length(rownames(MeA_group_projection_2PE_sal))/2)])
colnames(MeA_group_diffs_2PE_sal) <- c("id", "group", "time", "PI_diff")

MeA_group_diffs_2PE_cno <- cbind.data.frame(MeA_group_projection_2PE_cno$id[1:                                                                             (length(rownames(MeA_group_projection_2PE_cno))/2)],
                                        MeA_group_projection_2PE_cno$group[1:                                                                          (length(rownames(MeA_group_projection_2PE_cno))/2)],
                                        rep("CNO", times = length(rownames(MeA_group_projection_2PE_cno))/2),
                               MeA_group_projection_2PE_cno$PI[(length(rownames(MeA_group_projection_2PE_cno))/2)+1:
                                                               (length(rownames(MeA_group_projection_2PE_cno))/2)] -
                                          MeA_group_projection_2PE_cno$PI[1:                                                                         (length(rownames(MeA_group_projection_2PE_cno))/2)])
colnames(MeA_group_diffs_2PE_cno) <- c("id", "group", "time", "PI_diff")

MeA_group_diffs_2PE <- rbind.data.frame(MeA_group_diffs_2PE_sal, MeA_group_diffs_2PE_cno)

MeA_group_diffs_2PE$time <- factor(MeA_group_diffs_2PE$time, 
                                        levels = c("SAL", "CNO"))

MeA_group_diffs_2PE %>%
  group_by(group, time) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 9-NAc_pi_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(NAc_group_diffs_2PE, "PI_diff")
```

##### Pairwise comparisons

```{r 10-NAc_pi_diff_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_diffs_2PE, "PI_diff")
```

#### MeA {.tabset}

##### ANOVA

```{r 11-MeA_pi_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(MeA_group_diffs_2PE, "PI_diff")
```

##### Pairwise comparisons

```{r 12-MeA_pi_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_diffs_2PE, "PI_diff")
```

### Plots {.tabset}

#### NAc

```{r 13-NAc_pi_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup(NAc_group_diffs_2PE, "Change in Performance Index", 
            c(control_color, nac_color), pi_axes_2PE, "white")
```

#### MeA

```{r 14-MeA_pi_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup(MeA_group_diffs_2PE, "Change in Performance Index", 
            c(control_color, mea_color), pi_axes_2PE, "white")
```

## Difference in Differences {.tabset}

### NAc {.tabset}

```{r 15-NAc_pi_diff2x_2PE, message = FALSE, warning = FALSE}
NAc_group_diffs2x_2PE <- cbind.data.frame(NAc_group_diffs_2PE$id[1:                                                                             (length(rownames(NAc_group_diffs_2PE))/2)],
                                        NAc_group_diffs_2PE$group[1:                                                                          (length(rownames(NAc_group_diffs_2PE))/2)],
                              NAc_group_diffs_2PE$PI_diff[(length(rownames(NAc_group_diffs_2PE))/2)+1:
                                                               (length(rownames(NAc_group_diffs_2PE))/2)] -
                                          NAc_group_diffs_2PE$PI_diff[1:                                                                         (length(rownames(NAc_group_diffs_2PE))/2)])

colnames(NAc_group_diffs2x_2PE) <- c("id", "group", "PI_diff")

NAc_group_diffs2x_2PE %>%
  group_by(group) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### MeA

```{r 16-MeA_pi_diff2x_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 4, fig.width = 2}
MeA_group_diffs2x_2PE <- cbind.data.frame(MeA_group_diffs_2PE$id[1:                                                                             (length(rownames(MeA_group_diffs_2PE))/2)],
                                        MeA_group_diffs_2PE$group[1:                                                                          (length(rownames(MeA_group_diffs_2PE))/2)],
                              MeA_group_diffs_2PE$PI_diff[(length(rownames(MeA_group_diffs_2PE))/2)+1:
                                                               (length(rownames(MeA_group_diffs_2PE))/2)] -
                                          MeA_group_diffs_2PE$PI_diff[1:                                                                         (length(rownames(MeA_group_diffs_2PE))/2)])

colnames(MeA_group_diffs2x_2PE) <- c("id", "group", "PI_diff")

MeA_group_diffs2x_2PE %>%
  group_by(group) %>%
  get_summary_stats(PI_diff, type = "mean_se")
```

### T-tests {.tabset}

#### NAc

```{r 17-nac_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = NAc_group_diffs2x_2PE$PI_diff[NAc_group_diffs2x_2PE$group %in% "Gi"], 
       y = NAc_group_diffs2x_2PE$PI_diff[NAc_group_diffs2x_2PE$group %in% "mCh"])
```

#### MeA

```{r 18-MeA_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = MeA_group_diffs2x_2PE$PI_diff[MeA_group_diffs2x_2PE$group %in% "Gi"], 
       y = MeA_group_diffs2x_2PE$PI_diff[MeA_group_diffs2x_2PE$group %in% "mCh"])
```

### Graphs {.tabset}

#### NAc

```{r 19-nac_diff_graph_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(NAc_group_diffs2x_2PE, "CNO - SAL", nac_color, diff_pi_axes_2PE, pe_colors)
```

#### MeA

```{r 20-mea_diff_graph_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(MeA_group_diffs2x_2PE, "CNO - SAL", mea_color, diff_pi_axes_2PE, pe_colors)
```

# Port Distance metrics

## Difference {.tabset}

### Summary statistics

```{r 21-pd_calculate, message = FALSE, warning = FALSE}
#saline
baseline_array_projection_2PE_sal_pd <- transform_pd(data_projection_2PE_sal, "baseline", "PortDistance", 1, 2400)
treatment_array_projection_2PE_sal_pd <- transform_pd(data_projection_2PE_sal, "treatment", "PortDistance", 1, 2880)

pd_group_projection_2PE_sal <- group_array(data_projection_2PE_sal, 
                                           baseline_array_projection_2PE_sal_pd, 
                                           treatment_array_projection_2PE_sal_pd, "pd")

# cno
baseline_array_projection_2PE_cno_pd <- transform_pd(data_projection_2PE_cno, "baseline", "PortDistance", 1, 2400)
treatment_array_projection_2PE_cno_pd <- transform_pd(data_projection_2PE_cno, "treatment", "PortDistance", 1, 2880)

pd_group_projection_2PE_cno <- group_array(data_projection_2PE_cno, 
                                           baseline_array_projection_2PE_cno_pd, 
                                           treatment_array_projection_2PE_cno_pd, "pd")
```

#### NAc

```{r 22-NAc_pd_diff_stats, message = FALSE, warning = FALSE}
# saline
NAc_group_projection_2PE_sal_pd <- pd_group_projection_2PE_sal[pd_group_projection_2PE_sal$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection_2PE_sal_pd$time) <- c("Air", "2PE")

NAc_group_projection_2PE_sal_pd$group <- factor(NAc_group_projection_2PE_sal_pd$group, 
                                   levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection_2PE_sal_pd$group) <- c("mCh", "Gi")

NAc_group_diffs_2PE_sal_pd <- cbind.data.frame(NAc_group_projection_2PE_sal_pd$id[1:                                                                             (length(rownames(NAc_group_projection_2PE_sal_pd))/2)],
                                        NAc_group_projection_2PE_sal_pd$group[1:                                                                          (length(rownames(NAc_group_projection_2PE_sal_pd))/2)],
                                    rep("SAL", times = length(rownames(NAc_group_projection_2PE_sal_pd))/2),
                               NAc_group_projection_2PE_sal_pd$PD[(length(rownames(NAc_group_projection_2PE_sal_pd))/2)+1:
                                                               (length(rownames(NAc_group_projection_2PE_sal_pd))/2)] -
                                          NAc_group_projection_2PE_sal_pd$PD[1:                                                                         (length(rownames(NAc_group_projection_2PE_sal_pd))/2)])
colnames(NAc_group_diffs_2PE_sal_pd) <- c("id", "group", "time", "PD_diff")

# CNO
NAc_group_projection_2PE_cno_pd <- pd_group_projection_2PE_cno[pd_group_projection_2PE_cno$group 
                                     %in% c("NAc Gi", "NAc mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection_2PE_cno_pd$time) <- c("Air", "2PE")

NAc_group_projection_2PE_cno_pd$group <- factor(NAc_group_projection_2PE_cno_pd$group, 
                                   levels = c("NAc mCh", "NAc Gi"))
levels(NAc_group_projection_2PE_cno_pd$group) <- c("mCh", "Gi")

NAc_group_diffs_2PE_cno_pd <- cbind.data.frame(NAc_group_projection_2PE_cno_pd$id[1:                                                                             (length(rownames(NAc_group_projection_2PE_cno_pd))/2)],
                                        NAc_group_projection_2PE_cno_pd$group[1:                                                                          (length(rownames(NAc_group_projection_2PE_cno_pd))/2)],
                                    rep("CNO", times = length(rownames(NAc_group_projection_2PE_cno_pd))/2),
                               NAc_group_projection_2PE_cno_pd$PD[(length(rownames(NAc_group_projection_2PE_cno_pd))/2)+1:
                                                               (length(rownames(NAc_group_projection_2PE_cno_pd))/2)] -
                                          NAc_group_projection_2PE_cno_pd$PD[1:                                                                         (length(rownames(NAc_group_projection_2PE_cno_pd))/2)])
colnames(NAc_group_diffs_2PE_cno_pd) <- c("id", "group", "time", "PD_diff")

NAc_group_diffs_2PE_pd <- rbind.data.frame(NAc_group_diffs_2PE_sal_pd, NAc_group_diffs_2PE_cno_pd)

NAc_group_diffs_2PE_pd$time <- factor(NAc_group_diffs_2PE_pd$time, 
                                        levels = c("SAL", "CNO"))

NAc_group_diffs_2PE_pd %>%
  group_by(group, time) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

#### MeA

```{r 23-MeA_pd_diff_stats, message = FALSE, warning = FALSE}
# saline
MeA_group_projection_2PE_sal_pd <- pd_group_projection_2PE_sal[pd_group_projection_2PE_sal$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection_2PE_sal_pd$time) <- c("Air", "2PE")

MeA_group_projection_2PE_sal_pd$group <- factor(MeA_group_projection_2PE_sal_pd$group, 
                                   levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection_2PE_sal_pd$group) <- c("mCh", "Gi")

MeA_group_diffs_2PE_sal_pd <- cbind.data.frame(MeA_group_projection_2PE_sal_pd$id[1:                                                                             (length(rownames(MeA_group_projection_2PE_sal_pd))/2)],
                                        MeA_group_projection_2PE_sal_pd$group[1:                                                                          (length(rownames(MeA_group_projection_2PE_sal_pd))/2)],
                                    rep("SAL", times = length(rownames(MeA_group_projection_2PE_sal_pd))/2),
                               MeA_group_projection_2PE_sal_pd$PD[(length(rownames(MeA_group_projection_2PE_sal_pd))/2)+1:
                                                               (length(rownames(MeA_group_projection_2PE_sal_pd))/2)] -
                                          MeA_group_projection_2PE_sal_pd$PD[1:                                                                         (length(rownames(MeA_group_projection_2PE_sal_pd))/2)])
colnames(MeA_group_diffs_2PE_sal_pd) <- c("id", "group", "time", "PD_diff")

# CNO
MeA_group_projection_2PE_cno_pd <- pd_group_projection_2PE_cno[pd_group_projection_2PE_cno$group 
                                     %in% c("MeA Gi", "MeA mCh"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection_2PE_cno_pd$time) <- c("Air", "2PE")

MeA_group_projection_2PE_cno_pd$group <- factor(MeA_group_projection_2PE_cno_pd$group, 
                                   levels = c("MeA mCh", "MeA Gi"))
levels(MeA_group_projection_2PE_cno_pd$group) <- c("mCh", "Gi")

MeA_group_diffs_2PE_cno_pd <- cbind.data.frame(MeA_group_projection_2PE_cno_pd$id[1:                                                                             (length(rownames(MeA_group_projection_2PE_cno_pd))/2)],
                                        MeA_group_projection_2PE_cno_pd$group[1:                                                                          (length(rownames(MeA_group_projection_2PE_cno_pd))/2)],
                                    rep("CNO", times = length(rownames(MeA_group_projection_2PE_cno_pd))/2),
                               MeA_group_projection_2PE_cno_pd$PD[(length(rownames(MeA_group_projection_2PE_cno_pd))/2)+1:
                                                               (length(rownames(MeA_group_projection_2PE_cno_pd))/2)] -
                                          MeA_group_projection_2PE_cno_pd$PD[1:                                                                         (length(rownames(MeA_group_projection_2PE_cno_pd))/2)])
colnames(MeA_group_diffs_2PE_cno_pd) <- c("id", "group", "time", "PD_diff")

MeA_group_diffs_2PE_pd <- rbind.data.frame(MeA_group_diffs_2PE_sal_pd, MeA_group_diffs_2PE_cno_pd)

MeA_group_diffs_2PE_pd$time <- factor(MeA_group_diffs_2PE_pd$time, 
                                        levels = c("SAL", "CNO"))

MeA_group_diffs_2PE_pd %>%
  group_by(group, time) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### NAc {.tabset}

##### ANOVA

```{r 24-NAc_pd_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(NAc_group_diffs_2PE_pd, "PD_diff")
```

##### Pairwise comparisons

```{r 25-NAc_pd_diff_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_diffs_2PE_pd, "PD_diff")
```

#### MeA {.tabset}

##### ANOVA

```{r 26-MeA_pd_diff_anova_2PE, message = FALSE, warning = FALSE}
display_anova(MeA_group_diffs_2PE_pd, "PD_diff")
```

##### Pairwise comparisons

```{r 27-MeA_pd_pairwise_2PE, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_diffs_2PE_pd, "PD_diff")
```

### Plots {.tabset}

#### NAc

```{r 28-NAc_pd_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup_nobar(NAc_group_diffs_2PE_pd, "Change in Mean Port Distance (cm)", 
                   c("dimgrey", nac_color), pd_axes_2PE, "white", 0)
```

#### MeA

```{r 29-MeA_pd_diff_2PE, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 2.8, fig.width = 2.4}
bg_twogroup_nobar(MeA_group_diffs_2PE_pd, "Change in Mean Port Distance (cm)",  
                   c("dimgrey", mea_color), pd_axes_2PE, "white", 0)
```

## Difference in Differences {.tabset}

### NAc {.tabset}

```{r 30-NAc_pd_diff2x_2PE, message = FALSE, warning = FALSE}
NAc_group_diffs2x_2PE_pd <- cbind.data.frame(NAc_group_diffs_2PE_pd$id[1:                                                                             (length(rownames(NAc_group_diffs_2PE_pd))/2)],
                                        NAc_group_diffs_2PE_pd$group[1:                                                                          (length(rownames(NAc_group_diffs_2PE_pd))/2)],
                              NAc_group_diffs_2PE_pd$PD_diff[(length(rownames(NAc_group_diffs_2PE_pd))/2)+1:
                                                               (length(rownames(NAc_group_diffs_2PE_pd))/2)] -
                                          NAc_group_diffs_2PE_pd$PD_diff[1:                                                                         (length(rownames(NAc_group_diffs_2PE_pd))/2)])

colnames(NAc_group_diffs2x_2PE_pd) <- c("id", "group", "PD_diff")

NAc_group_diffs2x_2PE_pd %>%
  group_by(group) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### MeA

```{r 31-MeA_pd_diff2x_2PE, message = FALSE, warning = FALSE, dev = 'pdf'}
MeA_group_diffs2x_2PE_pd <- cbind.data.frame(MeA_group_diffs_2PE_pd$id[1:                                                                             (length(rownames(MeA_group_diffs_2PE_pd))/2)],
                                        MeA_group_diffs_2PE_pd$group[1:                                                                          (length(rownames(MeA_group_diffs_2PE_pd))/2)],
                              MeA_group_diffs_2PE_pd$PD_diff[(length(rownames(MeA_group_diffs_2PE_pd))/2)+1:
                                                               (length(rownames(MeA_group_diffs_2PE_pd))/2)] -
                                          MeA_group_diffs_2PE_pd$PD_diff[1:                                                                         (length(rownames(MeA_group_diffs_2PE_pd))/2)])

colnames(MeA_group_diffs2x_2PE_pd) <- c("id", "group", "PD_diff")

MeA_group_diffs2x_2PE_pd %>%
  group_by(group) %>%
  get_summary_stats(PD_diff, type = "mean_se")
```

### T-tests {.tabset}

#### NAc

```{r 32-nac_pd_diff_ttest_2x, message = FALSE, warning = FALSE}
t.test(x = NAc_group_diffs2x_2PE_pd$PD_diff[NAc_group_diffs2x_2PE_pd$group %in% "Gi"], 
       y = NAc_group_diffs2x_2PE_pd$PD_diff[NAc_group_diffs2x_2PE_pd$group %in% "mCh"])
```

#### MeA

```{r 33-MeA_pd_diff_ttest_2x, message = FALSE, warning = FALSE}
t.test(x = MeA_group_diffs2x_2PE_pd$PD_diff[MeA_group_diffs2x_2PE_pd$group %in% "Gi"], 
       y = MeA_group_diffs2x_2PE_pd$PD_diff[MeA_group_diffs2x_2PE_pd$group %in% "mCh"])
```

### Graphs {.tabset}

#### NAc

```{r 34-nac_diff_graph_2PE_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.2, fig.height = 3}
bg_diff(NAc_group_diffs2x_2PE_pd, "∆ CNO - SAL", nac_color, pd_axes_2PE_diff, pe_colors)
```

#### MeA

```{r 35-mea_diff_graph_2PE_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.2, fig.height = 3}
bg_diff(MeA_group_diffs2x_2PE_pd, "∆ CNO - SAL", mea_color, pd_axes_2PE_diff, pe_colors)
```

# Heatmap {.tabset}

Generates a heatmap for each group. Sums all groups together at baseline and at treatment, and applies a gaussian smooth filter to both. It then subtracts the baseline from the treatment to identify the difference between treatment and baseline for all groups. 

## SAL {.tabset}

```{r 36-heatmap_generate_sal, message=FALSE, warning=FALSE}
heatmap_list_sal <- get_heatmap(data_projection_2PE_sal)
```

## MeA mCh

```{r 37-heatmap_mea_mch_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`MeA-control`)
```

## MeA Gi

```{r 38-heatmap_mea_gi_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`MeA-Gi`)
```

## NAc mCh

```{r 39-heatmap_nac_mch_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`NAc-control`)
```

## NAc Gi

```{r 40-heatmap_nac_gi_sal, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_sal$`NAc-Gi`)
```

## CNO {.tabset}

```{r 41-heatmap_generate_cno, message=FALSE, warning=FALSE}
heatmap_list_cno <- get_heatmap(data_projection_2PE_cno)
```

## MeA mCh

```{r 42-heatmap_mea_mch_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`MeA-control`)
```

## MeA Gi

```{r 43-heatmap_mea_gi_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`MeA-Gi`)
```

## NAc mCh

```{r 44-heatmap_nac_mch_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`NAc-control`)
```

## NAc Gi

```{r 45-heatmap_nac_gi_cno, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list_cno$`NAc-Gi`)
```
