---
author: "James Howe"
params:
  dataset: "Genes (4quad)"
  path: "data/behavior/genes/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
genes_id <- params$dataset
genes_path <- params$path

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

genes_groups <- unlist(strsplit(Sys.glob(paste0(genes_path, "*")), genes_path))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_genes <- read_stim_data("4quad", genes_groups, genes_path, genes_labels)

data_genes <- list(data_genes$`vg1-control`, data_genes$`vg1-stim`, 
                   data_genes$`vg2-control`, data_genes$`vg2-stim`)
names(data_genes) <- c("VGlut1-control", "VGlut1-stim", "VGlut2-control", "VGlut2-stim")
```

# Performance Index metrics

## Repeated Measures {.tabset}

### Summary statistics {.tabset}

```{r 2-pi_stats, message = FALSE, warning = FALSE}
baseline_array_genes <- transform_pi(data_genes, "baseline", "Quadrant", 1, 2400)
treatment_array_genes <- transform_pi(data_genes, "treatment", "Quadrant", 1, 2881)

pi_group_genes <- group_array(data_genes, 
                              baseline_array_genes, 
                              treatment_array_genes, "pi")
```

#### VGlut2

```{r 3-VGlut2_pi_stats, message = FALSE, warning = FALSE}
VGlut2_group_genes <- pi_group_genes[pi_group_genes$group 
                                     %in% c("VGlut2 ChR2", "VGlut2 eYFP"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_genes$time) <- c("OFF", "ON")

VGlut2_group_genes$group <- factor(VGlut2_group_genes$group, 
                                   levels = c("VGlut2 eYFP", "VGlut2 ChR2"))
levels(VGlut2_group_genes$group) <- c("eYFP", "ChR2")

VGlut2_group_genes %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### VGlut1

```{r 4-VGlut1_pi_stats, message = FALSE, warning = FALSE}
VGlut1_group_genes <- pi_group_genes[pi_group_genes$group 
                                     %in% c("VGlut1 ChR2", "VGlut1 eYFP"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_genes$time) <- c("OFF", "ON")

VGlut1_group_genes$group <- factor(VGlut1_group_genes$group, 
                                   levels = c("VGlut1 eYFP", "VGlut1 ChR2"))
levels(VGlut1_group_genes$group) <- c("eYFP", "ChR2")

VGlut1_group_genes %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### VGlut2

##### ANOVA

```{r 5-VGlut2_pi_anova, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_genes, "PI")
```

##### Pairwise comparisons

```{r 6-VGlut2_pi_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_genes, "PI")
```

#### VGlut1

##### ANOVA

```{r 7-VGlut1_pi_anova, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_genes, "PI")
```

##### Pairwise comparisons

```{r 8-VGlut1_pi_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_genes, "PI")
```

### Plots {.tabset}

#### VGlut2

```{r 9-VGlut2_pi_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 3.2, fig.width = 2}
bg_twogroup(VGlut2_group_genes, rm_pi_label, VGlut2_color, genes_pi_axes, chr2_blue)
```

#### VGlut1

```{r 10-VGlut1_pi_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 3.2, fig.width = 2}
bg_twogroup(VGlut1_group_genes, rm_pi_label, VGlut1_color, genes_pi_axes, chr2_blue)
```

## Difference {.tabset}

### Summary statistics

#### VGlut2

```{r 11-VGlut2_pi_diff_stats, message = FALSE, warning = FALSE}
VGlut2_group_genes <- cbind.data.frame(VGlut2_group_genes$id[1:                                                                             (length(rownames(VGlut2_group_genes))/2)],
                                        VGlut2_group_genes$group[1:                                                                          (length(rownames(VGlut2_group_genes))/2)],
                               VGlut2_group_genes$PI[(length(rownames(VGlut2_group_genes))/2)+1:
                                                               (length(rownames(VGlut2_group_genes))/2)] -
                                          VGlut2_group_genes$PI[1:                                                                         (length(rownames(VGlut2_group_genes))/2)])

colnames(VGlut2_group_genes) <- c("id", "group", "PI")

VGlut2_group_genes %>%
  group_by(group) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### VGlut1

```{r 12-VGlut1_pi_diff_stats, message = FALSE, warning = FALSE}
VGlut1_group_genes <- cbind.data.frame(VGlut1_group_genes$id[1:                                                                             (length(rownames(VGlut1_group_genes))/2)],
                                        VGlut1_group_genes$group[1:                                                                          (length(rownames(VGlut1_group_genes))/2)],
                               VGlut1_group_genes$PI[(length(rownames(VGlut1_group_genes))/2)+1:
                                                             (length(rownames(VGlut1_group_genes))/2)] -
                                          VGlut1_group_genes$PI[1:                                                                         (length(rownames(VGlut1_group_genes))/2)])

colnames(VGlut1_group_genes) <- c("id", "group", "PI")

VGlut1_group_genes %>%
  group_by(group) %>%
  get_summary_stats(PI, type = "mean_se")
```

### T-tests {.tabset}

#### VGlut2

```{r 13-VGlut2_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut2_group_genes$PI[VGlut2_group_genes$group %in% "eYFP"], 
       y = VGlut2_group_genes$PI[VGlut2_group_genes$group %in% "ChR2"])
```

#### VGlut1

```{r 14-VGlut1_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut1_group_genes$PI[VGlut1_group_genes$group %in% "eYFP"], 
       y = VGlut1_group_genes$PI[VGlut1_group_genes$group %in% "ChR2"])
```

### Graphs {.tabset}

#### VGlut2

```{r 15-VGlut2_diff_graph, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(VGlut2_group_genes, diff_pi_label, VGlut2_color, genes_pi_axes, chr2_blue)
```

#### VGlut1

```{r 16-VGlut1_diff_graph, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(VGlut1_group_genes, diff_pi_label, VGlut1_color, genes_pi_axes, chr2_blue)
```

# Port Distance metrics

```{r 17-pd_calculate, message = FALSE, warning = FALSE}
baseline_array_genes_pd <- transform_pd(data_genes, "baseline", "PortDistance", 1, 2400)
treatment_array_genes_pd <- transform_pd(data_genes, "treatment", "PortDistance", 1, 2881)

pd_group_genes <- group_array(data_genes, 
                                   baseline_array_genes_pd, 
                                   treatment_array_genes_pd, "pd")
```

## Repeated Measures {.tabset}

### Summary statistics {.tabset}

#### VGlut2

```{r 18-VGlut2_pd_rm_stats, message = FALSE, warning = FALSE}
VGlut2_group_genes <- pd_group_genes[pd_group_genes$group 
                                                 %in% c("VGlut2 ChR2", "VGlut2 eYFP"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut2_group_genes$time) <- c("OFF", "ON")

VGlut2_group_genes$group <- factor(VGlut2_group_genes$group, 
                                          levels = c("VGlut2 eYFP", "VGlut2 ChR2"))
levels(VGlut2_group_genes$group) <- c("eYFP", "ChR2")

VGlut2_group_genes %>%
  group_by(group, time) %>%
  get_summary_stats(PD, type = "mean_se")
```

#### VGlut1

```{r 19-VGlut1_pd_rm_stats, message = FALSE, warning = FALSE}
VGlut1_group_genes <- pd_group_genes[pd_group_genes$group 
                                                 %in% c("VGlut1 ChR2", "VGlut1 eYFP"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(VGlut1_group_genes$time) <- c("OFF", "ON")

VGlut1_group_genes$group <- factor(VGlut1_group_genes$group, 
                                          levels = c("VGlut1 eYFP", "VGlut1 ChR2"))
levels(VGlut1_group_genes$group) <- c("eYFP", "ChR2")

VGlut1_group_genes %>%
  group_by(group, time) %>%
  get_summary_stats(PD, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### VGlut2

##### ANOVA

```{r 20-VGlut2_pd_anova, message = FALSE, warning = FALSE}
display_anova(VGlut2_group_genes, "PD")
```

##### Pairwise comparisons

```{r 21-VGlut2_pd_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut2_group_genes, "PD")
```

#### VGlut1

##### ANOVA

```{r 22-VGlut1_pd_anova, message = FALSE, warning = FALSE}
display_anova(VGlut1_group_genes, "PD")
```

##### Pairwise comparisons

```{r 23-VGlut1_pd_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(VGlut1_group_genes, "PD")
```

### Plots {.tabset}

#### VGlut2

```{r 24-VGlut2_pd_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 3.2, fig.width = 2}
bg_twogroup_nobar(VGlut2_group_genes, rm_pd_label, VGlut2_color, genes_pd_axes, chr2_blue, 0)
```

#### VGlut1

```{r 25-VGlut1_pi_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.height = 3.2, fig.width = 2}
bg_twogroup_nobar(VGlut1_group_genes, rm_pd_label, VGlut1_color, genes_pd_axes, chr2_blue, 0)
```

## Difference {.tabset}

### Summary statistics

#### VGlut2

```{r 26-VGlut2_pd_diff_stats, message = FALSE, warning = FALSE}
VGlut2_group_genes <- cbind.data.frame(VGlut2_group_genes$id[1:                                                                             (length(rownames(VGlut2_group_genes))/2)],
                                        VGlut2_group_genes$group[1:                                                                          (length(rownames(VGlut2_group_genes))/2)],
                               VGlut2_group_genes$PD[(length(rownames(VGlut2_group_genes))/2)+1:
                                                               (length(rownames(VGlut2_group_genes))/2)] -
                                          VGlut2_group_genes$PD[1:                                                                         (length(rownames(VGlut2_group_genes))/2)])

colnames(VGlut2_group_genes) <- c("id", "group", "PD")

VGlut2_group_genes %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

#### VGlut1

```{r 27-VGlut1_pd_diff_stats, message = FALSE, warning = FALSE}
VGlut1_group_genes <- cbind.data.frame(VGlut1_group_genes$id[1:                                                                             (length(rownames(VGlut1_group_genes))/2)],
                                        VGlut1_group_genes$group[1:                                                                          (length(rownames(VGlut1_group_genes))/2)],
                               VGlut1_group_genes$PD[(length(rownames(VGlut1_group_genes))/2)+1:
                                                             (length(rownames(VGlut1_group_genes))/2)] -
                                          VGlut1_group_genes$PD[1:                                                                         (length(rownames(VGlut1_group_genes))/2)])

colnames(VGlut1_group_genes) <- c("id", "group", "PD")

VGlut1_group_genes %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

### T-tests {.tabset}

#### VGlut2

```{r 28-VGlut2_pd_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut2_group_genes$PD[VGlut2_group_genes$group %in% "eYFP"], 
       y = VGlut2_group_genes$PD[VGlut2_group_genes$group %in% "ChR2"])
```

#### VGlut1

```{r 29-VGlut1_pd_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = VGlut1_group_genes$PD[VGlut1_group_genes$group %in% "eYFP"], 
       y = VGlut1_group_genes$PD[VGlut1_group_genes$group %in% "ChR2"])
```

### Graphs {.tabset}

#### VGlut2

```{r 30-VGlut2_diff_graph_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(VGlut2_group_genes, diff_pd_label, VGlut2_color, genes_pd_axes_diff, chr2_blue)
```

#### VGlut1

```{r 31-VGlut1_diff_graph_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(VGlut1_group_genes, diff_pd_label, VGlut1_color, genes_pd_axes_diff, chr2_blue)
```

# Heatmap {.tabset}

Generates a heatmap for each group. Sums all groups together at baseline and at treatment, and applies a gaussian smooth filter to both. It then subtracts the baseline from the treatment to identify the difference between treatment and baseline for all groups. 

```{r 32-heatmap_generate, message = FALSE, warning = FALSE}
heatmap_list <- get_heatmap(data_genes)
```

## VGlut1 eYFP

```{r 33-heatmap_vg1_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`VGlut1-control`)
```

## VGlut1 ChR2

```{r 34-heatmap_vg1_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`VGlut1-stim`)
```

## VGlut2 eYFP

```{r 35-heatmap_vg2_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`VGlut2-control`)
```

## VGlut2 ChR2

```{r 36-heatmap_vg2_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`VGlut2-stim`)
```

# Paths {.tabset}

## ChR2 {.tabset}

### VGlut2

```{r 37-path_vg2_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_path(data_genes$`VGlut2-stim`$`VGlut2 ChR2|123123-VG2-ChR2-89fB7-3_LR.txt`, VGlut2_color)
```

### VGlut1

```{r 38-path_vg1_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_path(data_genes$`VGlut1-stim`$`VGlut1 ChR2|210426_VG1-ChR2-VG12-3_LR.txt`, VGlut1_color)
```

## eYFP {.tabset}

### VGlut2

```{r 39-path_vg2_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_path(data_genes$`VGlut2-control`$`VGlut2 eYFP|050721_VG2-eYFP-79f19-1_LR.txt`, control_color)
```

### VGlut1

```{r 40-path_vg1_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_path(data_genes$`VGlut1-control`$`VGlut1 eYFP|210505_VG1-eYFP-VG11-1_LR.txt`, control_color) 
```
