---
author: "James Howe"
params:
  dataset: "Projections (4quad)"
  path: "data/behavior/projections/"
title: "Behavioral analysis: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
# set up paths
projection_id <- params$dataset
projection_path <- params$path

source("code/behavior-refs.R")
source("code/behavior-misc_processes.R")
source("code/behavior-plot_functions.R")

projection_groups <- unlist(strsplit(Sys.glob(paste0(projection_path, "*")), projection_path))[c(FALSE, TRUE)]
```

# Load the data

Names have to be given manually in most cases. Also for now copy into console because it does not load due to odd workspace issues. This loads all files in a directory and puts it into the correct format automatically.

```{r 1-read_data, message = FALSE, warning = FALSE}
# set up the object with pointers
data_projection <- read_stim_data("4quad", projection_groups, projection_path, projection_stim_labels)

data_projection <- list(data_projection$`MeA-control`, data_projection$`MeA-stim`, 
                        data_projection$`NAc-control`, data_projection$`NAc-stim`)
names(data_projection) <- c("MeA-control", "MeA-stim", "NAc-control", "NAc-stim")
```

# Performance Index metrics

## Repeated Measures {.tabset}

### Summary statistics {.tabset}

```{r 2-pi_stats, message = FALSE, warning = FALSE}
baseline_array_projection <- transform_pi(data_projection, "baseline", "Quadrant", 1, 2400)
treatment_array_projection <- transform_pi(data_projection, "treatment", "Quadrant", 1, 2881)

pi_group_projection <- group_array(data_projection, 
                              baseline_array_projection, 
                              treatment_array_projection, "pi")
```

#### NAc

```{r 3-NAc_pi_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- pi_group_projection[pi_group_projection$group 
                                     %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection$time) <- c("OFF", "ON")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                   levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### MeA

```{r 4-MeA_pi_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- pi_group_projection[pi_group_projection$group 
                                     %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "PI", baseline_pi, treatment_pi) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection$time) <- c("OFF", "ON")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                   levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group, time) %>%
  get_summary_stats(PI, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### NAc

##### ANOVA

```{r 5-NAc_pi_anova, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "PI")
```

##### Pairwise comparisons

```{r 6-NAc_pi_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "PI")
```

#### MeA

##### ANOVA

```{r 7-MeA_pi_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "PI")
```

##### Pairwise comparisons

```{r 8-MeA_pi_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "PI")
```

### Plots {.tabset}

#### NAc

```{r 9-NAc_pi_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 2, fig.height = 3.2}
bg_twogroup_nobar(NAc_group_projection, rm_pi_label, nac_color, proj_pi_axes, chr2_blue, 0)
```

#### MeA

```{r 10-MeA_pi_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 2, fig.height = 3.2}
bg_twogroup_nobar(MeA_group_projection, rm_pi_label, mea_color, proj_pi_axes, chr2_blue, 0)
```

## Difference {.tabset}

### Summary statistics

#### NAc

```{r 11-NAc_pi_diff_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- cbind.data.frame(NAc_group_projection$id[1:                                                                             (length(rownames(NAc_group_projection))/2)],
                                        NAc_group_projection$group[1:                                                                          (length(rownames(NAc_group_projection))/2)],
                               NAc_group_projection$PI[(length(rownames(NAc_group_projection))/2)+1:
                                                               (length(rownames(NAc_group_projection))/2)] -
                                          NAc_group_projection$PI[1:                                                                         (length(rownames(NAc_group_projection))/2)])

colnames(NAc_group_projection) <- c("id", "group", "PI")

NAc_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PI, type = "mean_se")
```

#### MeA

```{r 12-MeA_pi_diff_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- cbind.data.frame(MeA_group_projection$id[1:                                                                             (length(rownames(MeA_group_projection))/2)],
                                        MeA_group_projection$group[1:                                                                          (length(rownames(MeA_group_projection))/2)],
                               MeA_group_projection$PI[(length(rownames(MeA_group_projection))/2)+1:
                                                             (length(rownames(MeA_group_projection))/2)] -
                                          MeA_group_projection$PI[1:                                                                         (length(rownames(MeA_group_projection))/2)])

colnames(MeA_group_projection) <- c("id", "group", "PI")

MeA_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PI, type = "mean_se")
```

### T-tests {.tabset}

#### NAc

```{r 13-NAc_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = NAc_group_projection$PI[NAc_group_projection$group %in% "eYFP"], 
       y = NAc_group_projection$PI[NAc_group_projection$group %in% "ChR2"])
```

#### MeA

```{r 14-MeA_pi_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = MeA_group_projection$PI[MeA_group_projection$group %in% "eYFP"], 
       y = MeA_group_projection$PI[MeA_group_projection$group %in% "ChR2"])
```

### Graphs {.tabset}

#### NAc

```{r 15-nac_diff_graph, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(NAc_group_projection, diff_pi_label, nac_color, proj_pi_axes, chr2_blue)
```

#### MeA

```{r 16-mea_diff_graph, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.4, fig.height = 3}
bg_diff(MeA_group_projection, diff_pi_label, mea_color, proj_pi_axes, chr2_blue)
```

# Port Distance metrics

```{r 17-pd_calculate, message = FALSE, warning = FALSE}
baseline_array_projection_pd <- transform_pd(data_projection, "baseline", "PortDistance", 1, 2400)
treatment_array_projection_pd <- transform_pd(data_projection, "treatment", "PortDistance", 1, 2881)

pd_group_projection <- group_array(data_projection, 
                                   baseline_array_projection_pd, 
                                   treatment_array_projection_pd, "pd")
```

## Repeated measures {.tabset}

### Summary statistics

#### NAc

```{r 18-NAc_pd_rm_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- pd_group_projection[pd_group_projection$group 
                                                 %in% c("NAc ChR2", "NAc eYFP"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(NAc_group_projection$time) <- c("OFF", "ON")

NAc_group_projection$group <- factor(NAc_group_projection$group, 
                                          levels = c("NAc eYFP", "NAc ChR2"))
levels(NAc_group_projection$group) <- c("eYFP", "ChR2")

NAc_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

#### MeA

```{r 19-MeA_pd_rm_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- pd_group_projection[pd_group_projection$group 
                                                 %in% c("MeA ChR2", "MeA eYFP"),] %>%
  gather(key = "time", value = "PD", baseline_pd, treatment_pd) %>%
  convert_as_factor(group, time)
levels(MeA_group_projection$time) <- c("OFF", "ON")

MeA_group_projection$group <- factor(MeA_group_projection$group, 
                                          levels = c("MeA eYFP", "MeA ChR2"))
levels(MeA_group_projection$group) <- c("eYFP", "ChR2")

MeA_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

### Two-way repeated-measures ANOVA {.tabset}

#### NAc

##### ANOVA

```{r 20-NAc_pd_anova, message = FALSE, warning = FALSE}
display_anova(NAc_group_projection, "PD")
```

##### Pairwise comparisons

```{r 21-NAc_pd_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(NAc_group_projection, "PD")
```

#### MeA

##### ANOVA

```{r 22-MeA_pd_anova, message = FALSE, warning = FALSE}
display_anova(MeA_group_projection, "PD")
```

##### Pairwise comparisons

```{r 23-MeA_pd_pairwise, message = FALSE, warning = FALSE}
pairwise_comp_anova(MeA_group_projection, "PD")
```

### Plots {.tabset}

#### NAc

```{r 24-NAc_pd_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 2, fig.height = 3.2}
bg_twogroup_nobar(NAc_group_projection, rm_pd_label, nac_color, proj_pd_axes, chr2_blue, 0)
```

#### MeA

```{r 25-MeA_pd_plot, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 2, fig.height = 3.2}
bg_twogroup_nobar(MeA_group_projection, rm_pd_label, mea_color, proj_pd_axes, chr2_blue, 0)
```

## Difference {.tabset}

### Summary statistics

#### NAc

```{r 26-NAc_pd_diff_stats, message = FALSE, warning = FALSE}
NAc_group_projection <- cbind.data.frame(NAc_group_projection$id[1:                                                                             (length(rownames(NAc_group_projection))/2)],
                                        NAc_group_projection$group[1:                                                                          (length(rownames(NAc_group_projection))/2)],
                               NAc_group_projection$PD[(length(rownames(NAc_group_projection))/2)+1:
                                                               (length(rownames(NAc_group_projection))/2)] -
                                          NAc_group_projection$PD[1:                                                                         (length(rownames(NAc_group_projection))/2)])

colnames(NAc_group_projection) <- c("id", "group", "PD")

NAc_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

#### MeA

```{r 27-MeA_pd_diff_stats, message = FALSE, warning = FALSE}
MeA_group_projection <- cbind.data.frame(MeA_group_projection$id[1:                                                                             (length(rownames(MeA_group_projection))/2)],
                                        MeA_group_projection$group[1:                                                                          (length(rownames(MeA_group_projection))/2)],
                               MeA_group_projection$PD[(length(rownames(MeA_group_projection))/2)+1:
                                                             (length(rownames(MeA_group_projection))/2)] -
                                          MeA_group_projection$PD[1:                                                                         (length(rownames(MeA_group_projection))/2)])

colnames(MeA_group_projection) <- c("id", "group", "PD")

MeA_group_projection %>%
  group_by(group) %>%
  get_summary_stats(PD, type = "mean_se")
```

### T-tests {.tabset}

#### NAc

```{r 28-NAc_pd_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = NAc_group_projection$PD[NAc_group_projection$group %in% "eYFP"], 
       y = NAc_group_projection$PD[NAc_group_projection$group %in% "ChR2"])
```

#### MeA

```{r 29-MeA_pd_diff_ttest, message = FALSE, warning = FALSE}
t.test(x = MeA_group_projection$PD[MeA_group_projection$group %in% "eYFP"], 
       y = MeA_group_projection$PD[MeA_group_projection$group %in% "ChR2"])
```

### Graphs {.tabset}

#### NAc

```{r 30-NAc_diff_graph_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(NAc_group_projection, diff_pd_label, nac_color, ap_pd_axes_diff, chr2_blue)
```

#### MeA

```{r 31-MeA_diff_graph_pd, message = FALSE, warning = FALSE, dev = 'pdf', fig.width = 1.3, fig.height = 3}
bg_diff(MeA_group_projection, diff_pd_label, mea_color, ap_pd_axes_diff, chr2_blue)
```

# Heatmap {.tabset}

Generates a heatmap for each group. Sums all groups together at baseline and at treatment, and applies a gaussian smooth filter to both. It then subtracts the baseline from the treatment to identify the difference between treatment and baseline for all groups. 

```{r 32-heatmap_generate, message=FALSE, warning=FALSE}
heatmap_list <- get_heatmap(data_projection)
```

## MeA eYFP

```{r 33-heatmap_mea_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`MeA-control`)
```

## MeA ChR2

```{r 34-heatmap_mea_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`MeA-stim`)
```

## NAc eYFP

```{r 35-heatmap_nac_eyfp, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`NAc-control`)
```

## NAc ChR2

```{r 36-heatmap_nac_chr2, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4, dev = "svg"}
plot_heatmap(heatmap_array = heatmap_list$`NAc-stim`)
```
