---
author: "James Howe"
title: "Fluorescence projections analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This is a notebook that processes 4-quad data and outputs analyses and figures for publication. 

```{r setup}
source("../code/behavior-refs.R")
source("../code/behavior-misc_processes.R")
source("../code/behavior-plot_functions.R")
source("../code/sequencing_misc.R")
source("../code/sequencing-color_scales.R")
source("../code/sequencing-plot_functions.R")

require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

# Topographic MeA and NAc

## Retrograde NAc and MeA to plCoA {.tabset}

### Total numbers {.tabset}

```{r 1-read_data_retrograde, message = FALSE, warning = FALSE}
# set up the object
retro_mea_nac <- read.csv("data/projections/retrograde_mea_nac.csv")

mea_means <- retro_mea_nac[retro_mea_nac$group == "MeA",] %>% group_by(ap_location) %>% 
  summarise(sem = sd(number)/sqrt(4), number = mean(number))

nac_means <- retro_mea_nac[retro_mea_nac$group == "NAc",] %>% group_by(ap_location) %>% 
  summarise(sem = sd(number)/sqrt(4), number = mean(number))
```

#### MeA

```{r 2-mea_total, message = FALSE, warning = FALSE, fig.height = 2, fig.width = 4}
ggplot(retro_mea_nac[retro_mea_nac$group == "MeA",], aes(x = ap_location, y = number, group = animal_id)) +
  geom_line(aes(y = number, x = ap_location), data = mea_means, group = 1, colour = mea_color) +
  geom_errorbar(aes(ymin = number - sem, ymax = number + sem), 
                data = mea_means, group = 1, width = 0, colour = mea_color) +
  geom_line(colour = "gray") +
  theme_classic() +
  scale_x_reverse(limits = c(-1.29, -2.51), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 202)) +
  ylab("Labeled Cells") + xlab("AP location (mm from bregma)") +
  theme(axis.text.x = element_text(colour = "black"), axis.text.y = element_text(colour = "black"),
        legend.position = "none", legend.title = element_blank())
```

#### NAc

```{r 3-nac_total, message = FALSE, warning = FALSE, fig.height = 2, fig.width = 4}
ggplot(retro_mea_nac[retro_mea_nac$group == "NAc",], aes(x = ap_location, y = number, group = animal_id)) +
  geom_line(aes(y = number, x = ap_location), data = nac_means, group = 1, colour = nac_color) +
  geom_errorbar(aes(ymin = number - sem, ymax = number + sem), 
                data = nac_means, group = 1, width = 0, colour = nac_color) +
  geom_line(colour = "gray") +
  theme_classic() +
  scale_x_reverse(limits = c(-1.29, -2.51), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 120)) +
  ylab("Labeled Cells") + xlab("AP location (mm from bregma)") +
  theme(axis.text.x = element_text(colour = "black"), axis.text.y = element_text(colour = "black"),
        legend.position = "none", legend.title = element_blank())
```

### Proportion

```{r 4-label_proportion, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 5}
new_proportions <- retro_mea_nac %>% group_by(group, ap_location) %>% summarise(number = sum(number))
divisor <- retro_mea_nac %>% group_by(ap_location) %>% summarise(number = sum(number))
new_proportions$number[1:13] <- new_proportions$number[1:13] / divisor$number
new_proportions$number[14:26] <- new_proportions$number[14:26] / divisor$number

new_proportions$ap_location <- factor(new_proportions$ap_location, levels = rev(new_proportions$ap_location[1:13]))

ggplot(new_proportions, aes(x = ap_location, y = number, fill = group)) +
  geom_bar(position="stack", stat="identity") +
  geom_hline(yintercept = 0.568, linetype = "dashed") +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c(mea_color, nac_color)) +
  labs(fill = '') + xlab("") + ylab('Proportion in bin') +
  theme_classic() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

### Projection in Region {.tabset}

```{r 5-projection_proportion, message = FALSE, warning = FALSE}
retro_list <- split(retro_mea_nac, f = retro_mea_nac$animal_id)

percent_retro <- cbind.data.frame(c("A", "B", "C", "D", "E", "F", "G", "H"),
                                  c("MeA", "NAc", "MeA", "MeA", "NAc", "NAc", "MeA", "NAc"),
                                  unlist(lapply(retro_list, function(x) sum(x$number[1:5]) / sum(x$number))),
                                  unlist(lapply(retro_list, function(x) sum(x$number[6:8]) / sum(x$number))),
                                  unlist(lapply(retro_list, function(x) sum(x$number[9:13]) / sum(x$number))))
colnames(percent_retro) <- c("id", "group", "aplCoA", "mplCoA", "pplCoA")

percent_retro  <- percent_retro %>% pivot_longer(cols = c(aplCoA, mplCoA, pplCoA))

percent_retro %>%
  group_by(group, name) %>%
  get_summary_stats(value, type = "mean_se")
```

#### Two-way ANOVA {.tabset}

##### ANOVA

```{r 6-anova_proportion, message = FALSE, warning = FALSE}
proportion_anova <- anova_test(data = percent_retro,
                               dv = value,
                               wid = id,
                               between = group,
                               within = name)

proportion_anova$ANOVA
```

##### Pairwise comparisons

```{r 7-pairwise_proportion, message = FALSE, warning = FALSE}
percent_retro %>% tukey_hsd(value ~ name * group, paired = FALSE,
                            p.adjust.method = "bonferroni")
```

#### Plot

```{r 8-retro_proportion_plot, message = FALSE, warning = FALSE, fig.height = 2, fig.width = 2}
# remove middle for graphing
percent_retro <- percent_retro[percent_retro$name != "mplCoA",]

summary <- percent_retro %>%
    group_by(group, name) %>%
    summarize(sem = sd(value)/sqrt(n()), value = mean(value))

ggplot(percent_retro, aes(x = name, y = value, group = group, colour = group)) + 
  geom_bar(stat = "summary", width = 0.7, position = position_dodge(width=0.8), fill = NA) +
    geom_errorbar(aes(ymin = value - sem, ymax = value + sem), data = summary, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = group, group = group), shape = 21, color = 'black', 
               position = position_dodge(width = 0.8)) +
    scale_y_continuous(expand = c(0,0), limits = c(0, 1)) +
    scale_colour_manual(values = c(mea_color, nac_color)) +
    scale_fill_manual(values = c(mea_color, nac_color)) +
    xlab("") +
    ylab("Proportion from zone") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

# MeA-NAc Anterograde Collateralization {.tabset}

```{r 9-read_collateralization_data, message = FALSE, warning = FALSE}
# set up the object
ant_col_mea_nac <- read.csv("data/projections/anterograde_collateralization_mea_nac.csv")
ant_col_mea_nac[,3:8] <- ant_col_mea_nac[,3:8] / 10000000

paired_nac <- cbind.data.frame(rep(ant_col_mea_nac$animal_id[1:5], 6),
                               c(rep("NAc", 5), rep("MeA", 5), rep("AHi", 5), rep("OT", 5), 
                                 rep("pmCoA", 5), rep("BNST", 5)),
                               c(rep(1, 5), 
                                 ant_col_mea_nac$MeA_density[1:5] / ant_col_mea_nac$NAc_density[1:5],
                                 ant_col_mea_nac$AHi_density[1:5] / ant_col_mea_nac$NAc_density[1:5],
                                 ant_col_mea_nac$OT_density[1:5] / ant_col_mea_nac$NAc_density[1:5],
                                 ant_col_mea_nac$pmCoA_density[1:5] / ant_col_mea_nac$NAc_density[1:5],
                                 ant_col_mea_nac$BNST_density[1:5] / ant_col_mea_nac$NAc_density[1:5]))
colnames(paired_nac) <- c("animal_id", "region", "NAc_norm_density")
paired_nac$region <- factor(paired_nac$region, levels = c("NAc", "MeA", "AHi", 
                                                          "OT", "pmCoA", "BNST"))

paired_mea <- cbind.data.frame(rep(ant_col_mea_nac$animal_id[6:length(rownames(ant_col_mea_nac))], 6),
                               c(rep("MeA", 7), rep("NAc", 7), rep("AHi", 7), rep("OT", 7), 
                                 rep("pmCoA", 7), rep("BNST", 7)),
                               c(rep(1, times = 7),
                                 ant_col_mea_nac$NAc_density[6:length(rownames(ant_col_mea_nac))] /
                                   ant_col_mea_nac$MeA_density[6:length(rownames(ant_col_mea_nac))],
                                 ant_col_mea_nac$AHi_density[6:length(rownames(ant_col_mea_nac))] /
                                   ant_col_mea_nac$MeA_density[6:length(rownames(ant_col_mea_nac))],
                                 ant_col_mea_nac$OT_density[6:length(rownames(ant_col_mea_nac))] /
                                   ant_col_mea_nac$MeA_density[6:length(rownames(ant_col_mea_nac))],
                                 ant_col_mea_nac$pmCoA_density[6:length(rownames(ant_col_mea_nac))] /
                                   ant_col_mea_nac$MeA_density[6:length(rownames(ant_col_mea_nac))],
                                 ant_col_mea_nac$BNST_density[6:length(rownames(ant_col_mea_nac))] /
                                   ant_col_mea_nac$MeA_density[6:length(rownames(ant_col_mea_nac))]))
colnames(paired_mea) <- c("animal_id", "region", "MeA_norm_density")
paired_mea$region <- factor(paired_mea$region, levels = c("MeA", "NAc", "AHi", 
                                                          "OT", "pmCoA", "BNST"))
```

## Absolute Difference {.tabset}

### MeA {.tabset}

#### Plot

```{r 10-ant_col_mea_plot, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 2}
summary <- ant_col_mea_nac %>%
    group_by(retroaav_site) %>%
    summarize(sem = sd(MeA_density)/sqrt(n()), MeA_density = mean(MeA_density))

ggplot(ant_col_mea_nac, aes(x = retroaav_site, y = MeA_density, group = retroaav_site, colour = retroaav_site)) + 
    geom_bar(stat = "summary", fill = NA) +
    geom_errorbar(aes(ymin = MeA_density - sem, ymax = MeA_density + sem), data = summary, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = retroaav_site, group = retroaav_site), shape = 21, color = 'black') +
    scale_y_continuous(expand = c(0,0), limits = c(0, 5)) +
    scale_colour_manual(values = c(mea_color, nac_color)) +
    scale_fill_manual(values = c(mea_color, nac_color)) +
    xlab("") +
    ylab("MeA integrated fluorescence (a.u.)") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

#### T-test

```{r 11-ant_col_mea_ttest, message = FALSE, warning = FALSE}
t.test(x = ant_col_mea_nac$MeA_density[ant_col_mea_nac$retroaav_site %in% "MeA"], 
       y = ant_col_mea_nac$MeA_density[ant_col_mea_nac$retroaav_site %in% "NAc"])
```

### NAc {.tabset}

#### Plot

```{r 12-ant_col_nac_plot, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 2}
summary <- ant_col_mea_nac %>%
    group_by(retroaav_site) %>%
    summarize(sem = sd(NAc_density)/sqrt(n()), NAc_density = mean(NAc_density))

ggplot(ant_col_mea_nac, aes(x = retroaav_site, y = NAc_density, group = retroaav_site, colour = retroaav_site)) + 
    geom_bar(stat = "summary", fill = NA) +
    geom_errorbar(aes(ymin = NAc_density - sem, ymax = NAc_density + sem), data = summary, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = retroaav_site, group = retroaav_site), shape = 21, color = 'black') +
    scale_y_continuous(expand = c(0,0), limits = c(0, 5)) +
    scale_colour_manual(values = c(mea_color, nac_color)) +
    scale_fill_manual(values = c(mea_color, nac_color)) +
    xlab("") +
    ylab("NAc integrated fluorescence (a.u.)") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

#### T-test

```{r 13-ant_col_nac_ttest, message = FALSE, warning = FALSE}
t.test(x = ant_col_mea_nac$NAc_density[ant_col_mea_nac$retroaav_site %in% "NAc"], 
       y = ant_col_mea_nac$NAc_density[ant_col_mea_nac$retroaav_site %in% "MeA"])
```

### Combined Plot

```{r 14-ant_col_nac_combined, message = FALSE, warning = FALSE, fig.height = 2.6, fig.width = 2.6}
ant_col_mea_nac <- ant_col_mea_nac[,1:4]

ant_col_mea_nac <- ant_col_mea_nac %>%
  gather(key = "region", value = "density", MeA_density, NAc_density) %>%
  convert_as_factor(animal_id, retroaav_site, region)
levels(ant_col_mea_nac$region) <- c("MeA", "NAc")

summary <- ant_col_mea_nac %>%
  group_by(retroaav_site, region) %>%
  summarize(sem = sd(density)/sqrt(n()), density= mean(density))

ggplot(ant_col_mea_nac, aes(x = region, y = density, colour = as.character(retroaav_site))) +
    geom_bar(stat = "summary", position = "dodge", fill = NA) +
    geom_errorbar(aes(ymin = density - sem, ymax = density + sem), 
                  data = summary, width = .5, position = position_dodge(width = 0.9)) +
    #geom_point(aes(group = animal_id), shape = 21, color = 'black') +
    geom_point(aes(fill = as.character(retroaav_site), 
                   group = as.character(retroaav_site)), shape = 21, color = 'black', 
               position = position_dodge(width = 0.8)) +
    scale_y_continuous(expand = c(0,0), limits = c(0, 5)) +
    scale_colour_manual(values = c(mea_color, nac_color)) +
    scale_fill_manual(values = c(mea_color, nac_color)) +
    xlab("") +
    ylab("Integrated fluorescence (a.u.)" ) +
    facet_wrap(~ retroaav_site) +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

#### Two-way ANOVA {.tabset}

##### ANOVA

```{r 17-collateralization_anova, message = FALSE, warning = FALSE}
proportion_anova <- anova_test(data = ant_col_mea_nac,
                               dv = density,
                               wid = animal_id,
                               between =  retroaav_site,
                               within = region)

proportion_anova
```

##### Pairwise comparisons

```{r 18-collateralization_pairwise, message = FALSE, warning = FALSE}
pairwise_group_anova <- ant_col_mea_nac %>%
    tukey_hsd(density ~ region * retroaav_site, paired = FALSE,
              p.adjust.method = "bonferroni")
  
pairwise_group_anova
```

## Within-animal Relative Difference {.tabset}

### retro-MeA {.tabset}

#### Plot

```{r 19-ant_col_retromea_plot, message = FALSE, warning = FALSE, fig.height = 2.2, fig.width = 4}
summary <- paired_mea %>%
    group_by(region) %>%
    summarize(sem = sd(MeA_norm_density)/sqrt(n()), MeA_norm_density = mean(MeA_norm_density))

ggplot(paired_mea, aes(x = region, y = MeA_norm_density, group = region, colour = region)) + 
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_line(aes(group = animal_id), colour = "black") +
    geom_bar(stat = "summary", fill = NA) +
    geom_errorbar(aes(ymin = MeA_norm_density - sem, ymax = MeA_norm_density + sem), data = summary, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = region, group = region), shape = 21, color = 'black') +
    scale_y_continuous(expand = c(0,0), limits = c(0, 2)) +
    scale_colour_manual(values = rep(mea_color, 6)) +
    scale_fill_manual(values = rep(mea_color, 6)) +
    xlab("") +
    ylab("Within-animal integrated fluorescence (% MeA fluorescence)") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

#### Paired T-test

```{r 20-ant_col_retromea_pairedttest, message = FALSE, warning = FALSE}
t.test(x = paired_mea$MeA_norm_density[paired_mea$region %in% "MeA"], 
       y = paired_mea$MeA_norm_density[paired_mea$region %in% "NAc"],
       paired = TRUE)
```

### retro-NAc {.tabset}

#### Plot

```{r 21-ant_col_retronac_plot, message = FALSE, warning = FALSE, fig.height = 2.2, fig.width = 4}
summary <- paired_nac %>%
    group_by(region) %>%
    summarize(sem = sd(NAc_norm_density)/sqrt(n()), NAc_norm_density = mean(NAc_norm_density))

ggplot(paired_nac, aes(x = region, y = NAc_norm_density, group = region, colour = region)) + 
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_line(aes(group = animal_id), colour = "black") +
    geom_bar(stat = "summary", fill = NA) +
    geom_errorbar(aes(ymin = NAc_norm_density - sem, ymax = NAc_norm_density + sem), data = summary, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = region, group = region), shape = 21, color = 'black') +
    scale_y_continuous(expand = c(0,0), limits = c(0, 1.2)) +
    scale_colour_manual(values = rep(nac_color, 6)) +
    scale_fill_manual(values = rep(nac_color, 6)) +
    xlab("") +
    ylab("Within-animal integrated fluorescence (% NAc fluorescence)") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

#### Paired T-test

```{r 22-ant_col_retronac_pairedttest, message = FALSE, warning = FALSE}
t.test(x = paired_nac$NAc_norm_density[paired_nac$region %in% "NAc"], 
       y = paired_nac$NAc_norm_density[paired_nac$region %in% "MeA"],
       paired = TRUE)
```

# Anterograde SypEGFP

```{r 23-anterograde_graph, message = FALSE, warning = FALSE, fig.height = 2.5, fig.width = 9.6}
# set up the object with pointers
anterograde_syp <- read.csv("data/projections/anterograde_syp.csv", row.names = 1)

# change names to something more recognizable
rownames(anterograde_syp)[rownames(anterograde_syp) %in% "CPu"] <- "Str"
rownames(anterograde_syp)[rownames(anterograde_syp) %in% "Tu"] <- "OT"
rownames(anterograde_syp)[rownames(anterograde_syp) %in% "MPA"] <- "MPOA"

anterograde_syp <- anterograde_syp[!rownames(anterograde_syp) %in% "sox",]
anterograde_syp <- anterograde_syp[!rownames(anterograde_syp) %in% "mfb",]

# get means for each region
avg_anterograde_syp <- cbind.data.frame(apply(anterograde_syp, 1, mean),
                                        apply(anterograde_syp, 1, function(x) sd(x)/sqrt(5)))
colnames(avg_anterograde_syp) <- c("Mean", "SEM")

norm_anterograde_syp <- anterograde_syp / apply(anterograde_syp[76,], 1, mean)

# cut at half of plCoA fluorescence
norm_anterograde_syp <- norm_anterograde_syp[apply(norm_anterograde_syp, 1, mean) > 0.1,]

summary_anterograde_syp <- cbind.data.frame(apply(norm_anterograde_syp, 1, mean),
                                            apply(norm_anterograde_syp, 1, 
                                                  function(x) sd(x)/sqrt(5)),
                                           rownames(norm_anterograde_syp))
colnames(summary_anterograde_syp) <- c("value", "sem", "region")

norm_anterograde_syp <- cbind.data.frame(norm_anterograde_syp, rownames(norm_anterograde_syp))
colnames(norm_anterograde_syp) <- c("M1", "M2", "M3", "M4", "M5", "region")

# remove BMA because it could be some leak, and Nv and MPA, which are buoyed by outliers
norm_anterograde_syp <- norm_anterograde_syp[!rownames(norm_anterograde_syp) %in% c("BMA", "MPOA", "Nv"),]
summary_anterograde_syp <- summary_anterograde_syp[!rownames(summary_anterograde_syp) %in% c("BMA", "MPOA", "Nv"),]

norm_anterograde_syp <- norm_anterograde_syp %>% pivot_longer(M1:M5)
norm_anterograde_syp$region <- factor(norm_anterograde_syp$region)
norm_anterograde_syp$region <- reorder(norm_anterograde_syp$region, -norm_anterograde_syp$value) 

#
ggplot(data = norm_anterograde_syp, aes(x = region, y = value)) + 
  geom_bar(stat = "summary", position = "dodge", width = 0.5, fill = "grey") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_errorbar(aes(ymin = value - sem, ymax = value + sem), data = summary_anterograde_syp, 
                width = .3, position = position_dodge(width = 0.9)) +
  ylab("SypEGFP Fiber Density (a.u.)") +
  xlab("") +
  scale_x_reverse() +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(ylim = c(0, 5)) +
  theme_classic() +
  theme(legend.position="none",
        axis.ticks.x=element_blank(),
        axis.text.x = element_text(colour = "black", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black"))
```

# Two color anterograde projection mapping

## plCoA zone fluorescence

```{r 24-plCoA_zones_2color, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 4}
# set up the object with pointers
anterograde_2c <- read.csv("data/projections/anterograde_2color.csv", row.names = 1)

anterograde_2c_test <- cbind.data.frame(rownames(anterograde_2c), anterograde_2c) 
colnames(anterograde_2c_test)[1] <- "id"
anterograde_2c_test <- anterograde_2c_test %>% pivot_longer(AA:VP)

anterograde_2coa <- anterograde_2c[, colnames(anterograde_2c) %in% c("group", 
                                                                     "plCoAa", "plCoAm", "plCoAp")]
colnames(anterograde_2coa) <- c("group", "aplCoA", "mplCoA", "pplCoA")

summary_anterograde_2coa <- cbind.data.frame(c(rep("aplCoA", times = 3), rep("pplCoA", times = 3)),
                                             rep(c("aplCoA", "mplCoA", "pplCoA"), times = 2),
                                             c(mean(anterograde_2coa[1:5,2]),
                                               mean(anterograde_2coa[1:5,3]),
                                               mean(anterograde_2coa[c(1:3,5),4]),
                                               mean(anterograde_2coa[6:9,2]),
                                               mean(anterograde_2coa[6:9,3]),
                                               mean(anterograde_2coa[6:9,4])),
                                             c(sd(anterograde_2coa[1:5,2])/sqrt(5),
                                               sd(anterograde_2coa[1:5,3])/sqrt(5),
                                               sd(anterograde_2coa[c(1:3,5),4])/sqrt(4),
                                               sd(anterograde_2coa[6:9,2])/sqrt(4),
                                               sd(anterograde_2coa[6:9,3])/sqrt(4),
                                               sd(anterograde_2coa[6:9,4])/sqrt(4)))
colnames(summary_anterograde_2coa) <- c("group", "name", "value", "sem")

anterograde_2coa <- anterograde_2coa %>% pivot_longer(aplCoA:pplCoA)

ggplot(anterograde_2coa, aes(x = group, y = value, fill = name)) +
  geom_bar(stat = "summary", position = "dodge") + 
  geom_errorbar(aes(ymin = value - sem, ymax = value + sem), 
                data = summary_anterograde_2coa, width = .5, 
                position = position_dodge(width = 0.9)) +
  geom_point(aes(group = name), shape = 21, color = 'black', position = position_dodge(width = .9)) +
  scale_fill_manual(values = c(anterior_color, mid_color, posterior_color)) +
  xlab("") + ylab("Output proportion") +
  scale_y_continuous(expand = c(0,0), limits = c(0, .27)) +
  theme_classic() +
  theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

## Everywhere else fluorescence

```{r 25-brain_2color, message = FALSE, warning = FALSE, fig.height = 2, fig.width = 2}
# set up the object with pointers
anterograde_2noncoa <- anterograde_2c[, colnames(anterograde_2c) %in% 
                                        c("group", "MeA", "Nac")]

mea_test <- t.test(x = anterograde_2noncoa$MeA[anterograde_2noncoa$group == "aplCoA"],
       y = anterograde_2noncoa$MeA[anterograde_2noncoa$group == "pplCoA"])

nac_test <- t.test(x = anterograde_2noncoa$Nac[anterograde_2noncoa$group == "aplCoA"],
       y = anterograde_2noncoa$Nac[anterograde_2noncoa$group == "pplCoA"])

summary_anterograde_2noncoa <- cbind.data.frame(c(rep("aplCoA", times = 2), 
                                                  rep("pplCoA", times = 2)),
                                                c(rep(colnames(anterograde_2noncoa[2:3]), 
                                                      times = 2)),
                                                c(colMeans(anterograde_2noncoa[1:5,2:3], 
                                                           na.rm = TRUE),
                                                  colMeans(anterograde_2noncoa[6:9,2:3], 
                                                           na.rm = TRUE)),
                                                c(apply(anterograde_2noncoa[1:5,2:3], 2, 
                                                        function(x) sd(x, na.rm = TRUE) /
                                                          sum(!is.na(x))),
                                                  apply(anterograde_2noncoa[6:9,2:3], 2, 
                                                        function(x) sd(x, na.rm = TRUE) / 
                                                          sum(!is.na(x)))))
colnames(summary_anterograde_2noncoa) <- c("group", "name", "value", "sem")

anterograde_2noncoa <- anterograde_2noncoa %>% pivot_longer(!group)

ggplot(anterograde_2noncoa, aes(x = name, y = value, group = group, colour = group)) + 
  geom_bar(stat = "summary", width = 0.7, position = position_dodge(width=0.8), fill = NA) +
    geom_errorbar(aes(ymin = value - sem, ymax = value + sem), data = summary_anterograde_2noncoa, 
                  width = 0.3, position = position_dodge(width = 0.8), colour = "black") +
    geom_point(aes(fill = group, group = group), shape = 21, color = 'black', 
               position = position_dodge(width = 0.8)) +
    scale_y_continuous(expand = c(0,0), limits = c(0, .08)) +
    scale_colour_manual(values = c(anterior_color, posterior_color)) +
    scale_fill_manual(values = c(anterior_color, posterior_color)) +
    xlab("") +
    ylab("Output proportion") +
    theme_classic() +
    theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.x = element_text(colour = "black"),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

# Two color anterograde projection mapping

## plCoA zone fluorescence

```{r 26-plCoA_zones_2color, message = FALSE, warning = FALSE, fig.height = 3.2, fig.width = 18}
# set up the object with pointers
anterograde_cre <- read.csv("data/projections/anterograde_cre.csv", row.names = 1)

anterograde_cre_nonamy <- anterograde_cre[, !colnames(anterograde_cre) %in% 
                                        c("BMA", "plCoAa", "plCoAm", "plCoAp", "NAc")]

summary_anterograde_cre_nonamy  <- cbind.data.frame(c(rep("Slc17a6-Cre", times = 16), 
                                                  rep("Slc17a7-Cre", times = 16)),
                                                  rep(colnames(anterograde_cre_nonamy[2:17]), 
                                                      times = 2),
                                             c(colMeans(anterograde_cre_nonamy[1:4,2:17], 
                                                           na.rm = TRUE),
                                                  colMeans(anterograde_cre_nonamy[5:9,2:17], 
                                                           na.rm = TRUE)),
                                                c(apply(anterograde_cre_nonamy[1:4,2:17], 2, 
                                                        function(x) sd(x, na.rm = TRUE) /
                                                          sum(!is.na(x))),
                                                  apply(anterograde_cre_nonamy[5:9,2:17], 2, 
                                                        function(x) sd(x, na.rm = TRUE) / 
                                                          sum(!is.na(x)))))
colnames(summary_anterograde_cre_nonamy) <- c("group", "name", "value", "sem")

anterograde_cre_nonamy <- anterograde_cre_nonamy %>% pivot_longer(!group)
```

```{r 27-nacmea_solo, message = FALSE, warning = FALSE, fig.height = 2.5, fig.width = 2.6}
ggplot(anterograde_cre_nonamy[anterograde_cre_nonamy$name %in% c("Nac", "MeA"),], aes(x = name, y = value, group = group, colour = group)) +
  geom_bar(stat = "summary", width = 0.7, position = position_dodge(width=0.8), fill = NA) +
  geom_errorbar(aes(ymin = value - sem, ymax = value + sem), 
                data = summary_anterograde_cre_nonamy[summary_anterograde_cre_nonamy$name %in% c("Nac", "MeA"),], width = .5, 
                position = position_dodge(width = 0.8), color = "black") +
  geom_point(aes(fill = group, group = group), shape = 21, color = 'black', 
               position = position_dodge(width = 0.8)) +
  scale_colour_manual(values = c(VGlut2_color, VGlut1_color)) +
  scale_fill_manual(values = c(VGlut2_color, VGlut1_color)) +
  xlab("") + ylab("Output proportion") +
  scale_y_continuous(expand = c(0,0), limits = c(0, 14)) +
  theme_classic() +
  theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

```{r 28-vg1vg2_solo, message = FALSE, warning = FALSE, fig.height = 2.5, fig.width = 2.6}
ggplot(anterograde_cre_nonamy[anterograde_cre_nonamy$name %in% c("Nac", "MeA"),], aes(x = group, y = value, group = name, colour = name)) +
  geom_bar(stat = "summary", width = 0.7, position = position_dodge(width=0.8), fill = NA) +
  geom_errorbar(aes(ymin = value - sem, ymax = value + sem), 
                data = summary_anterograde_cre_nonamy[summary_anterograde_cre_nonamy$name %in% c("Nac", "MeA"),], width = .5, 
                position = position_dodge(width = 0.8), color = "black") +
  geom_point(aes(fill = name, group = name), shape = 21, color = 'black', 
               position = position_dodge(width = 0.8)) +
  scale_colour_manual(values = c(mea_color, nac_color)) +
  scale_fill_manual(values = c(mea_color, nac_color)) +
  xlab("") + ylab("Output proportion") +
  scale_y_continuous(expand = c(0,0), limits = c(0, 14)) +
  theme_classic() +
  theme(legend.position="none",
          axis.ticks.x=element_blank(),
          axis.text.y = element_text(colour = "black"),
          strip.background = element_blank())
```

```{r 29-vg1_solo, message = FALSE, warning = FALSE}
anterograde_cre_nonamy_vg1 <- anterograde_cre_nonamy[anterograde_cre_nonamy$group %in% "Slc17a7-Cre",]

anterograde_cre_nonamy_vg2 <- anterograde_cre_nonamy[anterograde_cre_nonamy$group %in% "Slc17a6-Cre",]

t.test(x = anterograde_cre_nonamy_vg1$value[ anterograde_cre_nonamy_vg1$name == "Nac"],
       y = anterograde_cre_nonamy_vg2$value[ anterograde_cre_nonamy_vg2$name == "Nac"])

t.test(x = anterograde_cre_nonamy_vg1$value[ anterograde_cre_nonamy_vg1$name == "MeA"],
       y = anterograde_cre_nonamy_vg2$value[ anterograde_cre_nonamy_vg2$name == "MeA"])

t.test(x = anterograde_cre_nonamy_vg1$value[ anterograde_cre_nonamy_vg1$name == "Nac"],
       y = anterograde_cre_nonamy_vg1$value[ anterograde_cre_nonamy_vg1$name == "MeA"])

t.test(x = anterograde_cre_nonamy_vg2$value[ anterograde_cre_nonamy_vg2$name == "Nac"],
       y = anterograde_cre_nonamy_vg2$value[ anterograde_cre_nonamy_vg2$name == "MeA"])
```
