---
author: "James Howe"
params:
  id: "plCoA"
  class: "GABA"
  path: "output/sequencing/03-processed_datasets-RNA/"
  dimn: 21
title: "GABA cell type classification (final): `r params$id`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook assigns broad identities based on well-known marker genes, consolidates them into legible identities, and then exports them for subclustering within their broad identities.

```{r setup, message = FALSE, warning = FALSE}
id <- params$id
cell_class <- params$class
path <- params$path
dimn <- params$dimn

source("code/sequencing_misc.R")
source("code/sequencing-color_scales.R")
source("code/sequencing-plot_functions.R")

require(Seurat)
require(tidyverse)
require(knitr)
require(scCustomize)
require(clustree)
require(chisq.posthoc.test)
require(speckle)
require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)
require(colorRamps)
require(Libra)
require(enrichR)
require(EnhancedVolcano)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 02

Imports the merged and transformed Seurat object from step 02. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already.

```{r 1-read_integrated_data, message = FALSE, warning = FALSE}
array <- readRDS(paste0(path, id, "_", cell_class, "_reprocessed_RNA.rds"))
```

# Cluster nuclei {.tabset}

Clusters nuclei using Seurat's implementation of the Leiden clustering algorithm (see methods for references), which improves upon the more traditional Louvain algorithm. Clustering is performed at a variety of resolutions so that the best can be chosen from among the different results, ensuring optimal cluster assignments prior to downstream segmentation. 

```{r 2-leiden_clustering, message = FALSE, warning = FALSE}
array <- FindNeighbors(array, dims = 1:dimn, k.param = 30, verbose = FALSE)

res_index <- c(0.01, seq(0.1, 1, 0.1))
for (i in 1:length(res_index)){
  array <- FindClusters(array, method = 4, resolution = res_index[i], verbose = FALSE)
}
```

## Clustree {.tabset}

### Standard

```{r 3-clustree_standard, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 14}
clustree(array, prefix = "SCT_snn_res.")
```

### Stability

```{r 4-clustree_stability, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 14}
clustree(array, prefix = "SCT_snn_res.", node_colour = "sc3_stability")
```

## Scatter {.tabset}

### PCA {.tabset}

```{r 5-pca_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r pca-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'pca', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### tSNE {.tabset}

```{r 6-tsne_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r tsne-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'tsne', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### UMAP {.tabset}

```{r 7-umap_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r umap-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'umap', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Annotate clusters

## Select optimal resolution

Optimal resolution can be selected by examining clustering on dimension-reduced data to determine if they match visual clustering. Further, clustree (and its packaged stability metric) can be used to find the highest resolution that does not lose stability, providing an optimal balance between over- and under-clustering. It is difficult to automate this without some degree of supervision or hand-curation. This is mostly to identify large clusters, so there is little need to get extremely specific so long as clusters are coherent.

```{r 8-select_resolution, message = FALSE, warning = FALSE}
optimal_res <- 0.5

clusters <- array[[paste0("SCT_snn_res.", optimal_res)]]
array[["seurat_clusters"]] <- NULL
for (i in 1:11){
  array[[paste0("SCT_snn_res.", res_index[i])]] <- NULL 
}
array <- AddMetaData(array, clusters, col.name = "clusters")
Idents(array) <- "clusters"

# helps downstrean formatting to regenerate cluster vector from the array vector
type_clusters_marker <- type_clusters <- as.character(array$clusters)

paste(optimal_res, "is optimal clustering resolution")
```

## Identify marker genes

```{r 9-find_markers, message = FALSE, warning = FALSE, results = "hide"}
pct_expressed_aplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$clusters), 
                 function(x) rowSums(array@assays$RNA@counts[, array$clusters == x & array$Region == "aplCoA"] != 0) 
                             / length(array$clusters[array$clusters == x & array$Region == "aplCoA"]))))

pct_expressed_pplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$clusters), 
                 function(x) rowSums(array@assays$RNA@counts[, array$clusters == x & array$Region == "pplCoA"] != 0) 
                             / length(array$clusters[array$clusters == x & array$Region == "pplCoA"]))))

pct_expressed <- pmax(pct_expressed_aplCoA, pct_expressed_pplCoA)

colnames(pct_expressed) <- levels(array$clusters)

rm(pct_expressed_aplCoA, pct_expressed_pplCoA)


# find de novo markers, clusters
marker_type <- markers_sc_wilcox(array, "clusters")

# find regional markers within cell types
marker_type_region <- markers_pb_edgeRLRT(array, "clusters", 0.1)
```

## Select marker genes

```{r 10-choose_markers, message = FALSE, warning = FALSE, results = "hide"}
# region-specific
marker_type_region_aplCoA <- lapply(marker_type_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC > 0.585,]})
marker_type_region_pplCoA <- lapply(marker_type_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC < -0.585,]})

# based on numbers for max of each one
#deg_range_type <- c(0, 75)

markers_list <- c("Slc17a7", "Slc17a6", # glutamatergic neuron
                  "Gad1", "Gad2", # GABAergic neurons
                  "Lamp5", "Il1rap", "Crispld1", # 0
                  "Nxph2", "Slit3", "Ndst4", # 1
                  "Vip", "Plpp4", "Sema5b", # 2
                  "Sst", "Man1a", "L3mbtl4", # 3
                  "Ralyl", "Nell2", "Fat3", # 4
                  "Slc16a2", "Pde3a", "Sema3e", # 5
                  "Npas1", "Syt6", "Cck", # 6
                  "Tacr1", "Unc5b", "Hs3st4", # 7
                  "Pdzrn3", "Cadps2", "Rgs12", # 8
                  "Vcan", "Dchs2", "Kcns3", # 9
                  "Npsr1", "Ptprk", "Chrm2", # 10
                  "Spon1", "Fign", "Fbn2", # 11
                  "Rai14", "Chst9", "Foxp2") # 12

markers_list_display <- c("Gad1", "Gad2", # GABAergic neurons
                          "Lamp5", "Crispld1", # 0
                          "Nxph2", "Slit3", # 1
                          "Vip", "Plpp4", # 2
                          "Sst", "L3mbtl4", # 3
                          "Nell2", "Fat3", # 4
                          "Slc16a2", "Pde3a", # 5
                          "Syt6", "Cck", # 6
                          "Tacr1", "Unc5b", # 7
                          "Pdzrn3", "Rgs12", # 8
                          "Vcan", "Kcns3", # 9
                          "Npsr1", "Chrm2", # 10
                          "Spon1", "Fbn2", # 11
                          "Rai14", "Foxp2") # 12

markers_list_display_half <- c("Gad1",  # GABAergic neurons
                          "Vcan", # 10
                          "Lamp5",  # 1
                          "Pdzrn3", # 9
                          "Vip",  # 3
                          "Cck", # 7
                          "Spon1", # 12
                          "Sst", # 4
                          "Nxph2", # 2
                          "Slc16a2", # 6
                          "Nell2", # 5
                          "Npsr1",  # 11
                          "Tacr1", # 8
                          "Foxp2") # 13
```

# Consolidate clusters

Based on known marker gene expression, assign broad cellular identities to clusters at the optimal resolution selected. These identities are hand-assigned, and multiple clusters are in many cases combined into broad cellular identities due to uneven differences between cell types.

```{r 11-consolidate_clusters, message = FALSE, warning = FALSE}
type_clusters[type_clusters %in% "0"] <- "GABA.1"
type_clusters_marker[type_clusters_marker %in% "0"] <- "GABA.Lamp5"
names(marker_type)[1] <- "GABA.1 | GABA.Lamp5"

type_clusters[type_clusters %in% "1"] <- "GABA.2"
type_clusters_marker[type_clusters_marker %in% "1"] <- "GABA.Nxph2"
names(marker_type)[2] <- "GABA.2 | GABA.Nxph2"

type_clusters[type_clusters %in% "2"] <- "GABA.3"
type_clusters_marker[type_clusters_marker %in% "2"] <- "GABA.Vip"
names(marker_type)[3] <- "GABA.3 | GABA.Vip"

type_clusters[type_clusters %in% "3"] <- "GABA.4"
type_clusters_marker[type_clusters_marker %in% "3"] <- "GABA.Sst"
names(marker_type)[4] <- "GABA.4 | GABA.Sst"

type_clusters[type_clusters %in% "4"] <- "GABA.5"
type_clusters_marker[type_clusters_marker %in% "4"] <- "GABA.Nell2"
names(marker_type)[5] <- "GABA.5 | GABA.Nell2"

type_clusters[type_clusters %in% "5"] <- "GABA.6"
type_clusters_marker[type_clusters_marker %in% "5"] <- "GABA.Slc16a2"
names(marker_type)[6] <- "GABA.6 | GABA.Slc16a2"

type_clusters[type_clusters %in% "6"] <- "GABA.7"
type_clusters_marker[type_clusters_marker %in% "6"] <- "GABA.Cck"
names(marker_type)[7] <- "GABA.7 | GABA.Cck"

type_clusters[type_clusters %in% "7"] <- "GABA.8"
type_clusters_marker[type_clusters_marker %in% "7"] <- "GABA.Tacr1"
names(marker_type)[8] <- "GABA.8 | GABA.Tacr1"

type_clusters[type_clusters %in% "8"] <- "GABA.9"
type_clusters_marker[type_clusters_marker %in% "8"] <- "GABA.Pdzrn3"
names(marker_type)[9] <- "GABA.9 | GABA.Pdzrn3"

type_clusters[type_clusters %in% "9"] <- "GABA.10"
type_clusters_marker[type_clusters_marker %in% "9"] <- "GABA.Vcan"
names(marker_type)[10] <- "GABA.10 | GABA.Vcan"

type_clusters[type_clusters %in% "10"] <- "GABA.11"
type_clusters_marker[type_clusters_marker %in% "10"] <- "GABA.Npsr1"
names(marker_type)[11] <- "GABA.11 | GABA.Npsr1"

type_clusters[type_clusters %in% "11"] <- "GABA.12"
type_clusters_marker[type_clusters_marker %in% "11"] <- "GABA.Spon1"
names(marker_type)[12] <- "GABA.12 | GABA.Spon1"

type_clusters[type_clusters %in% "12"] <- "GABA.13"
type_clusters_marker[type_clusters_marker %in% "12"] <- "GABA.Foxp2"
names(marker_type)[13] <- "GABA.13 | GABA.Foxp2"

# switch based on different levels
names(marker_type_region_aplCoA)[1:2] <- names(marker_type)[1:2]
names(marker_type_region_aplCoA)[3:4] <- names(marker_type)[11:12]
names(marker_type_region_aplCoA)[5:12] <- names(marker_type)[3:10]
names(marker_type_region) <- names(marker_type_region_pplCoA) <- names(marker_type_region_aplCoA)


# replace clusters with curated types
array <- AddMetaData(array, as.factor(type_clusters), col.name = "Type")
array <- AddMetaData(array, as.factor(type_clusters_marker), col.name = "Type.Marker")

array$Type <- factor(array$Type, levels = c("GABA.1", "GABA.2", "GABA.3",
                                            "GABA.4", "GABA.5", "GABA.6",
                                            "GABA.7", "GABA.8", "GABA.9",
                                            "GABA.10", "GABA.11", "GABA.12", "GABA.13"))
array$Type.Marker <- factor(array$Type.Marker, levels = c("GABA.Lamp5", "GABA.Nxph2", "GABA.Vip",
                                                        "GABA.Sst", "GABA.Nell2", "GABA.Slc16a2",
                                                          "GABA.Cck", "GABA.Tacr1", "GABA.Pdzrn3",
                                                          "GABA.Vcan", "GABA.Npsr1", "GABA.Spon1",
                                                          "GABA.Foxp2"))

Idents(array) <- "Type"

plot_group_array <- cbind.data.frame(array$Type,
                                     array$orig.ident,
                                     array$Region,
                                     array$Type.Marker)
colnames(plot_group_array) <- c("Type", "Batch", "Region", "Type.Marker")

table(array$Type)
```

# Visualize consolidated clusters {.tabset}

```{r 12-dr_consolidated, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "## {{tab_name}} {.unnumbered}",
        "```{r type-{{tab_name}}, message = FALSE, warning = FALSE}",
        "cluster_plot_formatted(array, '{{dr_type}}', 'Type', gaba_type_colors2)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Show gene expression information

## Volcano (region markers) {.tabset}

### Unlabeled {.tabset}

```{r 13-volcano_unlabeled, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
src_list <- lapply(names(marker_type_region), function(clusters) {
    src <- c(
        "#### {{clusters}} {.unnumbered}",
        "```{r volcano-unlabeled-{{clusters}}, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}",
        "enhanced_volcano_plot(marker_type_region[['{{clusters}}']], 
                               title_id = paste('{{clusters}}'), label_size = 0)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Labeled {.tabset}

```{r 14-volcano_labeled, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
src_list <- lapply(names(marker_type_region), function(clusters) {
    src <- c(
        "#### {{clusters}} {.unnumbered}",
        "```{r volcano-labeled-{{clusters}}, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}",
        "enhanced_volcano_plot(marker_type_region[['{{clusters}}']], 
                               title_id = paste('{{clusters}}'), label_size = 1)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## List {.tabset}

### Type {.tabset}

```{r 15-markers_list_type, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_type), function(group) {
    src <- c(
        "#### {{group}} {.unnumbered}",
        "```{r marker-type-{{group}}, message = FALSE, warning = FALSE}",
        "marker_type[['{{group}}']]",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Region {.tabset}

#### aplCoA {.tabset}

```{r 16-markers_list_aplCoA, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_type_region_aplCoA), function(group) {
    src <- c(
        "##### {{group}} {.unnumbered}",
        "```{r marker-type-aplCoA-{{group}}, message = FALSE, warning = FALSE}",
        "marker_type_region_aplCoA[['{{group}}']]",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

#### pplCoA {.tabset}

```{r 17-markers_list_pplCoA, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_type_region_pplCoA), function(group) {
    src <- c(
        "##### {{group}} {.unnumbered}",
        "```{r marker-type-pplCoA-{{group}}, message = FALSE, warning = FALSE}",
        "marker_type_region_pplCoA[['{{group}}']]",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Scatter {.tabset}

### PCA {.tabset}

```{r 18-pca_markers, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r pca-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'pca', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### tSNE {.tabset}

```{r 19-tsne_markers, message = FALSE, warning = FALSE, results = "hide", }
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r tsne-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'tsne', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### UMAP {.tabset}

```{r 20-umap_markers, message = FALSE, warning = FALSE, results = "hide", }
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r umap-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'umap', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## DEG Abundance {.tabset}

### aplCoA

```{r 21-deg_abundance_magnitude_type_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
# not enough DEGs, cannot run these plots

#deg_abundance_plot_magnitude(marker_type_region_aplCoA, deg_intensity_colors_aplCoA, deg_range_type, "aplCoA")
```

### pplCoA

```{r 22-deg_abundance_magnitude_type_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
#deg_abundance_plot_magnitude(marker_type_region_pplCoA, deg_intensity_colors_pplCoA, deg_range_type, "pplCoA")
```


# Visualize consolidated cluster composition

## Absolute Composition {.tabset}

```{r 23-type_absolute, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(br, br_colors) {
    src <- c(
        "### {{br}} {.unnumbered}",
        "```{r class-absolute-{{br}}, message = FALSE, warning = FALSE}",
        "absolute_bar_plot_formatted(plot_group_array, 'Type', '{{br}}', {{br_colors}})",  
        "```",
        ""
    )
    knit_expand(text = src)
}, batch_region, batch_color_list)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Relative Composition {.tabset}

### Bar {.tabset}

#### Batch

```{r 24-type_relative_batch, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 3.5}
relative_bar_plot_formatted(plot_group_array, 'Type', 'Batch', batch_colors_rna)
```

#### Region {.tabset}

##### Unordered

```{r 25-type_relative_region, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 7}
relative_bar_plot_formatted(plot_group_array, 'Type', 'Region', region_colors) + 
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

##### Ordered

```{r 26-region_relative_ranked_ordered, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 7}
relative_bar_plot_formatted_ranked(plot_group_array, 'Type', 'Region', region_colors) +
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

##### Ordered (marker name)

```{r 27-region_relative_ranked_ordered_marker, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 7}
relative_bar_plot_formatted_ranked(plot_group_array, 'Type.Marker', 'Region', region_colors) +
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

#### Chi-square results

```{r 28-chi_square_class, message = FALSE, warning = FALSE}
chisq_table <- table(array$Region, array$Type)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")

# can't do propeller w/ only two groups, so skip here (if it doesn't pass chi-sq though, likely won't pass propeller)
```

#### Propeller results

```{r 29-propeller_type, message = FALSE, warning = FALSE}
props <- propeller(array, clusters = array$Type, sample = array$orig.ident, group = array$Region)

prop_table <- cbind.data.frame(rownames(props), props$BaselineProp.Freq*100, props$Tstatistic, props$FDR,
                               ifelse(props$FDR > 0.05, "ns", ifelse(
                                 props$FDR > 0.01, "*", ifelse(
                                   props$FDR > 0.001, "**", ifelse(
                                     props$FDR > 0.0001, "***", "****"
                               )))))
colnames(prop_table) <- c("Type", "% Freq", "F-statistic", "FDR", "Significance")

prop_table
```

### Region {.tabset}

#### Absolute

```{r 30-region_relative, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
absolute_bar_plot_formatted(plot_group_array, 'Region', 'Type', gaba_type_colors2)
```

#### Relative

```{r 31-region_relative, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
relative_bar_plot_formatted(plot_group_array, 'Region', 'Type', gaba_type_colors2) +
  geom_hline(yintercept = table(array$Type)[2] / length(array$Type), linetype = "dashed")
```

#### Chi-square results

```{r 32-chi_square_region, message = FALSE, warning = FALSE}
chisq_table <- table(array$Type, array$Region)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")
```

### Batch {.tabset}

#### Absolute

```{r 33-region_relative, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
absolute_bar_plot_formatted(plot_group_array, 'Batch', 'Type', gaba_type_colors2)
```

#### Relative

```{r 34-region_relative, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
relative_bar_plot_formatted(plot_group_array, 'Batch', 'Type', gaba_type_colors2)
```

#### Chi-square results

```{r 35-chi_square_region, message = FALSE, warning = FALSE}
chisq_table <- table(array$Type, array$orig.ident)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")
```

## Examine metrics for consolidated clusters {.tabset}

```{r 36-vln_consolidated_type, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(metric, label) {
    src <- c(
        "### {{label}} {.unnumbered}",
        "```{r vln-type-{{metric}}, message = FALSE, warning = FALSE}",
        "violin_metrics_formatted(array, 'Type', '{{metric}}', '{{label}}', gaba_type_colors2)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, vln_metrics$id, vln_metrics$label)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Visualize marker genes in consolidated clusters {.tabset}

## Dot plot {.tabset}

```{r 37-dot_tg, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
array <- PrepSCTFindMarkers(array)

array <- AddMetaData(array, array$Type, col.name = "Type.Display")
array$Type.Display <- factor(array$Type.Display, levels = rev(c("GABA.10", "GABA.1", "GABA.9",
                                                            "GABA.3", "GABA.7", "GABA.12",
                                                            "GABA.4", "GABA.2", "GABA.6",
                                                            "GABA.5", "GABA.11", "GABA.8",
                                                            "GABA.13")))

markers_list_display <- c("Slc17a7", "Slc17a6",
                          "Ntng1", "Sema3a", "Ccbe1", "Zfp536", "Ror1", "Smoc1", 
                          "Satb2", "Vwc2", "Etv1", "Ebf2", "Adarb2", "Ebf1", "Gpc5", "Sim1")

Idents(array) <- "Type.Display"
DotPlot_scCustom(array, features = markers_list_display_half, colors_use = dotplot_colors) + 
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

Idents(array) <- "Type"
```

## Stacked Violin {.tabset}

### All markers

```{r 38-stacked_vln_marker, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
VlnPlot(array, features = markers_list, 
        pt.size = 0, stack = TRUE, flip = TRUE, 
        group.by = 'Type') + 
        theme(legend.position = 'none')
```

## Heatmap

```{r 39-heatmap_marker, message = FALSE, warning = FALSE, results = "hide", dev = "png", fig.height = 8, fig.width = 16}
DoHeatmap(array, features = markers_list, group.by = 'Type', size = 0,
          group.colors = gaba_type_colors2) +
          scale_fill_gradientn(colours = heatmap_colors) +  
          scale_colour_manual(values = gaba_type_colors2)
```

`r out`

# Visualize cluster distances {.tabset}

## Dendrogram {.tabset}

### Region

```{r 40-region_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
region_dend <- create_dendrogram(array, as.factor(array$Region), region_colors)

plot(region_dend[[2]], axes = FALSE)
```

### Batch

```{r 41-library_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
batch_dend <- create_dendrogram(array, as.factor(array$orig.ident), batch_colors_rna)

plot(batch_dend[[2]], axes = FALSE)
```

### Type

```{r 42-type_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
type_dend <- create_dendrogram(array, as.factor(array$Type), gaba_type_colors2)

plot(type_dend[[2]], axes = FALSE)
```

### Type with Region ID

```{r 43-type_dendrogram_region, message = FALSE, warning = FALSE, results = "hide"}
# create region+class convolution ID
#array <- AddMetaData(array, metadata = paste(array$Region, array$Type), col.name = "Region_Type")

#type_region_dend <- create_dendrogram(array, as.factor(array$Region_Type), region_gaba_type_colors2)

#plot(type_region_dend[[2]], axes = FALSE)
```

## Cluster distance heatmap {.tabset}

### Region {.tabset}

#### Distance

```{r 44-cluster_heatmap_region_dist, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(region_dend, method_id = "distance")
```

#### Correlation

```{r 45-cluster_heatmap_region_cor, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(region_dend, method_id = "correlation")
```

### Batch {.tabset}

#### Distance

```{r 46-cluster_heatmap_batch_dist, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(batch_dend, method_id = "distance")
```

#### Correlation

```{r 47-cluster_heatmap_batch_cor, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(batch_dend, method_id = "correlation")
```

### Type {.tabset}

#### Distance

```{r 48-cluster_heatmap_type_dist, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(type_dend, method_id = "distance")
```

#### Correlation

```{r 49-cluster_heatmap_type_cor, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(type_dend, method_id = "correlation")
```

### Type with Region ID {.tabset}

#### Distance

```{r 50-cluster_heatmap_region_dist, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
#dendrogram_heatmap(type_region_dend, method_id = "distance")
```

#### Correlation

```{r 51-cluster_heatmap_region_cor, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
#dendrogram_heatmap(type_region_dend, method_id = "correlation")
```

## Pseudobulk PCA {.tabset}

### Batch

```{r 52-pseudobulk_pca_batch, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "orig.ident", "Batch", batch_colors_rna)
```

### Type

```{r 53-pseudobulk_pca_type, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "Type", "Type", gaba_type_colors2)
```

### Region-Type

```{r 54-pseudobulk_pca_region-type, message = FALSE, warning = FALSE, results = "hide"}
#pseudobulk_pca(array, "Region_Type", "Region_Type", region_gaba_type_colors2)
```

# Colored by type {.tabset}

# Abundance Plot

```{r 55-abundance_ordered, message = FALSE, warning = FALSE, fig.height = 2, fig.width = 10}
type_vector <- as.data.frame(table(array$Type.Display))

ggplot(type_vector, aes(Var1, fill = Var1)) +
       ylab("Nuclei") +
       geom_bar(aes(weight = Freq)) + scale_y_continuous(expand = c(0,0)) +
       scale_fill_manual(values = gaba_type_colors2_display) +
       theme_classic() +  theme(axis.ticks.x = element_blank(), legend.position="none",
                                axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

## Scatter {.tabset}

```{r 56-dr_colored_type, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "### {{tab_name}} {.unnumbered}",
        "```{r class-{{tab_name}}, message = FALSE, warning = FALSE}",
        "cluster_plot_formatted(array, '{{dr_type}}', 'Type', gaba_type_colors2)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

# Split matrix into constituent parts and save

```{r 57-save_matrices, message = FALSE, warning = FALSE, results = "hide"}
# save cluster assignments, do not need whole array
cluster_file <- cbind.data.frame(array$Tissue, array$Class, array$Type, array$Type.Marker)
colnames(cluster_file) <- c("Tissue", "Class", "Type", "Type.Marker")
write.csv(cluster_file, file = "output/sequencing/cluster_lists/05M-GABA_type_clusters.csv", col.names = TRUE)

# save DEGs
for (i in 1:length(names(marker_type))){
  write.csv(marker_type[[i]], 
            file = paste0("output/sequencing/marker_lists/cell_type/", names(marker_type)[i], ".csv"))
}

# save the overgroups/tissues
for (i in 1:length(names(marker_type_region_aplCoA))){
    write.csv(marker_type_region_aplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_type_region_aplCoA)[i], "_aplCoA.csv")) 
}

for (i in 1:length(names(marker_type_region_pplCoA))){
  for (j in 1:length(names(marker_type_region_pplCoA[[i]]))){
    write.csv(marker_type_region_pplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_type_region_pplCoA)[i], "_pplCoA.csv"))
  }
}

```
