---
author: "James Howe"
params:
  id: "plCoA"
  input_path: "output/sequencing/03-processed_datasets-RNA/"
  output_path: "output/sequencing/04-subcluster_datasets-RNA/"
title: "Reclassification and merging of clusters: `r params$id`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook assigns broad identities based on well-known marker genes, consolidates them into legible identities, and then exports them for subclustering within their broad identities.

```{r setup, message = FALSE, warning = FALSE}
id <- params$id
input <- paste0(params$input_path, id)
output <- params$output_path
dimn <- params$dimn

source("code/sequencing_misc.R")
source("code/sequencing-color_scales.R")
source("code/sequencing-plot_functions.R")

require(Seurat)
require(tidyverse)
require(knitr)
require(scCustomize)
require(clustree)
require(chisq.posthoc.test)
require(speckle)
require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)
require(colorRamps)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 02

Imports the merged and transformed Seurat object from step 02. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already.

```{r 1-read_integrated_data, message = FALSE, warning = FALSE}
array <- readRDS("output/sequencing/04-subcluster_datasets-RNA/plCoA_all_RNA.rds")
```

# Import annotation {.tabset}

Adds annotation from lower level clusters.

```{r 2-import_annotate, message = FALSE, warning = FALSE}
# neuron vs nonneuron
neuron_clusters <- read.csv("output/sequencing/cluster_lists/04C-Neuron_class_clusters.csv", row.names = 1)
nonneuron_clusters <- read.csv("output/sequencing/cluster_lists/03F-Nonneuron_class_clusters.csv", row.names = 1)

# type annotation
glut_clusters <- read.csv("output/sequencing/cluster_lists/05L-Glut_type_clusters.csv", row.names = 1)
gaba_clusters <- read.csv("output/sequencing/cluster_lists/05M-GABA_type_clusters.csv", row.names = 1)
astro_clusters <- read.csv("output/sequencing/cluster_lists/05N-Astro_type_clusters.csv", row.names = 1)
macro_clusters <- read.csv("output/sequencing/cluster_lists/05O-Macro_type_clusters.csv", row.names = 1)
nfol_clusters <- read.csv("output/sequencing/cluster_lists/05P-NFOL_type_clusters.csv", row.names = 1)
mol_clusters <- read.csv("output/sequencing/cluster_lists/05Q-MOL_type_clusters.csv", row.names = 1)
abc_clusters <- read.csv("output/sequencing/cluster_lists/05R-ABC_type_clusters.csv", row.names = 1)
vlmc_clusters <- read.csv("output/sequencing/cluster_lists/05S-VLMC_type_clusters.csv", row.names = 1)

# replace classes
array <- AddMetaData(array, metadata = as.character(array$Tissue), col.name = "Class")

array$Class[array$Class == "Neuron"] <- neuron_clusters$Class
array$Class[array$Class == "Nonneuron"] <- nonneuron_clusters$Class

# replace types
array <- AddMetaData(array, metadata = array$Class, col.name = "Type")
array <- AddMetaData(array, metadata = array$Class, col.name = "Type_Marker")

array$Type[array$Type %in% "Glut"] <- glut_clusters$Type
array$Type_Marker[array$Type_Marker == "Glut"] <- glut_clusters$Type.Marker

array$Type[array$Type %in% "GABA"] <- gaba_clusters$Type
array$Type_Marker[array$Type_Marker == "GABA"] <- gaba_clusters$Type.Marker

array$Type[array$Type == "Astro"] <- astro_clusters$Type
array$Type_Marker[array$Type_Marker == "Astro"] <- astro_clusters$Type.Marker

array$Type[array$Type == "Macro"] <- macro_clusters$Type
array$Type_Marker[array$Type_Marker == "Macro"] <- macro_clusters$Type.Marker

array$Type[array$Type == "NFOL"] <- nfol_clusters$Type
array$Type_Marker[array$Type_Marker == "NFOL"] <- nfol_clusters$Type.Marker

array$Type[array$Type == "MOL"] <- mol_clusters$Type
array$Type_Marker[array$Type_Marker == "MOL"] <- mol_clusters$Type.Marker

array$Type[array$Type == "ABC"] <- abc_clusters$Type
array$Type_Marker[array$Type_Marker == "ABC"] <- abc_clusters$Type.Marker

array$Type[array$Type == "VLMC"] <- vlmc_clusters$Type
array$Type_Marker[array$Type_Marker == "VLMC"] <- vlmc_clusters$Type.Marker

array$Class <- factor(array$Class, levels = c("Glut", "GABA", "Astro", "Micro", "Macro", 
                                              "OPC", "NFOL", "MOL", "Endo", "Mural", "ABC", "VLMC"))

array$Type <- factor(array$Type, levels = c("Glut.1", "Glut.2", "Glut.3",
                                            "Glut.4", "Glut.5", "Glut.6",
                                            "Glut.7", "Glut.8", "Glut.9",
                                            "Glut.10", "Glut.11", "Glut.12", "Glut.13", "Glut.14",
                                            "GABA.1", "GABA.2", "GABA.3",
                                            "GABA.4", "GABA.5", "GABA.6",
                                            "GABA.7", "GABA.8", "GABA.9",
                                            "GABA.10", "GABA.11", "GABA.12", "GABA.13",
                                            "Astro.1", "Astro.2",
                                            "Micro", "Macro.1", "Macro.2", 
                                            "OPC", "NFOL.1", "NFOL.2", "MOL.1", "MOL.2", 
                                            "Endo", "Mural", 
                                            "ABC.1", "ABC.2", "ABC.3", "VLMC.1", "VLMC.2", "VLMC.3"))
array$Type_Marker <- factor(array$Type_Marker, 
                            levels = c("Glut.Zfp536", "Glut.Satb2",
                                       "Glut.Gulp1", "Glut.Fign", 
                                       "Glut.Ror1", "Glut.Reln",
                                       "Glut.Meis1", "Glut.Smoc1", "Glut.Ntng1",
                                       "Glut.Ebf1", "Glut.Vwc2", 
                                       "Glut.Ebf2", "Glut.Etv1", "Glut.Sim1",
                                       "GABA.Lamp5", "GABA.Nxph2", "GABA.Vip",
                                       "GABA.Sst", "GABA.Nell2", "GABA.Slc16a2",
                                       "GABA.Npas1", "GABA.Tacr1", "GABA.Pdzrn3",
                                       "GABA.Vcan", "GABA.Npsr1", "GABA.Spon1", "GABA.Rai14", 
                                       "Astro.Luzp2", "Astro.Myoc",
                                       "Micro", "Macro.F13a1", "Macro.Cd74", 
                                       "OPC", "NFOL.Frmd4a", "NFOL.Sgcd", "MOL.Mast4", "MOL.Prom1", 
                                       "Endo", "Mural", 
                                       "ABC.Slc4a10", "ABC.Ranbp3l", "VLMC.Mgat4c", "VLMC.Bnc2", "VLMC.Hecw2"))

plot_group_array <- cbind.data.frame(array$Tissue,
                                     array$Class,
                                     array$Type,
                                     array$orig.ident,
                                     array$Region)
colnames(plot_group_array) <- c("Tissue", "Class", "Type", "Batch", "Region")
```

# Visualize consolidated clusters {.tabset}

## Class {.tabset}

```{r 3-dr_consolidated_class, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "### {{tab_name}} {.unnumbered}",
        "```{r class-{{tab_name}}, message = FALSE, warning = FALSE}",
        "cluster_plot_formatted(array, '{{dr_type}}', 'Class', class_colors)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Type {.tabset}

```{r 4-dr_consolidated_type, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "### {{tab_name}} {.unnumbered}",
        "```{r type-{{tab_name}}, message = FALSE, warning = FALSE}",
        "cluster_plot_formatted(array, '{{dr_type}}', 'Type', type_colors)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Visualize consolidated cluster composition

## Absolute Composition {.tabset}

### Class {.tabset}

```{r 5-class_absolute, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(br, br_colors) {
    src <- c(
        "#### {{br}} {.unnumbered}",
        "```{r class-absolute-{{br}}, message = FALSE, warning = FALSE}",
        "absolute_bar_plot_formatted(plot_group_array, 'Class', '{{br}}', {{br_colors}})",  
        "```",
        ""
    )
    knit_expand(text = src)
}, batch_region, batch_color_list)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Type {.tabset}

```{r 6-type_absolute, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(br, br_colors) {
    src <- c(
        "#### {{br}} {.unnumbered}",
        "```{r type-absolute-{{br}}, message = FALSE, warning = FALSE}",
        "absolute_bar_plot_formatted(plot_group_array, 'Type', '{{br}}', {{br_colors}})",  
        "```",
        ""
    )
    knit_expand(text = src)
}, batch_region, batch_color_list)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Relative Composition {.tabset}

### Bar {.tabset}

#### Batch {.tabset}

##### Class

```{r 7-class_relative_batch, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
relative_bar_plot_formatted(plot_group_array, 'Class', 'Batch', batch_colors_rna)
```

##### Type

```{r 8-type_relative_batch, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 8}
relative_bar_plot_formatted(plot_group_array, 'Type', 'Batch', batch_colors_rna)
```

#### Region {.tabset}

##### Class

```{r 9-class_relative_region, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
relative_bar_plot_formatted(plot_group_array, 'Class', 'Region', region_colors) + 
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

##### Type

```{r 10-type_relative_region, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 8}
relative_bar_plot_formatted(plot_group_array, 'Type', 'Region', region_colors) + 
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

#### Region Ranked {.tabset}

##### Class

```{r 11-class_relative_region_ranked, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
relative_bar_plot_formatted_ranked(plot_group_array, 'Class', 'Region', region_colors) + 
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

##### Type

```{r 12-type_relative_region_ranked, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 8}
relative_bar_plot_formatted(plot_group_array, 'Type', 'Region', region_colors) + 
  geom_hline(yintercept = table(array$Region)[2] / length(array$Region), linetype = "dashed")
```

#### Chi-square results {.tabset}

##### Class

```{r 13-chi_square_class, message = FALSE, warning = FALSE}
chisq_table <- table(array$Region, array$Class)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")
```

##### Type

```{r 14-chi_square_type, message = FALSE, warning = FALSE}
chisq_table <- table(array$Region, array$Type)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")
```

#### Propeller {.tabset}

##### Class

```{r 15-propeller_class, message = FALSE, warning = FALSE}
props <- propeller(array, clusters = array$Class, sample = array$orig.ident, group = array$Region)

prop_table <- cbind.data.frame(rownames(props), props$BaselineProp.Freq*100, props$Tstatistic, props$FDR,
                               ifelse(props$FDR > 0.05, "ns", ifelse(
                                 props$FDR > 0.01, "*", ifelse(
                                   props$FDR > 0.001, "**", ifelse(
                                     props$FDR > 0.0001, "***", "****"
                               )))))
colnames(prop_table) <- c("Type", "% Freq", "F-statistic", "FDR", "Significance")

prop_table
```

##### Type

```{r 16-propeller_type, message = FALSE, warning = FALSE}
props <- propeller(array, clusters = array$Type, sample = array$orig.ident, group = array$Region)

prop_table <- cbind.data.frame(rownames(props), props$BaselineProp.Freq*100, props$Tstatistic, props$FDR,
                               ifelse(props$FDR > 0.05, "ns", ifelse(
                                 props$FDR > 0.01, "*", ifelse(
                                   props$FDR > 0.001, "**", ifelse(
                                     props$FDR > 0.0001, "***", "****"
                               )))))
colnames(prop_table) <- c("Type", "% Freq", "F-statistic", "FDR", "Significance")

prop_table
```

### Region {.tabset}

#### Absolute {.tabset}

##### Class

```{r 17-region_absolute_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 3}
absolute_bar_plot_formatted(plot_group_array, 'Region', 'Class', class_colors)
```

##### Type


```{r 18-region_absolute_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 12}
absolute_bar_plot_formatted(plot_group_array, 'Region', 'Type', type_colors)
```

#### Relative {.tabset}

##### Class

```{r 19-region_relative_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
relative_bar_plot_formatted(plot_group_array, 'Region', 'Class', class_colors)
```

##### Type

```{r 20-region_relative_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 12}
relative_bar_plot_formatted(plot_group_array, 'Region', 'Type', type_colors)
```

#### Chi-square results

```{r 21-chi_square_region, message = FALSE, warning = FALSE}
chisq_table <- table(array$Tissue, array$Region)

chisq.test(chisq_table)
chisq.posthoc.test(chisq_table, method = "bonferroni")
```

### Batch {.tabset}

#### Absolute {.tabset}

##### Class

```{r 22-region_relative_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
absolute_bar_plot_formatted(plot_group_array, 'Batch', 'Class', class_colors)
```

##### Type

```{r 23-region_relative_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 8}
absolute_bar_plot_formatted(plot_group_array, 'Batch', 'Type', type_colors)
```

#### Relative

##### Class

```{r 24-region_relative_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 4}
relative_bar_plot_formatted(plot_group_array, 'Batch', 'Class', class_colors)
```

##### Type

```{r 25-region_relative_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 8}
relative_bar_plot_formatted(plot_group_array, 'Batch', 'Type', type_colors)
```

# Examine metrics for consolidated clusters {.tabset}

## Class {.tabset}

```{r 26-vln_consolidated_class, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(metric, label) {
    src <- c(
        "### {{label}} {.unnumbered}",
        "```{r vln-class-{{metric}}, message = FALSE, warning = FALSE}",
        "violin_metrics_formatted(array, 'Class', '{{metric}}', '{{label}}', class_colors)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, vln_metrics$id, vln_metrics$label)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Type {.tabset}

```{r 27-vln_consolidated_type, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(metric, label) {
    src <- c(
        "### {{label}} {.unnumbered}",
        "```{r vln-type-{{metric}}, message = FALSE, warning = FALSE}",
        "violin_metrics_formatted(array, 'Type', '{{metric}}', '{{label}}', type_colors)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, vln_metrics$id, vln_metrics$label)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Dot Plot {.tabset}

### Class

```{r 28-dot_tg_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 6}
array <- PrepSCTFindMarkers(array)

Idents(array) <- "Class"

DotPlot_scCustom(array, features = marker_features_half, colors_use = dotplot_colors) + 
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

### Class

```{r 29-dot_tg_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 6, fig.width = 6}
Idents(array) <- "Type"

DotPlot_scCustom(array, features = marker_features_half, colors_use = dotplot_colors) + 
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

## Stacked Violin {.tabset}

### Class

```{r 30-stacked_vln_marker_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 6}
VlnPlot(array, features = marker_features, 
        pt.size = 0, stack = TRUE, flip = TRUE, 
        group.by = 'Class') + 
        theme(legend.position = 'none')
```

### Class

```{r 31-stacked_vln_marker_type, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
VlnPlot(array, features = marker_features, 
        pt.size = 0, stack = TRUE, flip = TRUE, 
        group.by = 'Type') + 
        theme(legend.position = 'none')
```

## Heatmap {.tabset}

### Class

```{r 32-heatmap_marker_class, message = FALSE, warning = FALSE, results = "hide", dev = "png", fig.height = 8, fig.width = 16}
DoHeatmap(array, features = marker_features, group.by = 'Class', size = 0,
          group.colors = class_colors) +
          scale_fill_gradientn(colours = heatmap_colors) +  
          scale_colour_manual(values = class_colors)
```

### Type

```{r 33-heatmap_marker_type, message = FALSE, warning = FALSE, results = "hide", dev = "png", fig.height = 8, fig.width = 16}
DoHeatmap(array, features = marker_features, group.by = 'Class', size = 0,
          group.colors = type_colors) +
          scale_fill_gradientn(colours = heatmap_colors) +  
          scale_colour_manual(values = type_colors)
```

# Visualize cluster distances {.tabset}

## Dendrogram {.tabset}

### Class

```{r 34-class_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
class_dend <- create_dendrogram(array, as.factor(array$Class), class_colors)

plot(class_dend[[2]], axes = FALSE)
```

### Type

```{r 35-type_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
type_dend <- create_dendrogram(array, as.factor(array$Type), type_colors)

plot(type_dend[[2]], axes = FALSE)
```

### Class with Region ID

```{r 36-class_dendrogram_region, message = FALSE, warning = FALSE, results = "hide"}
# create region+class convolution ID
array <- AddMetaData(array, metadata = paste(array$Region, array$Class), col.name = "Region_Class")

class_region_dend <- create_dendrogram(array, as.factor(array$Region_Class), region_class_colors)

plot(class_region_dend[[2]], axes = FALSE)
```

### Type with Region ID

```{r 37-type_dendrogram_region, message = FALSE, warning = FALSE, results = "hide"}
# create region+class convolution ID
array <- AddMetaData(array, metadata = paste(array$Region, array$Type), col.name = "Region_Type")

type_region_dend <- create_dendrogram(array, as.factor(array$Region_Type), region_type_colors)

plot(type_region_dend[[2]], axes = FALSE)
```

## Cluster distance heatmap {.tabset}

### Class {.tabset}

#### Distance

```{r 38-cluster_heatmap_class_dist, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(class_dend, method_id = "distance")
```

#### Correlation

```{r 39-cluster_heatmap_class_cor, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(class_dend, method_id = "correlation")
```

### Type {.tabset}

#### Distance

```{r 40-cluster_heatmap_type_dist, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(type_dend, method_id = "distance")
```

#### Correlation

```{r 41-cluster_heatmap_type_cor, message = FALSE, warning = FALSE, results = "hide"}
dendrogram_heatmap(type_dend, method_id = "correlation")
```

### Class with Region ID {.tabset}

#### Distance

```{r 42-cluster_heatmap_region_class_dist, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(class_region_dend, method_id = "distance")
```

#### Correlation

```{r 43-cluster_heatmap_region_class_cor, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(class_region_dend, method_id = "correlation")
```

### Type with Region ID {.tabset}

#### Distance

```{r 44-cluster_heatmap_region_type_dist, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(type_region_dend, method_id = "distance")
```

#### Correlation

```{r 45-cluster_heatmap_region_type_cor, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(type_region_dend, method_id = "correlation")
```

## Pseudobulk PCA {.tabset}

### Class

```{r 46-pseudobulk_pca_clas, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "orig.ident", "Batch", class_colors)
```

### Type

```{r 47-pseudobulk_pca_clas, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "orig.ident", "Type", type_colors)
```

### Region-Class

```{r 48-pseudobulk_pca_region-class, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "Region_Class", "Region_Class", region_class_colors)
```

### Region-Type

```{r 49-pseudobulk_pca_region-tissue, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca(array, "Region_Type", "Region_Type", region_type_colors)
```
