---
author: "James Howe"
params:
  id: "plCoA"
  input_path: "output/sequencing/03-processed_datasets-RNA/"
  output_path: "output/sequencing/04-subcluster_datasets-RNA/"
title: "Reclassification and merging of clusters: `r params$id`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook assigns broad identities based on well-known marker genes, consolidates them into legible identities, and then exports them for subclustering within their broad identities.

```{r setup, message = FALSE, warning = FALSE}
id <- params$id
input <- paste0(params$input_path, id)
output <- params$output_path
dimn <- params$dimn

source("../code/sequencing_misc.R")
source("../code/sequencing-color_scales.R")
source("../code/sequencing-plot_functions.R")

require(Seurat)
require(tidyverse)
require(knitr)
require(scCustomize)
require(clustree)
require(chisq.posthoc.test)
require(speckle)
require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)
require(colorRamps)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 02

Imports the merged and transformed Seurat object from step 02. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already.

```{r 1-read_integrated_data, message = FALSE, warning = FALSE}
array <- readRDS("output/sequencing/04-subcluster_datasets-RNA/plCoA_all_RNA.rds")
```

# Import annotation {.tabset}

Adds annotation from lower level clusters.

```{r 2-import_annotate, message = FALSE, warning = FALSE}
# neuron vs nonneuron
neuron_clusters <- read.csv("output/sequencing/cluster_lists/04C-Neuron_class_clusters.csv", row.names = 1)
nonneuron_clusters <- read.csv("output/sequencing/cluster_lists/03F-Nonneuron_class_clusters.csv", row.names = 1)

# type annotation
glut_clusters <- read.csv("output/sequencing/cluster_lists/05L-Glut_type_clusters.csv", row.names = 1)
gaba_clusters <- read.csv("output/sequencing/cluster_lists/05M-GABA_type_clusters.csv", row.names = 1)
astro_clusters <- read.csv("output/sequencing/cluster_lists/05N-Astro_type_clusters.csv", row.names = 1)
macro_clusters <- read.csv("output/sequencing/cluster_lists/05O-Macro_type_clusters.csv", row.names = 1)
nfol_clusters <- read.csv("output/sequencing/cluster_lists/05P-NFOL_type_clusters.csv", row.names = 1)
mol_clusters <- read.csv("output/sequencing/cluster_lists/05Q-MOL_type_clusters.csv", row.names = 1)
abc_clusters <- read.csv("output/sequencing/cluster_lists/05R-ABC_type_clusters.csv", row.names = 1)
vlmc_clusters <- read.csv("output/sequencing/cluster_lists/05S-VLMC_type_clusters.csv", row.names = 1)

# replace classes
array <- AddMetaData(array, metadata = as.character(array$Tissue), col.name = "Class")

array$Class[array$Class == "Neuron"] <- neuron_clusters$Class
array$Class[array$Class == "Nonneuron"] <- nonneuron_clusters$Class

# replace types
array <- AddMetaData(array, metadata = array$Class, col.name = "Type")
array <- AddMetaData(array, metadata = array$Class, col.name = "Type_Marker")

array$Type[array$Type %in% "Glut"] <- glut_clusters$Type
array$Type_Marker[array$Type_Marker == "Glut"] <- glut_clusters$Type.Marker

array$Type[array$Type %in% "GABA"] <- gaba_clusters$Type
array$Type_Marker[array$Type_Marker == "GABA"] <- gaba_clusters$Type.Marker

array$Type[array$Type == "Astro"] <- astro_clusters$Type
array$Type_Marker[array$Type_Marker == "Astro"] <- astro_clusters$Type.Marker

array$Type[array$Type == "Macro"] <- macro_clusters$Type
array$Type_Marker[array$Type_Marker == "Macro"] <- macro_clusters$Type.Marker

array$Type[array$Type == "NFOL"] <- nfol_clusters$Type
array$Type_Marker[array$Type_Marker == "NFOL"] <- nfol_clusters$Type.Marker

array$Type[array$Type == "MOL"] <- mol_clusters$Type
array$Type_Marker[array$Type_Marker == "MOL"] <- mol_clusters$Type.Marker

array$Type[array$Type == "ABC"] <- abc_clusters$Type
array$Type_Marker[array$Type_Marker == "ABC"] <- abc_clusters$Type.Marker

array$Type[array$Type == "VLMC"] <- vlmc_clusters$Type
array$Type_Marker[array$Type_Marker == "VLMC"] <- vlmc_clusters$Type.Marker

array$Class <- factor(array$Class, levels = c("Glut", "GABA", "Astro", "Micro", "Macro", 
                                              "OPC", "NFOL", "MOL", "Endo", "Mural", "ABC", "VLMC"))

array$Type <- factor(array$Type, levels = c("Glut.1", "Glut.2", "Glut.3",
                                            "Glut.4", "Glut.5", "Glut.6",
                                            "Glut.7", "Glut.8", "Glut.9",
                                            "Glut.10", "Glut.11", "Glut.12", "Glut.13", "Glut.14",
                                            "GABA.1", "GABA.2", "GABA.3",
                                            "GABA.4", "GABA.5", "GABA.6",
                                            "GABA.7", "GABA.8", "GABA.9",
                                            "GABA.10", "GABA.11", "GABA.12", "GABA.13",
                                            "Astro.1", "Astro.2",
                                            "Micro", "Macro.1", "Macro.2", 
                                            "OPC", "NFOL.1", "NFOL.2", "MOL.1", "MOL.2", 
                                            "Endo", "Mural", 
                                            "ABC.1", "ABC.2", "ABC.3", "VLMC.1", "VLMC.2", "VLMC.3"))
array$Type_Marker <- factor(array$Type_Marker, 
                            levels = c("Glut.Zfp536", "Glut.Satb2",
                                       "Glut.Gulp1", "Glut.Fign", 
                                       "Glut.Ror1", "Glut.Reln",
                                       "Glut.Meis1", "Glut.Smoc1", "Glut.Ntng1",
                                       "Glut.Ebf1", "Glut.Vwc2", 
                                       "Glut.Ebf2", "Glut.Etv1", "Glut.Sim1",
                                       "GABA.Lamp5", "GABA.Nxph2", "GABA.Vip",
                                       "GABA.Sst", "GABA.Nell2", "GABA.Slc16a2",
                                       "GABA.Npas1", "GABA.Tacr1", "GABA.Pdzrn3",
                                       "GABA.Vcan", "GABA.Npsr1", "GABA.Spon1", "GABA.Rai14", 
                                       "Astro.Luzp2", "Astro.Myoc",
                                       "Micro", "Macro.F13a1", "Macro.Cd74", 
                                       "OPC", "NFOL.Frmd4a", "NFOL.Sgcd", "MOL.Mast4", "MOL.Prom1", 
                                       "Endo", "Mural", 
                                       "ABC.Slc4a10", "ABC.Ranbp3l", "VLMC.Mgat4c", "VLMC.Bnc2", "VLMC.Hecw2"))

plot_group_array <- cbind.data.frame(array$Tissue,
                                     array$Class,
                                     array$Type,
                                     array$orig.ident,
                                     array$Region)
colnames(plot_group_array) <- c("Tissue", "Class", "Type", "Batch", "Region")
```

# Identify marker genes

```{r 9-find_markers, message = FALSE, warning = FALSE, results = "hide"}
pct_expressed_aplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$Class), 
                 function(x) rowSums(array@assays$RNA@counts[, array$Class == x & array$Region == "aplCoA"] != 0) 
                             / length(array$Class[array$Class == x & array$Region == "aplCoA"]))))

pct_expressed_pplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$Class), 
                 function(x) rowSums(array@assays$RNA@counts[, array$Class == x & array$Region == "pplCoA"] != 0) 
                             / length(array$Class[array$Class == x & array$Region == "pplCoA"]))))

pct_expressed <- pmax(pct_expressed_aplCoA, pct_expressed_pplCoA)

colnames(pct_expressed) <- levels(array$Class)

rm(pct_expressed_aplCoA, pct_expressed_pplCoA)


# find de novo markers, clusters
marker_class <- markers_sc_wilcox(array, "Class")
marker_type <- markers_sc_wilcox(array, "Type")

# find regional markers within cell types
marker_class_region <- markers_pb_edgeRLRT(array, "Class", 0.1)
marker_type_region <- markers_pb_edgeRLRT(array, "Type", 0.1)
```

# Select marker genes

```{r 10-choose_markers, message = FALSE, warning = FALSE, results = "hide"}
# region-specific
marker_class_region_aplCoA <- lapply(marker_class_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC > 0.585,]})
marker_class_region_pplCoA <- lapply(marker_class_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC < -0.585,]})

marker_type_region_aplCoA <- lapply(marker_type_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC > 0.585,]})
marker_type_region_pplCoA <- lapply(marker_type_region, 
                                    function(x) {x[x$p_val_adj < .05 & x$avg_logFC < -0.585,]})

# based on numbers for max of each one
deg_range_class <- c(0, 90)
deg_range_type <- c(0, 90)
```

## DEG Abundance {.tabset}

### Class {.tabset}

#### aplCoA

```{r 11-deg_abundance_magnitude_class_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
deg_abundance_plot_magnitude(marker_class_region_aplCoA, deg_intensity_colors_aplCoA, deg_range_class, "aplCoA")
```

#### pplCoA

```{r 12-deg_abundance_magnitude_class_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
deg_abundance_plot_magnitude(marker_class_region_pplCoA, deg_intensity_colors_pplCoA, deg_range_class, "pplCoA")
```

### Type {.tabset}

#### aplCoA

```{r 13-deg_abundance_magnitude_class_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
deg_abundance_plot_magnitude(marker_type_region_aplCoA, deg_intensity_colors_aplCoA, deg_range_type, "aplCoA")
```

#### pplCoA

```{r 14-deg_abundance_magnitude_class_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 2.5}
deg_abundance_plot_magnitude(marker_type_region_pplCoA, deg_intensity_colors_pplCoA, deg_range_type, "pplCoA")
```
