---
author: "James Howe"
params:
  id: "plCoA"
  input_path: "output/sequencing/03-clusters-RNA/"
title: "Initial cell type classification: `r params$id`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook assigns broad identities based on well-known marker genes, consolidates them into legible identities, and then exports them for subclustering within their broad identities.

```{r setup, message = FALSE, warning = FALSE}
id <- params$id
input <- paste0(params$input_path, id, "_all_initial.rds")
dimn <- params$dimn

source("code/sequencing_misc.R")
source("code/sequencing-color_scales.R")
source("code/sequencing-plot_functions.R")

require(Seurat)
require(tidyverse)
require(knitr)
require(EnhancedVolcano)
require(Libra)
require(enrichR)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 03

Imports the merged and transformed Seurat object from step 03: initial clustering. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already, as well as have clusters assigned.

```{r 1-read_data, message = FALSE, warning = FALSE}
array <- readRDS(input)
```

## Find Proportion Expressed Per Gene

```{r 2-percent_expressed, message, FALSE, warning = FALSE}
pct_expressed_aplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$Class), 
                 function(x) rowSums(array@assays$RNA@counts[, array$Class == x & array$Region == "aplCoA"] != 0) 
                             / length(array$Class[array$Class == x & array$Region == "aplCoA"]))))

pct_expressed_pplCoA <- do.call(cbind.data.frame, 
                         (lapply(levels(array$Class), 
                 function(x) rowSums(array@assays$RNA@counts[, array$Class == x & array$Region == "pplCoA"] != 0) 
                             / length(array$Class[array$Class == x & array$Region == "pplCoA"]))))

pct_expressed <- pmax(pct_expressed_aplCoA, pct_expressed_pplCoA)

colnames(pct_expressed) <- levels(array$Class)

rm(pct_expressed_aplCoA, pct_expressed_pplCoA)
```

# De Novo Markers {.tabset}

Chooses de novo markers first for individual cell types at the tissue and class level, and also for regions within these cell types. Markers are found using the Seurat FindMarkers algorithm, which uses the Wilcoxon rank-sum test between both groups of cells being compared. Requires at least 3 cells expressing the feature in each group being compared, and sets a lower bound of a fold change of 1.5 and a minimum of 10% of cells in the group expressing the feature, with p-values of 0.01 after adjustment. Region-specific markers are identified using pseudobulk edgeR-LRT testing with batches as replicates and regions as labels within cell types.

```{r 2-find_markers, message = FALSE, warning = FALSE, results = "hide"}
# find de novo markers, clusters
marker_tissue <- markers_sc_wilcox(array, "Tissue")
marker_class <- markers_sc_wilcox(array, "Class")

# find regional markers within cell types
marker_tissue_region <- markers_pb_edgeRLRT(array, "Tissue", 0.1)
marker_class_region <- markers_pb_edgeRLRT(array, "Class", 0.1)
```

# Volcano (region markers) {.tabset}

## Unlabeled {.tabset}

### Tissue {.tabset}

```{r 3-volcano_tissue, message = FALSE, warning = FALSE, results = "hide", fig.height = 6, fig.width = 4}
src_list <- lapply(levels(as.factor(array$Tissue)), function(tissue) {
    src <- c(
        "##### {{tissue}} {.unnumbered}",
        "```{r volcano-tissue-{{tissue}}, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 4}",
        "enhanced_volcano_plot(marker_tissue_region${{tissue}}, 
                               title_id = paste('{{tissue}}'), label_size = 0)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Class {.tabset}

```{r 4-volcano_class, message = FALSE, warning = FALSE, results = "hide", fig.height = 6, fig.width = 4}
src_list <- lapply(levels(as.factor(array$Class)), function(class) {
    src <- c(
        "##### {{class}} {.unnumbered}",
        "```{r volcano-class-{{class}}, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 4}",
        "enhanced_volcano_plot(marker_class_region${{class}}, 
                               title_id = paste('{{class}}'), label_size = 0)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Labeled {.tabset}

### Tissue {.tabset}

```{r 5-volcano_tissue_label, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
src_list <- lapply(levels(as.factor(array$Tissue)), function(tissue) {
    src <- c(
        "##### {{tissue}} {.unnumbered}",
        "```{r volcano-tissue-{{tissue}}-label, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}",
        "enhanced_volcano_plot(marker_tissue_region${{tissue}}, 
                               title_id = paste('{{tissue}}'), label_size = 2)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Class {.tabset}

```{r 6-volcano_class_label, message = FALSE, warning = FALSE, results = "hide", fig.height = 12, fig.width = 12}
src_list <- lapply(levels(as.factor(array$Class)), function(class) {
    src <- c(
        "##### {{class}} {.unnumbered}",
        "```{r volcano-class-{{class}}-label, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}",
        "enhanced_volcano_plot(marker_class_region${{class}}, title_id = paste('{{class}}'), 
        label_size = 2)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

```{r 7-glut-volcano-pub, message = FALSE, warning = FALSE, results = "hide", fig.height = 6, fig.width = 4}
EnhancedVolcano(marker_class_region$Glutamatergic,  
                title = "Glutamatergic",
                subtitle = 'P-value < .01, Magnitude change > log2(0.585)-fold (1.5 or 50%)',
                pointSize = 1.5,
                labSize = 0,
                lab = rownames(marker_class_region$Glutamatergic),
                pCutoff = 1e-02,
                FCcutoff = 0.585,
                x = 'avg_logFC',
                y = 'p_val_adj',
                xlim = c(-6, 6),
                ylim = c(0, 20),
                gridlines.major = FALSE,
                gridlines.minor = FALSE)
```

```{r 8-gaba-volcano-pub, message = FALSE, warning = FALSE, results = "hide", fig.height = 6, fig.width = 4}
EnhancedVolcano(marker_class_region$GABAergic,  
                title = "GABAergic",
                subtitle = 'P-value < .01, Magnitude change > log2(0.585)-fold (1.5 or 50%)',
                pointSize = 1.5,
                labSize = 0,
                lab = rownames(marker_class_region$GABAergic),
                pCutoff = 1e-02,
                FCcutoff = 0.585,
                x = 'avg_logFC',
                y = 'p_val_adj',
                xlim = c(-6, 6),
                ylim = c(0, 20),
                gridlines.major = FALSE,
                gridlines.minor = FALSE)
```

# Cell type marker genes

```{r 9-filter_marker_lists, message = FALSE, warning = FALSE, results = "hide"}
# region-specific
marker_tissue_region_aplCoA <- lapply(marker_tissue_region, 
                                      function(x) {x[x$p_val_adj < .05 & x$avg_logFC > 0.585,]})
marker_tissue_region_pplCoA <- lapply(marker_tissue_region, 
                                      function(x) {x[x$p_val_adj < .05 & x$avg_logFC < -0.585,]})

# 1.5-fold difference
marker_class_region_aplCoA <- lapply(marker_class_region, 
                              function(x) {x[x$p_val_adj < .05 & x$avg_logFC > 0.585,]})
marker_class_region_pplCoA <- lapply(marker_class_region, 
                                       function(x) {x[x$p_val_adj < .05 & x$avg_logFC < -0.585,]})

# based on numbers for max of each one
deg_range_tissue <- c(0, 450)
deg_range_class <- c(0, 250)
```

## Tissue {.tabset}

```{r 10-markers_list_tissue, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_tissue), function(group) {
    src <- c(
        "### {{group}} {.unnumbered}",
        "```{r marker-tissue-{{group}}, message = FALSE, warning = FALSE}",
        "marker_tissue${{group}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Class {.tabset}

```{r 11-markers_list_class, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_class), function(group) {
    src <- c(
        "### {{group}} {.unnumbered}",
        "```{r marker-class-{{group}}, message = FALSE, warning = FALSE}",
        "marker_class${{group}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Region marker genes {.tabset}

## aplCoA {.tabset}

### Tissue {.tabset}

```{r 12-markers_list_aplCoA_tissue, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_tissue_region_aplCoA), function(tissue) {
    src <- c(
        "##### {{tissue}} {.unnumbered}",
        "```{r marker-tissue-aplCoA-{{tissue}}, message = FALSE, warning = FALSE}",
        "marker_tissue_region_aplCoA${{tissue}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Class {.tabset}

```{r 13-markers_list_aplCoA_class, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_class_region_aplCoA), function(class) {
    src <- c(
        "##### {{class}} {.unnumbered}",
        "```{r marker-class-aplCoA-{{class}}, message = FALSE, warning = FALSE}",
        "marker_class_region_aplCoA${{class}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## pplCoA {.tabset}

### Tissue {.tabset}

```{r 14-markers_list_pplCoA_tissue, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_tissue_region_pplCoA), function(tissue) {
    src <- c(
        "##### {{tissue}} {.unnumbered}",
        "```{r marker-tissue-pplCoA-{{tissue}}, message = FALSE, warning = FALSE}",
        "marker_tissue_region_pplCoA${{tissue}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Class {.tabset}

```{r 15-markers_list_cea_class, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(marker_class_region_pplCoA), function(class) {
    src <- c(
        "##### {{class}} {.unnumbered}",
        "```{r marker-class-pplCoA-{{class}}, message = FALSE, warning = FALSE}",
        "marker_class_region_pplCoA${{class}}",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# DEG Abundance

## Region-specific {.tabset}

### Tissue {.tabset}

#### All DEGs {.tabset}

##### aplCoA

```{r 16-deg_abundance_tissue_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 1}
deg_abundance_plot(marker_tissue_region_aplCoA, rep(region_colors[1], times = length(levels(array$Tissue))),
                   array$Tissue, deg_range_tissue)
```

##### pplCoA

```{r 17-deg_abundance_tissue_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 1}
deg_abundance_plot(marker_tissue_region_pplCoA, rep(region_colors[2], times = length(levels(array$Tissue))),
                   array$Tissue, deg_range_tissue)
```

#### Magnitude-based DEGs {.tabset}

##### aplCoA

```{r 18-deg_abundance_magnitude_tissue_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 1}
deg_abundance_plot_magnitude(marker_tissue_region_aplCoA, deg_intensity_colors_aplCoA, deg_range_tissue, "aplCoA")
```

##### pplCoA

```{r 19-deg_abundance_magnitude_tissue_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 4, fig.width = 1}
deg_abundance_plot_magnitude(marker_tissue_region_pplCoA, deg_intensity_colors_pplCoA, deg_range_tissue, "pplCoA")
```

### Class {.tabset}

#### All DEGs {.tabset}

##### aplCoA

```{r 20-deg_abundance_class_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 2, fig.width = 3.5}
deg_abundance_plot(marker_class_region_aplCoA, rep(region_colors[1], times = length(levels(array$Class))),
                   array$Class, deg_range_class)
```

##### pplCoA

```{r 21-deg_abundance_class_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 2, fig.width = 3.5}
deg_abundance_plot(marker_class_region_pplCoA, rep(region_colors[2], times = length(levels(array$Class))),
                   array$Class, deg_range_class)
```

#### Magnitude-based DEGs {.tabset}

##### aplCoA

```{r 22-deg_abundance_magnitude_class_aplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 2, fig.width = 3.5}
deg_abundance_plot_magnitude(marker_class_region_aplCoA, deg_intensity_colors_aplCoA, deg_range_class, "aplCoA")
```

##### pplCoA

```{r 23-deg_abundance_magnitude_class_pplCoA, message = FALSE, warning = FALSE, results = "hide", fig.height = 2, fig.width = 3.5}
deg_abundance_plot_magnitude(marker_class_region_pplCoA, deg_intensity_colors_pplCoA, deg_range_class, "pplCoA")
```

# enrichR {.tabset}

```{r 24-start_enrichR, message = FALSE, warning = FALSE}
dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018", "KEGG_2016")
```

## Type {.tabset}

### Tissue

```{r 25-run_enrichR-tissue, message = FALSE, warning = FALSE, results = 'hide'}
enrichr_tissue <- marker_tissue

for (i in 1:length(enrichr_tissue)){
  enrichr_tissue[[i]] <- enrichr(marker_tissue[[i]]$gene, databases = dbs) 
}
```

### Class

```{r 26-run_enrichR-class, message = FALSE, warning = FALSE, results = 'hide'}
enrichr_class <- marker_class

for (i in 1:length(enrichr_class)){
  enrichr_class[[i]] <- enrichr(marker_class[[i]]$gene, databases = dbs) 
}
```

## Region {.tabset}

### Tissue

```{r 27-run_enrichR-region-tissue, message = FALSE, warning = FALSE, results = 'hide'}
enrichr_region_tissue <- list(marker_tissue_region_aplCoA, marker_tissue_region_pplCoA)

enrichr_region_tissue[[1]] <- lapply(marker_tissue_region_aplCoA, function(x) enrichr(rownames(x), databases = dbs))
enrichr_region_tissue[[2]] <- lapply(marker_tissue_region_pplCoA, function(x) enrichr(rownames(x), databases = dbs))
                              
names(enrichr_region_tissue) <- c("aplCoA", "pplCoA")
```

### Class

```{r 28-run_enrichR-region-class, message = FALSE, warning = FALSE, results = 'hide'}
enrichr_region <- list(marker_class_region_aplCoA, marker_class_region_aplCoA)

enrichr_region[[1]] <- lapply(marker_class_region_aplCoA, function(x) enrichr(rownames(x), databases = dbs))
enrichr_region[[2]] <- lapply(marker_class_region_pplCoA, function(x) enrichr(rownames(x), databases = dbs))
                              
names(enrichr_region) <- c("aplCoA", "pplCoA")
```

# Save gene lists

Save the gene lists produced by identifying DEGs from each method.

```{r 29-save_matrices, message = FALSE, warning = FALSE}
# need to loop separately due to subsetting quirks

# save marker lists
for (i in 1:length(names(marker_tissue))){
  write.csv(marker_tissue[[i]], 
            file = paste0("output/sequencing/marker_lists/cell_type/", names(marker_tissue)[i], ".csv"))
}

for (i in 1:length(names(marker_class))){
  write.csv(marker_class[[i]], 
            file = paste0("output/sequencing/marker_lists/cell_type/", names(marker_class)[i], ".csv"))
}

# save the overgroups/tissues
for (i in 1:length(names(marker_tissue_region_aplCoA))){
    write.csv(marker_tissue_region_aplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_tissue_region_aplCoA)[i], "_aplCoA.csv")) 
}

for (i in 1:length(names(marker_tissue_region_pplCoA))){
  for (j in 1:length(names(marker_tissue_region_pplCoA[[i]]))){
    write.csv(marker_tissue_region_pplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_tissue_region_pplCoA)[i], "_pplCoA.csv"))
  }
}

# save the subgroups/classes
for (i in 1:length(names(marker_class_region_aplCoA))){
    write.csv(marker_class_region_aplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_class_region_aplCoA)[i], "_aplCoA.csv")) 
}

for (i in 1:length(names(marker_class_region_pplCoA))){
  for (j in 1:length(names(marker_class_region_pplCoA[[i]]))){
    write.csv(marker_class_region_pplCoA[[i]], 
              file = paste0("output/sequencing/marker_lists/region_in_celltype/", 
                            names(marker_class_region_pplCoA)[i], "_pplCoA.csv"))
  }
}
```
