---
author: "James Howe"
params:
  input_path: "output/spatial/merged/merged_array.rds"
  output_path: "output/spatial/merged/"
title: "Spatial preprocessing: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook is a basic workflow to go from raw CellRanger ATAC pipeline output to a pre-processed, Signac-formatted dataset with low-quality cells and outliers removed.  Most filtering steps are generally found in other papers, as listed in the methods.

```{r setup, message = FALSE, warning = FALSE}
# set up paths
input <- params$input_path
output <- params$output_path
id <- params$dataset
path <- paste0(input, id)
output_path <- paste0(output, id)

# import helper scripts
source("code/sequencing_misc.R")
source("code/sequencing-color_scales.R")
source("code/sequencing-plot_functions.R")

# load packages
require(tidyverse)
require(Seurat)
require(SeuratData)
require(patchwork)
require(hdf5r)
require(Matrix.utils)
require(knitr)
require(future)
require(scCustomize)
require(clustree)
require(chisq.posthoc.test)
require(speckle)
require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)
require(colorRamps)
require(reticulate)

# set up parallelization, multisession for compatibility purposes, assuming 32GB RAM
plan("multisession", earlySignal = TRUE, gc = TRUE)
options(future.globals.maxSize = 32 * 1024 ^ 3)

#use_virtualenv("r-reticulate")
use_python("/Users/jhowe6/anaconda3/bin/python", required = TRUE)
leidenalg <- import("leidenalg")

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 02

Imports the merged and transformed Seurat object from step 02. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already.

```{r 1-read_integrated_data, message = FALSE, warning = FALSE}
array <- readRDS(input)
```

# Cluster nuclei {.tabset}

Clusters nuclei using Seurat's implementation of the Leiden clustering algorithm (see methods for references), which improves upon the more traditional Louvain algorithm. Clustering is performed at a variety of resolutions so that the best can be chosen from among the different results, ensuring optimal cluster assignments prior to downstream segmentation. 

```{r 2-leiden_clustering, message = FALSE, warning = FALSE}
array <- FindNeighbors(array, dims = 1:50, k.param = 30, verbose = FALSE)

res_index <- c(0.01, seq(0.1, 2, 0.1))

for (i in 1:length(res_index)){
  array <- FindClusters(array, algorithm = 4, resolution = res_index[i], verbose = TRUE)
}
```

## Clustree {.tabset}

### Standard

```{r 3-clustree_standard, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 14}
clustree(array, prefix = "SCT_snn_res.")
```

### Stability

```{r 4-clustree_stability, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 14}
clustree(array, prefix = "SCT_snn_res.", node_colour = "sc3_stability")
```

## Scatter {.tabset}

### PCA {.tabset}

```{r 5-pca_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r pca-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'pca', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### tSNE {.tabset}

```{r 6-tsne_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r tsne-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'tsne', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### UMAP {.tabset}

```{r 7-umap_res, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(res_index, function(res) {
    src <- c(
        "#### Res {{res}} {.unnumbered}",
        "```{r umap-res-{{res}}, message = FALSE, warning = FALSE}",
        "resolution_plot_formatted(array, 'umap', {{res}}, 'SCT')",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Annotate clusters

## Select optimal resolution

Optimal resolution can be selected by examining clustering on dimension-reduced data to determine if they match visual clustering. Further, clustree (and its packaged stability metric) can be used to find the highest resolution that does not lose stability, providing an optimal balance between over- and under-clustering. It is difficult to automate this without some degree of supervision or hand-curation. This is mostly to identify large clusters, so there is little need to get extremely specific so long as clusters are coherent.

```{r 8-select_resolution, message = FALSE, warning = FALSE}
optimal_res <- 0.7

clusters <- array[[paste0("SCT_snn_res.", optimal_res)]]
array[["seurat_clusters"]] <- NULL
for (i in 1:11){
  array[[paste0("SCT_snn_res.", res_index[i])]] <- NULL 
}
array <- AddMetaData(array, clusters, col.name = "clusters")
Idents(array) <- "clusters"

# helps downstrean formatting to regenerate cluster vector from the array vector
type_clusters_marker <- type_clusters <- as.character(array$clusters)

paste(optimal_res, "is optimal clustering resolution")
```

## Visualize initial clusters {.tabset}

### Dimension-reduced space {.tabset}

```{r 9-dr_consolidated, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "#### {{tab_name}} {.unnumbered}",
        "```{r initial_dr-{{tab_name}}, message = FALSE, warning = FALSE}",
        "DimPlot_scCustom(array, reduction = '{{dr_type}}', group.by = 'ident', colors_use = spatial_colors_initial) + theme_classic() + theme(plot.title = element_blank(), legend.text=element_text(size=8))",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### Map {.tabset}

```{r 10-dr_consolidated_spatial, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(array@images), function(image_name) {
    src <- c(
        "#### {{image_name}} {.unnumbered}",
        "```{r initial_map-{{image_name}}, message = FALSE, warning = FALSE}",
        "SpatialDimPlot(array, images = '{{image_name}}', pt.size.factor = 25)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Find markers

```{r 11-find_markers, message = FALSE, warning = FALSE, results = "hide"}

# find de novo markers, clusters
marker_type <- markers_sc_wilcox(array, "clusters")

#array <- FindSpatiallyVariableFeatures(array, assay = "SCT", selection.method = "moransi")

markers_list_celltype <- c("Slc17a7", "Slc17a6", # glutamatergic neuron
                           "Zfp536", "Maml2", # 0
                           "Satb2", "Col23a1", # 1
                           "Gulp1", "Adarb2", # 2
                           "Fign", "Ccbe1", # 3
                           "Ror1", "Stard13", # 4
                           "Reln", "Sema3a", # 5
                           "Meis1", "Gpc5", # 6
                           "Smoc1", "Chst9", # 7
                           "Ntng1", "Rmst", # 8
                           "Ebf1", "Galnt14", # 9
                           "Vwc2", "Trhr", # 10
                           "Ebf2", "Kcnip1", # 11
                           "Etv1", "Grik3", # 12
                           "Sim1", "Fbn2") # 13

markers_list_spots <- c("Slc17a7", "Slc17a6", # glutamatergic neuron
                        "Tmem91", # 0
                        "Baiap3", # 1
                        "Ptgds", # 2
                        "Tafa1", # 3
                        "Car12", # 4
                        "Mbp", # 5
                        "Smoc1", # 6
                        "Tac1", # 7
                        "Sim1", # 8
                        "Gm42418", # 9
                        "Npy", # 10
                        "Hbb-bt", # 11
                        "Cartpt") # 12

markers_list_spots <- c("Slc17a7", "Slc17a6", # glutamatergic neuron
                        "Baiap3", # 1
                        "Tafa1", # 2
                        "Meis2", # 3
                        "Ptgds", # 4
                        "Gm42418", # 5
                        "Car12", # 6
                        "Tmem91", # 7
                        "Mbp", # 8
                        "Sim1", # 9
                        "Col16a1", # 10
                        "Cartpt") # 11

markers_list <- unique(c(markers_list_celltype, markers_list_spots))
```


```{r 12-classify_cells, message = FALSE, warning = FALSE}
type_clusters[type_clusters %in% "1"] <- "aplCoA.1"
type_clusters_marker[type_clusters_marker %in% "1"] <- "Spatial.Baiap3"

type_clusters[type_clusters %in% "2"] <- "pplCoA.1"
type_clusters_marker[type_clusters_marker %in% "2"] <- "Spatial.Tafa1"

type_clusters[type_clusters %in% "3"] <- "aplCoA.2"
type_clusters_marker[type_clusters_marker %in% "3"] <- "Spatial.Meis2"

type_clusters[type_clusters %in% "4"] <- "L1.1"
type_clusters_marker[type_clusters_marker %in% "4"] <- "Spatial.Ptgds"

type_clusters[type_clusters %in% "5"] <- "L1.2"
type_clusters_marker[type_clusters_marker %in% "5"] <- "Spatial.Gm42418"

type_clusters[type_clusters %in% "6"] <- "pplCoA.2"
type_clusters_marker[type_clusters_marker %in% "6"] <- "Spatial.Car12"

type_clusters[type_clusters %in% "7"] <- "aplCoA.3"
type_clusters_marker[type_clusters_marker %in% "7"] <- "Spatial.Tmem91"

type_clusters[type_clusters %in% "8"] <- "OLG"
type_clusters_marker[type_clusters_marker %in% "8"] <- "Spatial.Mbp"

type_clusters[type_clusters %in% "9"] <- "NLOT"
type_clusters_marker[type_clusters_marker %in% "9"] <- "Spatial.Sim1"

type_clusters[type_clusters %in% "10"] <- "aplCoA.4"
type_clusters_marker[type_clusters_marker %in% "10"] <- "Spatial.Col16a1"

type_clusters[type_clusters %in% "11"] <- "aplCoA.5"
type_clusters_marker[type_clusters_marker %in% "11"] <- "Spatial.Cartpt"

array <- AddMetaData(array, as.factor(type_clusters), col.name = "Type")

array$Type <- factor(array$Type, levels = c("aplCoA.1", "pplCoA.1", "aplCoA.2", 
                                            "L1.1", "L1.2", "pplCoA.2", "aplCoA.3", 
                                            "OLG", "NLOT", "aplCoA.4", "aplCoA.5"))

Idents(array) <- "Type"

table(array$Type)

plot_group_array <- cbind.data.frame(array$Type,
                                     array$id,
                                     array$id_number)
colnames(plot_group_array) <- c("Type", "Slice", "Section")
```

# Visualize consolidated clusters {.tabset}

## Scatter {.tabset}

```{r 13-dr_consolidated_scatter, message = FALSE, warning = FALSE, results = "hide"}
src_list <- mapply(function(tab_name, dr_type) {
    src <- c(
        "## {{tab_name}} {.unnumbered}",
        "```{r consolidated_cluster-{{tab_name}}, message = FALSE, warning = FALSE}",
        "cluster_plot_formatted(array, '{{dr_type}}', 'Type', spatial_colors)",  
        "```",
        ""
    )
    knit_expand(text = src)
}, dr_params$name, dr_params$type)
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Map {.tabset}

```{r 14-dr_consolidated_map, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(names(array@images), function(image_name) {
    src <- c(
        "### {{image_name}} {.unnumbered}",
        "```{r consolidated_cluster_map-{{image_name}}, message = FALSE, warning = FALSE}",
        "SpatialDimPlot(array, images = '{{image_name}}', pt.size.factor = 25) + scale_fill_manual(values = spatial_colors)",
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Visualize marker genes {.tabset}

## Scatter {.tabset}

### PCA {.tabset}

```{r 15-pca_markers, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r pca-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'pca', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### tSNE {.tabset}

```{r 16-tsne_markers, message = FALSE, warning = FALSE, results = "hide", }
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r tsne-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'tsne', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### UMAP {.tabset}

```{r 17-umap_markers, message = FALSE, warning = FALSE, results = "hide", }
src_list <- lapply(markers_list, function(marker) {
    src <- c(
        "#### {{marker}} {.unnumbered}",
        "```{r umap-{{marker}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'umap', '{{marker}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Map {.tabset}

```{r 18-marker_map, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(markers_list, function(marker_name) {
    src <- c(
        "### {{marker_name}} {.unnumbered}",
        "```{r marker_map-{{marker_name}}, message = FALSE, warning = FALSE}",
        "SpatialFeaturePlot(array, images = 'slice1.16', features = '{{marker_name}}', pt.size.factor = 25)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

# Visualize Cluster Distances

## Dendrogram {.tabset}

### Batch

```{r 39-library_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
batch_dend <- create_dendrogram(array, as.factor(array$id_number), spatial_colors_section)

plot(batch_dend[[2]], axes = FALSE)
```

### Type

```{r 40-type_dendrogram, message = FALSE, warning = FALSE, results = "hide"}
type_dend <- create_dendrogram(array, as.factor(array$Type), spatial_colors)

plot(type_dend[[2]], axes = FALSE)
```

## Pseudobulk PCA {.tabset}

### Section

```{r 15-pseudobulk_pca_batch, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca_spatial(array, "id_number", "Section", spatial_colors_section)
```

### Type

```{r 16-pseudobulk_pca_type, message = FALSE, warning = FALSE, results = "hide"}
pseudobulk_pca_spatial(array, "Type", "Type", spatial_colors_section)
```

## Cluster distance heatmap {.tabset}

### Batch {.tabset}

#### Distance

```{r 44-cluster_heatmap_batch_dist, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(batch_dend, method_id = "distance")
```

#### Correlation

```{r 45-cluster_heatmap_batch_cor, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(batch_dend, method_id = "correlation")
```

### Type {.tabset}

#### Distance

```{r 46-cluster_heatmap_type_dist, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(type_dend, method_id = "distance")
```

#### Correlation

```{r 47-cluster_heatmap_type_cor, message = FALSE, warning = FALSE, results = "hide", fig.height = 30, fig.width = 30}
dendrogram_heatmap(type_dend, method_id = "correlation")
```

# Save clustered matrix

The output can now be passed to the next step of the pipeline, broad cell type classification.

```{r 17-save_output, message = FALSE, warning = FALSE}
saveRDS(array, file = "output/spatial/merged/clustered_array.rds")
```
