---
author: "James Howe"
params:
  input_path: "output/spatial/merged/merged_array.rds"
  cells_path: "output/sequencing/05-subcluster_process-RNA/Glutamatergic_processed.rds"
  clusters_path: "output/sequencing/cluster_lists/05L-Glut_type_clusters.csv"
  output_path: "output/spatial/merged/"
title: "Spatial preprocessing: `r params$dataset`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Introduction

This notebook is a basic workflow to project specific cell types from glutamatergic and GABAergic neurons down into spatial data.

```{r setup, message = FALSE, warning = FALSE}
# set up paths
input <- params$input_path
cells_input <- params$cells_path
clusters_input <- params$clusters_path
output <- params$output_path
id <- params$dataset
path <- paste0(input, id)
output_path <- paste0(output, id)

# import helper scripts
source("code/sequencing_misc.R")
source("code/sequencing-color_scales.R")
source("code/sequencing-plot_functions.R")

# load packages
require(tidyverse)
require(Seurat)
require(SeuratData)
require(patchwork)
require(hdf5r)
require(Matrix.utils)
require(knitr)
require(future)
require(scCustomize)
require(clustree)
require(chisq.posthoc.test)
require(speckle)
require(ggtree)
require(pvclust)
require(dendextend)
require(heatmap3)
require(colorRamps)

# set up parallelization, multisession for compatibility purposes, assuming 32GB RAM
plan("multisession", earlySignal = TRUE, gc = TRUE)
options(future.globals.maxSize = 32 * 1024 ^ 3)

# all images are PDFs, avoids pixelation
knitr::opts_chunk$set(dev = 'pdf')
```

## Read in data from step 02

Imports the merged and transformed Seurat objects to project and the Visium object. This object should contain SCT data, all relevant metadata, and it should be barcode- and feature-filtered already for all such objects.

```{r 1-read_integrated_data, message = FALSE, warning = FALSE}
array <- readRDS(input)
rna_array <- readRDS(cells_input)
rna_clusters <- read.csv(clusters_input, row.names = 1)

rna_array <- AddMetaData(rna_array, metadata = rna_clusters$Type, col.name = "Type")
```

# Project nuclei onto Visium

Clusters nuclei using Seurat's implementation of the Leiden clustering algorithm (see methods for references), which improves upon the more traditional Louvain algorithm. Clustering is performed at a variety of resolutions so that the best can be chosen from among the different results, ensuring optimal cluster assignments prior to downstream segmentation. 

```{r 2-predictions, message = FALSE, warning = FALSE}
anchors <- FindTransferAnchors(reference = rna_array, 
                               query = array, 
                               normalization.method = "SCT", dims = 1:50, npcs = 50)

predictions.assay <- TransferData(anchorset = anchors, 
                                  refdata = rna_array$Type, 
                                  prediction.assay = TRUE,
                                  weight.reduction = array[["pca"]], dims = 1:50)

array[["predictions"]] <- predictions.assay

DefaultAssay(array) <- "predictions"
```

# Visualize predictions

## Scatter {.tabset}

### PCA {.tabset}

```{r 3-pca_markers, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(rownames(array@assays$predictions), function(pred_type) {
    src <- c(
        "#### {{pred_type}} {.unnumbered}",
        "```{r pca-{{pred_type}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'pca', '{{pred_type}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### tSNE {.tabset}

```{r 4-tsne_markers, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(rownames(array@assays$predictions), function(pred_type) {
    src <- c(
        "#### {{pred_type}} {.unnumbered}",
        "```{r tsne-{{pred_type}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'tsne', '{{pred_type}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

### UMAP {.tabset}

```{r 5-umap_markers, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(rownames(array@assays$predictions), function(pred_type) {
    src <- c(
        "#### {{pred_type}} {.unnumbered}",
        "```{r umap-{{pred_type}}, message = FALSE, warning = FALSE}",
        "feature_plot_formatted(array, 'umap', '{{pred_type}}', feature_intensity_colors, NA)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`

## Map {.tabset}

```{r 18-type_map, message = FALSE, warning = FALSE, results = "hide"}
src_list <- lapply(rownames(array@assays$predictions), function(pred_type) {
    src <- c(
        "### {{pred_type}} {.unnumbered}",
        "```{r prediction_map-{{pred_type}}, message = FALSE, warning = FALSE}",
        "SpatialFeaturePlot(array, images = 'slice1.16', features = '{{pred_type}}', pt.size.factor = 25)",  
        "```",
        ""
    )
    knit_expand(text = src)
})
out <- knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`
